### 2021-12-10 Manuscript/FLPhish(Trans).tex
first commit

\documentclass[journal]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage{algorithm}  
\usepackage{algorithmicx}  
\usepackage{algpseudocode}  
\usepackage{amsmath} 
\usepackage{color,array}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}  
\usepackage{booktabs}
\usepackage{soul}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{diagbox}
\usepackage{float}
\ifCLASSINFOpdf
\else
\fi

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}

\author{Beibei~Li,~\IEEEmembership{Member,~IEEE,}
        Peiran~Wang,~\IEEEmembership{Student Member,~IEEE,}
        Qinglei~Kong,~\IEEEmembership{Student Member,~IEEE,}
        Yuan~Zhang,~\IEEEmembership{Member,~IEEE,}
        and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
\thanks{This paper is the extended vision of the paper, `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in IEEE ISCC 2021, and was awarded `Best Paper Award' in this conference.}
\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065 China. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
\thanks{Q. Kong is with the Future Network of Intelligence Institute, The Chinese University of Hong Kong, Shenzhen 518172, China, and also with The University of Science and Technology of China, Hefei 230052, China. Email: kql8904@163.com.}
\thanks{Y. Zhang is with the Center for Cyber Security, School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
\thanks{R. Lu is with the Faculty of Computer Science, University of New Brunswick, Fredericton, NB, Canada E3B 5A3. Email: rlu1@unb.ca.}
}

\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

\maketitle

\begin{abstract}
  Federated Learning, a new distributed machine learning scheme, is gaining popularity as the demand for personal privacy grows. Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process. Byzantine attacks are extremely difficult to defend against in the current FL scheme. In this study, we present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. First, we design a new Ensemble FL architecture, to enable flexible implementation of various types of deep learning models in different clients. Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks. Furthermore, a reputation mechanism based on Bayes's theorem is presented to assess each client's level of confidence. Last, we propose two aggregation techniques in FLPhish: FLPhish-threshold and FLPhish-weight. FLPhish is tested with varying proportions of Byzantine clients and varying degrees of distribution imbalance. Extensive experiments under various situations demonstrates the proposed FLPhish's great efficacy in resisting Byzantine attacks in Ensemble FL.
\end{abstract}

\begin{IEEEkeywords}
Federated learning, ensemble learning, bayesian inference reputation, phishing.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\begin{table}[t]
  \caption{Summary of Notations}
  \resizebox{0.5\textwidth}{!}{
  \begin{tabular}{lp{6cm}}
    \bottomrule
    Term&Description\\
    \hline
    $s$ & central server in FL \\
    $\mathbf{M}$ & global model preserved by $s$\\
    $c_i$ & the $i$th client in FL, $i=1,2,3,...,u$ \\
    $d_i$ & the local dataset preserved by the $i$th client \\
    $C$ & the ensemble of all the clients \\
    $u$ & the number of clients\\
    $\mathbf{m_i}$ & local models trained by the $i$th client\\
    $D_t$ & the unlabeled dataset chosen by $s$ in each procedure\\
    $D$ & the unlabeled dataset preserved by $s$\\
    $n$ & the number of samples in $D_t$\\
    $B_t$ & the labeled dataset (\textit{`bait'}) chosen by $s$ in each procedure\\
    $B$ & the labeled dataset preserved by $s$\\
    $m$ & the number of samples in $B_t$\\
    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$ in $t$th procedure\\
    $q_i$ & the label of $c_i$ to judge it is a malicious client or not\\
    $r_q$ & the threhold of malicious clients\\
    $x^t_l$ & the $l$th data point in $D_t$\\
    $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$th data point made by $i$th client\\
    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th round's unlabeled dataset\\
    \hline
  \end{tabular}
  }
\end{table}

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are gathered from users, such as the app's users. Developers get information from users and utilize it to create the dataset. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy protection, making it difficult to get data directly from consumers any more. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}. FL is a privacy-preserving machine learning solution that allows a central server to train a global model without gaining access to individuals' personal privacy data. Instead of training global model on users' private data, the central server in FL just needs to train its global model using their gradient updates. FL protects an individual's privacy while simultaneously reducing the load on the central server by leveraging the capabilities of distributed computation and storage. FL is soon applied by many companies. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp}.

\par In FL, thousands of clients from different sources participate in the training process. Such a large-scale distributed system also brings security issues to FL. Former researchers have already studied the privacy problems of FL and offered their schemes to enhance privacy protection in FL \cite{ref_33_privacy}\cite{ref_34_VerifyNet}. Furthermore, FL clients may be manipulated or poisoned by malicious attackers. Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network\cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly changing the gradient updates, the malicious clients send the incorrect gradient updates to the central server. The incorrect gradient updates cause the central server's global updates to learn incorrect knowledge from the clients. As a result, they render the central server's global model obsolete. Furthermore, Byzantine attacks are divided into two types based on the consequences of the attacks: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients in FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major kinds. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another group of Byzantine-robust approaches (dubbed Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggest that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}. We present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item First, we design a new FL architecture, Ensemble Federated Learning (called Ensemble FL). Ensemble FL utilizes an unlabeled dataset to replace the gradient updates in traditional FL. This architecture supports different types of deep learning models in each client and makes FL more flexible.
  \item Second, we craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system. It preserves the security of Ensemble FL.
  \item Third, we present a bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients. The reputation mechanism helps FLPhish identify the Byzantine clients more accurately.
  \item Last, we propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism. FLPhish using FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish with FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process. These two algorithms contribute to the robustness of FLPhish.
\end{itemize}

\section{Related Work}

\subsection{Byzantine Defense Methods in Federated Learning}
Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al}. Krum developed an approach \cite{ref_12_defense}. Krum selects one client's update as a global model based on a square-distance score in each iteration. 
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation algorithms Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected. Median sorts the values of each parameter of all local model updates as well. And it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach Draco to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Zeno uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first, and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantages of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

\subsection{Reputation Mechanism in Information Security}
The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system \cite{ref_41_reputation, ref_44_reputation}.
In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust. This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance algorithm that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}. The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system. Furthermore, they presented a reputation-based primary change scheme. The node with a higher reputation would get greater opportunities to generate new valid blocks, which reduces the security risk of the system.
In 2020, Chouikhi \textit{et al.} built a model for reputation computing and a credibility model to enhance network efficiency \cite{ref_23_reputation}. They used the reputation score or value to measure the behavior of a vehicle towards other vehicles and network services. And the credibility of vehicles is used to determine the accuracy of a reputation score offered by a vehicle. 
In the same year, Wen \textit{et al.} proposed a Dirichlet reputation-based scheme and adopt the reputation score to select a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}. Furthermore, they developed an artificial noise detection method with multiple thresholds. They provided ratings with multiple graded levels. In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
In 2021, Liang \textit{et al.} presented a markov-based reputation scheme in an intrusion detection system. The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.

\section{Models and Design Goals}

In this section, we discuss the system model, threat model and identify our design goals.

\subsection{System Model}We first discuss the design of traditional FL consisting of two entities, FL server, and FL client.
  \begin{figure}
    \centering
  \includegraphics[width=0.5\textwidth]{figures/FLPhish_System.pdf}
  \caption{System Model\&Threat Model.}
  \label{fig_system}
  \end{figure}   
\subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each round. After receiving the gradient updates of all the clients, the FL server utilizes the gradient updates to aggregate a global update. The aggregation process is accomplished based on FedAvg. After the aggregation process, the FL server updates the global model via adding the global updates to the global model.

\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($c_{i}$ indicates the $i$th client in FL) preserves a local dataset $d_{i}$ collected by themselves. FL client $c_{i}$ uses its local dataset $d_{i}$ to train the model sent from the FL server. Then it dispatches the gradient updates of the model back to the FL server. It repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.

\subsection{Threat Model}
However, the current system still suffers from multiple problems, especially Byzantine attacks. Malicious Byzantine client $b$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $b$ to modify the labels of training data and ensure the features of data unchanging \cite{ref_18_label_flipping}. Byzantine client $b$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $b$ dispatches the false updates of the gradient to the central server. Therefore the false updates of the gradient cause the central server to learn false distilled knowledge from clients. The server $s$'s aggregation process is played on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size number larger than $d_{i}$'s real size number. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

\subsection{Design Goals}
The key objective of the proposed FLPhish scheme is to provide a robust approach to accurately resist opportunistic untargeted attacks in our Ensemble FL system. Our design goals are given as follows:

  \par \textit{1)} Inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provide more opportunities for us to counter Byzantine attacks in FL.
  \par \textit{2)} Our proposed Ensemble FL architecture lacks protection against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based model to guard against Byzantine attacks in our proposed Ensemble FL system.
  \par \textit{3)} To accurately assess clients' behaviors, we further propose an effective bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
  \par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

  \begin{figure*}
    \centering
  \includegraphics[width=0.95\textwidth]{figures/Figure_FLPhish.pdf}
  \caption{Our Proposed FLPhish Scheme.}
  \label{fig_Phishing}
  \end{figure*}

\section{Our Proposed FLPhish Scheme}
In this section, we elaborate on the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation algorithms.

\begin{algorithm}[t]
  \caption{Ensemble FL} %algorithm name
  \label{alg:system}
  \hspace*{0.02in} {\bf Input:} %the input of the algorithm
  the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$; number of training iterations $T$; unlabeled batch size $n$;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its own local dataset $d_i$;
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ samples) from $D$;
      \For{\textit{i=1,2,3,...,u}}
        \State $s \overset{D_{t}}{\rightarrow} c_{i}$;
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$;
        \State $c_i \overset{\mathbf{k_i^t}}{\rightarrow} s$;
      \EndFor
      \State $Y_t$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$;
      \State $\mathbf{M}$ = $ModelUpdate(Y_t, D_t, \mathbf{M})$;
    \EndFor \\
    \Return $\mathbf{M}$.
  \end{algorithmic}
\end{algorithm}
\begin{algorithm}[t]
  \caption{KnowledgeEnsemble} %algorithm name
  \label{alg:KnowledgeEnsemble}
  \hspace*{0.02in} {\bf Input:} %input of the algorithm
  the ensemble of ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th procedure; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
      \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
      \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
    \EndFor \\
    \Return $\mathbf{\hat{y}^t}$.
  \end{algorithmic}

\end{algorithm}

\subsection{Designed Ensemble Federated Learning}
Inspired by the idea of ensemble learning, we propose a new FL architecture, Ensemble FL.
\par Unlike existing FL architecture, which adopts gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.

\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the number of the client) undertakes the task of collecting their local data, and labeling its local data. {$c_{i}$} collects data from the personal computer, smartphone, and smart cars, etc. The collected data is labeled and preprocessed by {$c_{i}$}. After that, {$c_{i}$} adopts the preprocessed local dataset to train its local model. When receiving a public dataset, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
\subsubsection{{Central server}} Central server {$s$} is responsible for making a public dataset and building a global model. The public dataset consists of a variety of data that is unlabeled. The dataset is collected by {$s$} or produced by it (such as using GAN to generate data). After the construction of the public dataset, {$s$} sends the public dataset to the clients. Each client {$c_{i}$} sends its predictions about the public dataset back to {$s$}. After receiving all the predictions, {$s$} aggregates the predictions. Then {$s$} employs the aggregated results and the public dataset to train the global model.

\par This system model demonstrates a variety of advantages over traditional FL architectures:
\begin{itemize}

  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in traditional FL. Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients). Different selected features in different clients are permitted as well.
  \item The overheads and latency of the communication process are significantly reduced compared to the traditional FL architecture. Transferring data is much faster than transferring gradient updates. 
\end{itemize}

\begin{algorithm}[t]
  \caption{Phishing Mechanism} 
  \hspace*{0.02in} {\bf Input:} 
  the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$ and labeled dataset $B$; number of training iterations $T$; unlabeled batch size $n$;labeled batch size $m$.\\
  \hspace*{0.02in} {\bf Output:} 
  output result
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its own local dataset $d_i$.
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
      \For{\textit{i=1,2,3,...,u}}
        \State $s$ sends $D_t$ and $B_t$ to $c_i$.
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
        \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
        \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
        \If{$a_i^t > r_q$}
          \State $q_i = 1$.
          \For{\textit{j=i,i+1,i+2,...,u-1}}
            \State $d_j \gets d_{j-1}$.
            \State $c_j \gets c_{j+1}$.
            \State $\mathbf{k_j^t} \gets \mathbf{k_{j+1}^t}$.
            \State $q_j \gets q_{j+1}$.
            \State $a_j^t \gets a_{j+1}^t$.
          \EndFor
        \EndIf
      \EndFor
      \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
      \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
    \EndFor
    \State\Return $\mathbf{M}$
  \end{algorithmic}
  \end{algorithm}

\subsection{Phishing Mechanism-based Detection}
The proposed Ensemble FL still confronts the threat of Byzantine attacks. Malicious clients can manipulate their local model via label flipping. They mislabel the local dataset to build a `poisoned' local model. When malicious clients receive unlabeled data from the central server, they manufacture false predictions (called poisoned knowledge) and send these false predictions to the central server. Subsequently, the central server aggregates the false predictions as the labels of the unlabeled dataset. Then central server trains the global model using these unlabeled datasets with the false aggregation predictions. Therefore, a flawed global model is manufactured. Inspired by the idea of ensemble learning, we consider utilizing the labeled data in the architecture of Ensemble FL to cope with Byzantine attacks. We called labeled data `bait'.
  \subsubsection{\ul{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$. Each client $c_i$ possesses a local dataset $d_i$. At the beginning of the Ensemble FL, $c_{i}$ utilizes its local dataset $d_i$ to train a local model $\mathbf{m_i}$ as
  \begin{equation}
    \mathbf{m_i}=Train(d_i).
  \end{equation}
  \subsubsection{\ul{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly. Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
  \begin{equation}
    s \overset{{D_{t},B_{t}}}{\rightarrow} c_{i}.
  \end{equation}
  \subsubsection{\ul{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
  \begin{equation}
    \mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i})
  \end{equation}
  ($c_i$ can not distinguish between $D_t$ and $B_t$) via the local model trained by itself in Step 1  and sends its prediction back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix}.
  \end{equation}

  Unlike benign clients, malicious clients return the false prediction as the distilled knowledge to central server $s$.
  \subsubsection{\ul{Byzantine Identifying}} Accepting the distilled knowledge from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions via the true label of the \textit{`bait'}:
  \begin{equation}
    a_i^t=AccuracyCal(\mathbf{k_i^t}, B_t).
  \end{equation}
  Then $s$ identifies those clients who hold a low value of accuracy and distinguishes as malicious clients.
  \subsubsection{\ul{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregate the knowledge $\mathbf{\hat{k}^t}$ from all clients as
  \begin{equation}
    \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
  \end{equation}
  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
  \begin{equation}
    \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
  \end{equation}

\subsection{Bayesian Inference-based Reputation Mechanism}
Server $s$ maintains a reputation list which records the reputation of all the clients $C$ in the model. Let $X_i$ be the reputation of the $c_i$ client which represents $s$'s belief that how likely client $c_i$ is a Byzantine client. The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st round to the $t$th round. Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the $X_i$.
\par Initially, the reputation is neutral. Each client $c_i$ is considered a benign client by server $s$ with a probability of 50\%. When a new update $\mathbf{k_i^t}$ comes to the server $s$, the reputation is updated by the $s$. When the reputation is lower than the threshold $r$, $s$ considers the client $c_i$ as a Byzantine client officially and discards the update coming from the client $c_i$. The updates of the client $c_i$ are reconsidered in the aggregation when the $X_i$ exceeds the threshold $r$.
\par We employ bayesian inference to construct our reputation mechanism. Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions. Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism. Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$. Given $X_i=\gamma_i$, then the conditional probability is 
\begin{equation}
    Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}.
\end{equation}
$\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$. $\gamma_i$ is unknown. Equation \ref{equation_1} indicates the likelihood function for $X$. According to bayes' theory, we compute the posterior probability as
\begin{equation}
    Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
\end{equation}
As the posterior probability function is given by our analysis, the final value for the expectation value of reputation $X$ is computed as
\begin{equation}
    E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
\end{equation}
Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X. Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$. Therefore the density function is
\begin{equation}
    f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}.
\end{equation}
$B$ function is the beta function. Therefore we compute the expectation of $X$ as
\begin{equation}
    E(x)=\frac{\alpha}{\alpha+\beta}.
\end{equation}

Therefore server ${s}$ can easily compute the reputation of the client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$. We set the initial value of the reputation to 50\% by set the value of ${\alpha}$ and ${\beta}$ to 1. This indicates that the probability of being benign client and malicious client are equal for client ${c_{i}}$. When a new round of FL is accomplished, ${\alpha_{i}}'$ and ${\beta_{i}}'$ are provided as the new evidence for the computation of the reputation. The parameters are updated as ${(\alpha_{i}+{\alpha_{i}}',\beta_{i}+{\beta_{i}}')}$. Then the reputation is given by
\begin{equation}
    {E(x_{i})}'=\frac{\alpha_{i}+{\alpha_{i}}'}{\alpha_{i}+{\alpha_{i}}'+\beta_{i}+{\beta_{i}}'}.
\end{equation}

\subsection{Aggregation Algorithms}
Based on our reputation mechanism, we propose our Byzantine-tolerant aggregation algorithms: FLPhish-threshold and FLPhish-weight.
\subsubsection{{FLPhish-threshold}}
FLPhish-threshold as the aggregation rules identify the clients whose reputation is lower than the reputation threshold. Then the server discards the Byzantine clients and aggregate the global model using the survived clients' updates. Server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and given them a aggregation weight as
\begin{equation}
  \omega_{i}=\begin{cases}
    1 & \text{ if } x\geq \tau \\ 
    0 & \text{ if } x< \tau 
    \end{cases}.
\end{equation} 
The aggregated knowledge is given by
\begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times \omega_{i},
\end{equation}
\begin{equation}
  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
\subsubsection{{FLPhish-weight}}
Unlike FLPhish-threshold, FLPhish-weight does not discard the potential Byzantine clients' updates. On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight. Due to our reputation mechanism, the Byzantine clients are offered a low value of reputation, so it has a lower influence on aggregation.
Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$ and the prediction results 
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix},
  \end{equation}
  FLPhish-weight computes the aggregated knowledge as
    \begin{equation}
    \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
  \end{equation}
  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
  \begin{equation}
    \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
  \end{equation} 
In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and give them lower weight.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[t]

  \renewcommand\arraystretch{1.5}
  \centering
  \caption{Parameter Settings}
  \resizebox{0.5\textwidth}{!}{
  \label{tab:my-table}
  \begin{tabular}{ll}
    \bottomrule
    \textbf{Parameter}                    & \textbf{Parameter Value}              \\ \hline
    Client Number                         & 50 clients                                \\ \hline
    Sample Total Number                   & 60000 samples                             \\ \hline
    \multirow{2}{*}{Client Sample Number} & 800 training samples                      \\
                                          & 200 test samples                          \\ \hline
    \multirow{2}{*}{Server Sample Number} & 8000 unlabeled samples                    \\
                                          & 2000 labeled samples                      \\ \hline
    Round Number                          & 10 rounds                                 \\ \hline
    \multirow{2}{*}{Round Sample Number}  & 800 unlabeled samples                     \\
                                          & 200 labeled samples                       \\ \hline
    Deep Learning Model                   & Residual Networks                         \\ \hline
    Byzantine Fractions $p$               & 0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9     \\ \hline
    Imbalance Degree $q$                  & 0.1,0.2,0.5,0.6,0.7,0.8               \\ \hline
    Dataset $d$                         & MNIST,Fashion-MNIST,CIFAR-10              \\ \hline
    \end{tabular}
}
\end{table}

\section{Performance Evaluation}
In this section, we experimentally evaluate our FLPhish against untargeted attacks under different conditions. Furthermore, we compare our FLPhish's performance with FedAvg's performance, and the results show that FLPhish outperforms FedAvg in defending against Byzantine attacks.

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
    \subfigure[$q=0.9$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
  \label{fig_exp_mnist-reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
    \subfigure[$q=0.9$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on Fashion-MNIST on different imbalance degrees.}
  \label{fig_exp_fashion_reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[{$q=$}0.1]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
    \subfigure[{$q=$}0.2]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
    \subfigure[{$q=$}0.5]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
    \subfigure[{$q=$}0.9]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on CIFAR-10 on different imbalance degrees.}
  \label{fig_exp_cifar_reputation}
  \vspace{0.2in}
\end{figure*}

\subsection{Experiment Setup}

  \subsubsection{{\textit{The fractions {$p$} of Byzantine clients}}} We evaluate our FLPhish under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} According to the previous research \cite{ref_06_model}, we distribute the data in a dataset among all the clients. Giving $M$ classes of data in a dataset, we split the clients into $M$ groups. A client $c$ in group $m$ is provided with data where data $m$ accounts for over $q$ percent. Within the same group, data are uniformly distributed among all the clients. The parameter $q$ controls the distribution inference of clients' local training data. If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed. We evaluate our FLPhish on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
  \subsubsection{{\textit{The number of clients}}} The number of clients is set to 50 in our experiment.
  \subsubsection{{\textit{The local CNN model used by clients}}} ResNet is employed to perform deep learning tasks in our local client.
  \subsubsection{{\textit{The datasets {$d$}}}} We take three different datasets as our experiment datasets: \begin{itemize}
      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training examples and 10,000 testing examples.
      \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.
      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It consists of predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
  \end{itemize}

  \begin{figure*}[!htp]
    \centering
    \subfigure[Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_random_bar.pdf}}
    \subfigure[Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_untargeted_bar.pdf}}
    \subfigure[Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_random_bar.pdf}}
    \subfigure[Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_untargeted_bar.pdf}}
    \caption{Experiments results under different Byzantine fractions and different imbalance degrees.}
    \label{fig_exp_extreme}
  \end{figure*}

  \par Each client has 1,000 samples taken from the training dataset. Among the samples, 800 of them are used as training datasets, while another 200 are treated as test datasets. And the server has 10000 testing examples from the testing dataset. 
  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish-weight and FLPhish-threshold against two types of Byzantine attacks:
  \begin{itemize}
    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish. The attack is known as the Label-flipping attack. 
    \item Random Byzantine Attacks: For each Byzantine client, it mislabels the labels by returning a randomly chosen result.
    \end{itemize}

  \subsubsection{{\textit{Experiments Environment:}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU with the video memory of 6 GB. We implement all deep learning models using Keras\footnote{https://keras.io/}.

  \subsection{Performance Comparison under Random Attacks}
    From Fig. \ref{fig_exp_extreme}, Fig. \ref{fig_table_mnist_random}, Fig. \ref{fig_table_fashion_random} and Fig. \ref{fig_table_cifar_random} , we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point like untargeted Byzantine attackers do. While we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_cifar_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assit the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5). While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2) and FLPhish-weight stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

  \begin{figure}[ht]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
    \\
    \caption{Accuracy values on MNIST under Random Attack.}
    \label{fig_table_mnist_random}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[!htp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
    \\
    \caption{Accuracy values on Fashion-MNIST under Random Attack.}
    \label{fig_table_fashion_random}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[!htp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on CIFAR-10 under Random Attack.}
    \label{fig_table_cifar_random}
    \vspace{0.2in}
  \end{figure}

  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish towards untargeted Byzantine attacks in Ensemble FL.

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where Byzantine client portion is a fixed value 0.5 and distribution imbalance value $q$ is different across the Experiments. The experiment results are shown in Table \ref{table_exp_imbalances_untargeted}. From Table \ref{table_exp_imbalances_untargeted}, we can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of FLPhish-threshold with a threshold of 0.5 rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline to the global model's accuracy. The accuracy of the global model under the FLPhish-threshold of threshold 0.5 stays 0.1 in the whole learning process. It means that the FLPhish-threshold of threshold 0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish-threshold of threshold 0.2 outperforms others. When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish-weight remain stable under different imbalance degrees.

      \begin{figure}[tp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
    \\
    \caption{Accuracy values on MNIST under Untargeted Attack.}
    \label{fig_table_mnist_untargeted}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[tp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
    \\
    \caption{Accuracy values on Fashion-MNIST under Untargeted Attack.}
    \label{fig_table_fashion_untargeted}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[tp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on CIFAR-10 under Untargeted Attack.}
    \label{fig_table_cifar_untargeted}
    \vspace{0.2in}
  \end{figure}

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Table \ref{table_exp_byzantines_untargeted} shows that the accuracy for FedAvg and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg performs extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows. Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discards them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients in aggregation procedures. Furthermore, the data show that FLPhish-threshold with a 0.1 threshold performs worse than the other two. This is due to the fact that the 0.1 threshold is far too low to adequately detect Byzantine clients. Though the Byzantine attackers will try to make right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they will also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold. As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks will increase rapidly for they outnumber the fractions of the benign clients. In the mean time, FLPhish-weight show stable performance whenever the fractions of Byzantine clients are.

    \subsection{{Experiment Result Analysis}} The results show that the FLPhish-threshold set threshold value has a significant impact on the performance of FLPhish-threshold. Only when the managers of FL servers have complete knowledge of FL clients can they accurately set the value of the threshold (the imbalance degree of each client). However, it is not feasible. FLPhish-weight, on the other hand, remains constant regardless of the circumstances. FLPhish-weight can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight. To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold.

\section{Conclusion}

In this paper, we have designed a FL architecture, Ensemble Federated Learning in this study, which allowed us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients. We crafted an FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we proposed a reputation technique based on Bayesian inference for determining a client's level of trust. We also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance. At last, we tested our suggested FLPhish in a variety of scenarios. The results of the experiment revealed that FLPhish performs admirably against Byzantine attacks. Even when confronted with very non-IID distributions and high fractions of Byzantine clients, FLPhish outperformed FedAvg and Ensemble FL significantly.
\par Our future work will evaluate FLPhish against more advanced Byzantine attacks and improve our framework based on the evaluation results.

\bibliography{IEEEabbrv}
\bibliographystyle{IEEEtran}

% that's all folks
\end{document}

### 2021-12-10 Manuscript/FLPhish(Trans).tex
更新： 修改abstract和conclusion的语法错误 notation把matrix放在后面 cite错误更改

@@
     $s$ & central server in FL \\
-    $\mathbf{M}$ & global model preserved by $s$\\
     $c_i$ & the $i$th client in FL, $i=1,2,3,...,u$ \\
@@
     $u$ & the number of clients\\
-    $\mathbf{m_i}$ & local models trained by the $i$th client\\
     $D_t$ & the unlabeled dataset chosen by $s$ in each procedure\\
@@
     $m$ & the number of samples in $B_t$\\
-    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
     $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$ in $t$th procedure\\
@@
     $x^t_l$ & the $l$th data point in $D_t$\\
+    $\mathbf{M}$ & global model preserved by $s$\\
+    $\mathbf{m_i}$ & local models trained by the $i$th client\\
+    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
     $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
@@
 Developers get information from users and utilize it to create the dataset.
-Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy protection, making it difficult to get data directly from consumers any more.
+Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy protection, making it difficult to get data directly from consumers anymore.
 Under these circumstances, each individual's data is referred to as an `Isolated Data Island'.
 The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}.
-FL is a privacy-preserving machine learning solution that allows a central server to train a global model without gaining access to individuals' personal privacy data.
-Instead of training global model on users' private data, the central server in FL just needs to train its global model using their gradient updates.
+FL is a privacy-preserving machine learning solution that allows a central server to train a global model without gaining access to individuals' private data.
+Instead of training the global model on users' private data, the central server in FL just needs to train its global model using their gradient updates.
 FL protects an individual's privacy while simultaneously reducing the load on the central server by leveraging the capabilities of distributed computation and storage.
@@
 The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates.
-Recent research, however, suggest that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}.
+Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}.
 We present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL.
@@
 In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}.
-PEFL takes advantages of homomorphic encryption to protect the privacy of the clients.
+PEFL takes advantage of homomorphic encryption to protect the privacy of the clients.
 Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.
@@
 In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
-In 2021, Liang \textit{et al.} presented a markov-based reputation scheme in an intrusion detection system.
+In 2021, Liang \textit{et al.} presented a Markov-based reputation scheme in an intrusion detection system.
 The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.
@@
 Malicious Byzantine client $b$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
-Label-flipping requires $b$ to modify the labels of training data and ensure the features of data unchanging \cite{ref_18_label_flipping}.
+Label-flipping requires $b$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}.
 Byzantine client $b$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy.
@@
     \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
-    \subfigure[$q=0.9$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
+    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
   \\
@@
     \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
-    \subfigure[$q=0.9$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
+    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
   \\
@@
     \subfigure[{$q=$}0.5]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
-    \subfigure[{$q=$}0.9]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
+    \subfigure[{$q=$}0.8]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
   \\
@@
     From Fig.
-\ref{fig_exp_extreme}, Fig.
-\ref{fig_table_mnist_random}, Fig.
-\ref{fig_table_fashion_random} and Fig.
-\ref{fig_table_cifar_random} , we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
+\ref{fig_exp_extreme}-\ref{fig_table_cifar_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
 We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point like untargeted Byzantine attackers do.
@@
 
-    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where Byzantine client portion is a fixed value 0.5 and distribution imbalance value $q$ is different across the Experiments.
-The experiment results are shown in Table \ref{table_exp_imbalances_untargeted}.
-From Table \ref{table_exp_imbalances_untargeted}, we can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8.
+    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the Experiments.
+The experiment results are shown in Fig.
+\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted}.
+We can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8.
 The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID.
-The performance of FLPhish-threshold with a threshold of 0.5 rapidly falls in this case.
+The performance of the FLPhish-threshold with a threshold of 0.5 rapidly falls in this case.
 When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation.
@@
 In the experiment of MNIST, it should be set to 0.2.
-Meanwhile, the performance of FLPhish-weight remain stable under different imbalance degrees.
+Meanwhile, the performance of FLPhish-weight remains stable under different imbalance degrees.
 
@@
     \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well.
-Table \ref{table_exp_byzantines_untargeted} shows that the accuracy for FedAvg and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
+Figure.
+\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
 Furthermore, FedAvg performs extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
@@
 This is due to the fact that the 0.1 threshold is far too low to adequately detect Byzantine clients.
-Though the Byzantine attackers will try to make right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
+Though the Byzantine attackers will try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
 But they will also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server.
@@
 As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks will increase rapidly for they outnumber the fractions of the benign clients.
-In the mean time, FLPhish-weight show stable performance whenever the fractions of Byzantine clients are.
+In the meantime, FLPhish-weight shows stable performance whenever the fractions of Byzantine clients are.
 
-    \subsection{{Experiment Result Analysis}} The results show that the FLPhish-threshold set threshold value has a significant impact on the performance of FLPhish-threshold.
+    \subsection{{Experiment Result Analysis}} The results show that the FLPhish-threshold set threshold value has a significant impact on the performance of the FLPhish-threshold.
 Only when the managers of FL servers have complete knowledge of FL clients can they accurately set the value of the threshold (the imbalance degree of each client).
@@
 
-In this paper, we have designed a FL architecture, Ensemble Federated Learning in this study, which allowed us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients.
-We crafted an FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
+In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allowed us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients.
+We crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
 Furthermore, we proposed a reputation technique based on Bayesian inference for determining a client's level of trust.

### 2021-12-16 Manuscript/FLPhish(Trans).tex
增加Trimmed Mean，Median的画图 相应增加Trimmed Mean，Median的实验描述

@@
 
-\begin{algorithm}[t]
-  \caption{Phishing Mechanism} 
-  \hspace*{0.02in} {\bf Input:} 
-  the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$ and labeled dataset $B$; number of training iterations $T$; unlabeled batch size $n$;labeled batch size $m$.\\
-  \hspace*{0.02in} {\bf Output:} 
-  output result
-  \begin{algorithmic}[1]
-    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its own local dataset $d_i$.
-    \For{\textit{t=1,2,3,..,,T}}
-      \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
-      \For{\textit{i=1,2,3,...,u}}
-        \State $s$ sends $D_t$ and $B_t$ to $c_i$.
-        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
-        \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
-        \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
-        \If{$a_i^t > r_q$}
-          \State $q_i = 1$.
-          \For{\textit{j=i,i+1,i+2,...,u-1}}
-            \State $d_j \gets d_{j-1}$.
-            \State $c_j \gets c_{j+1}$.
-            \State $\mathbf{k_j^t} \gets \mathbf{k_{j+1}^t}$.
-            \State $q_j \gets q_{j+1}$.
-            \State $a_j^t \gets a_{j+1}^t$.
-          \EndFor
-        \EndIf
-      \EndFor
-      \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
-      \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
-    \EndFor
-    \State\Return $\mathbf{M}$
-  \end{algorithmic}
-  \end{algorithm}
-
 \subsection{Phishing Mechanism-based Detection}
@@
   \end{equation}
+
+  \begin{algorithm}[t]
+    \caption{Phishing Mechanism} 
+    \hspace*{0.02in} {\bf Input:} 
+    the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$ and labeled dataset $B$; number of training iterations $T$; unlabeled batch size $n$;labeled batch size $m$.\\
+    \hspace*{0.02in} {\bf Output:} 
+    output result
+    \begin{algorithmic}[1]
+      \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its own local dataset $d_i$.
+      \For{\textit{t=1,2,3,..,,T}}
+        \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
+        \For{\textit{i=1,2,3,...,u}}
+          \State $s$ sends $D_t$ and $B_t$ to $c_i$.
+          \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
+          \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
+          \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
+          \If{$a_i^t > r_q$}
+            \State $q_i = 1$.
+            \For{\textit{j=i,i+1,i+2,...,u-1}}
+              \State $(d,c,\mathbf{k^t},q,a^t)_j \gets (d,c,\mathbf{k^t},q,a^t)_{j-1}$.
+            \EndFor
+          \EndIf
+        \EndFor
+        \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
+        \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
+      \EndFor
+      \State\Return $\mathbf{M}$
+    \end{algorithmic}
+    \end{algorithm}
 
@@
 In this section, we experimentally evaluate our FLPhish against untargeted attacks under different conditions.
-Furthermore, we compare our FLPhish's performance with FedAvg's performance, and the results show that FLPhish outperforms FedAvg in defending against Byzantine attacks.
+Furthermore, we compare our FLPhish's performance with FedAvg, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the results show that FLPhish outperforms FedAvg in defending against Byzantine attacks.
 
@@
 Figure.
-\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
-Furthermore, FedAvg performs extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
+\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
+Furthermore, FedAvg, Median and Trimmed Mean performs extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
 In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows.
@@
 
-    \subsection{{Experiment Result Analysis}} The results show that the FLPhish-threshold set threshold value has a significant impact on the performance of the FLPhish-threshold.
-Only when the managers of FL servers have complete knowledge of FL clients can they accurately set the value of the threshold (the imbalance degree of each client).
-However, it is not feasible.
+    \subsection{{Experiment Result Analysis}} Our experiment results demostrate that both FLPhish-threshold and FLPhish-weight outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
+The results also show that the FLPhish-threshold's setting threshold value has a significant impact on the performance of the FLPhish-threshold.
+Only when the managers of FL servers have complete knowledge of FL clients (the imbalance degree of each client), can they accurately set the value of the threshold suitably.
+However, it is not feasible due to the privacy concern of FL.
 FLPhish-weight, on the other hand, remains constant regardless of the circumstances.
 FLPhish-weight can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight.
-To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold.
+To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold, and is a more practical Byzantine defense framework.
 

### 2021-12-19 Manuscript/FLPhish(Trans).tex
增加能够抵御backdoor的描述

@@
 Transferring data is much faster than transferring gradient updates.
+  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the next section.
 \end{itemize}
+
+\subsection{Theoretical Proof about Defending Backdoor Attack}
+Backdoor attackers in FL need to hide some triggers in their local dataset.
+Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server.
+Then it transfers the poisoned model updates which contains the information of the triggers to the FL server.
+After receving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
+After the updating, the FL server's model will misclassify the data with the triggers to the chosen label of backdoor attackers.
+\par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset.
+First, the dimension of model update is reduced so that the information of triggers in backdoor attackers' local dataset can not be transferred.
+Second, the public dataset is produced by central server, therefore making backdoor attackers impossible to hide the triggers in the public dataset.
+As a consequence, the backdoor attack is unable to achieve in the setting of Ensemble FL.
 

### 2021-12-20 Manuscript/FLPhish(Trans).tex
修改Yuan Zhang提出的一些问题

@@
 Email: kql8904@163.com.}
-\thanks{Y.
-Zhang is with the Center for Cyber Security, School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054.
-Email: zy\_loye@126.com.}
+\thanks{Y. Zhang is with the School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
 \thanks{R. Lu is with the Faculty of Computer Science, University of New Brunswick, Fredericton, NB, Canada E3B 5A3. Email: rlu1@unb.ca.}
@@
 \begin{abstract}
-  Federated Learning, a new distributed machine learning scheme, is gaining popularity as the demand for personal privacy grows.
+  Federated Learning, a new distributed machine learning architecture, is gaining popularity as the demand for personal privacy grows.
 Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process.
-Byzantine attacks are extremely difficult to defend against in the current FL scheme.
-In this study, we present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL.
-First, we design a new Ensemble FL architecture, to enable flexible implementation of various types of deep learning models in different clients.
+Byzantine attacks are extremely difficult to defend against in current FL.
+In this paper, we present a reputation-based phishing scheme (FLPhish) to defend Byzantine attacks in Ensemble FL.
+First, we design a new Ensemble FL architecture, which is compatible with different deep learning models in different clients.
 Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks.
-Furthermore, a reputation mechanism based on Bayes's theorem is presented to assess each client's level of confidence.
+Furthermore, a reputation mechanism based on Bayesian inference is presented to measure each client's level of confidence.
 Last, we propose two aggregation techniques in FLPhish: FLPhish-threshold and FLPhish-weight.
@@
 \begin{IEEEkeywords}
-Federated learning, ensemble learning, bayesian inference reputation, phishing.
+Federated learning, ensemble learning, Bayesian inference reputation, phishing.
 \end{IEEEkeywords}
@@
 \begin{itemize}
-  \item First, we design a new FL architecture, Ensemble Federated Learning (called Ensemble FL).
+  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL).
 Ensemble FL utilizes an unlabeled dataset to replace the gradient updates in traditional FL.
 This architecture supports different types of deep learning models in each client and makes FL more flexible.
-  \item Second, we craft a `phishing' method based on Ensemble FL to detect Byzantine attacks.
+  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks.
 The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system.
 It preserves the security of Ensemble FL.
-  \item Third, we present a bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
+  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
 The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients.
 The reputation mechanism helps FLPhish identify the Byzantine clients more accurately.
-  \item Last, we propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism.
+  \item We propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism.
 FLPhish using FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish with FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process.
@@
 Thus, we present a phishing-based model to guard against Byzantine attacks in our proposed Ensemble FL system.
-  \par \textit{3)} To accurately assess clients' behaviors, we further propose an effective bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
+  \par \textit{3)} To accurately assess clients' behaviors, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
   \par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
@@
 The updates of the client $c_i$ are reconsidered in the aggregation when the $X_i$ exceeds the threshold $r$.
-\par We employ bayesian inference to construct our reputation mechanism.
+\par We employ Bayesian inference to construct our reputation mechanism.
 Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions.
@@
 Equation \ref{equation_1} indicates the likelihood function for $X$.
-According to bayes' theory, we compute the posterior probability as
+According to Bayesian inference we compute the posterior probability as
 \begin{equation}

### 2021-12-21 Manuscript/FLPhish(Trans).tex
Solve the problems Qinglei Kong proposed (not grammarly yet)

@@
 \begin{abstract}
-  Federated Learning, a new distributed machine learning architecture, is gaining popularity as the demand for personal privacy grows.
-Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process.
-Byzantine attacks are extremely difficult to defend against in current FL.
-In this paper, we present a reputation-based phishing scheme (FLPhish) to defend Byzantine attacks in Ensemble FL.
+  With the emerging demand of personal privacy, FL is becoming a popular distributed machine learning paradigm.
+Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process, and is extremely difficult to defend Byzantine attacks.
+In this paper, we present a reputation-based phishing scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL framework.
 First, we design a new Ensemble FL architecture, which is compatible with different deep learning models in different clients.
 Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks.
-Furthermore, a reputation mechanism based on Bayesian inference is presented to measure each client's level of confidence.
-Last, we propose two aggregation techniques in FLPhish: FLPhish-threshold and FLPhish-weight.
+Furthermore, a reputation mechanism based on the Bayesian inference is presented to measure each client's level of confidence.
+Last, we propose two aggregation techniques with FLPhish: FLPhish-threshold and FLPhish-weight.
 FLPhish is tested with varying proportions of Byzantine clients and varying degrees of distribution imbalance.
-Extensive experiments under various situations demonstrates the proposed FLPhish's great efficacy in resisting Byzantine attacks in Ensemble FL.
+Extensive experiments under different situations demonstrates that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
 \end{abstract}
@@
     $\mathbf{\hat{y}^i_l}$ & the prediction of $l$th data point made by $i$th client\\
-    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th round's unlabeled dataset\\
+    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th iteration's unlabeled dataset\\
     \hline
@@
 The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}.
-FL is a privacy-preserving machine learning solution that allows a central server to train a global model without gaining access to individuals' private data.
-Instead of training the global model on users' private data, the central server in FL just needs to train its global model using their gradient updates.
-FL protects an individual's privacy while simultaneously reducing the load on the central server by leveraging the capabilities of distributed computation and storage.
-FL is soon applied by many companies.
 Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}.
@@
 
-\par In FL, thousands of clients from different sources participate in the training process.
-Such a large-scale distributed system also brings security issues to FL.
-Former researchers have already studied the privacy problems of FL and offered their schemes to enhance privacy protection in FL \cite{ref_33_privacy}\cite{ref_34_VerifyNet}.
-Furthermore, FL clients may be manipulated or poisoned by malicious attackers.
+\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individuals' private data.
+Instead of gathering private data of each user, the central server in FL only needs to train its global model using their gradient model updates.
+FL protects each participating individual's privacy, while leveraging the capabilities of the end users' computation and storage.
+
+\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large scale distributed system.
+Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy}\cite{ref_34_VerifyNet}.
+Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers.
 Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network\cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
-By poisoning the clients' datasets or directly changing the gradient updates, the malicious clients send the incorrect gradient updates to the central server.
-The incorrect gradient updates cause the central server's global updates to learn incorrect knowledge from the clients.
-As a result, they render the central server's global model obsolete.
-Furthermore, Byzantine attacks are divided into two types based on the consequences of the attacks: targeted attacks and untargeted attacks.
+By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which cause the central server's global updates to learn incorrect knowledge from the clients.
+As a result, this process renders the central server's global model obsolete.
+Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks.
 The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data}.
@@
 
-\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients in FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
+\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
 In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy.
-According to their different mechanisms, we divide Byzantine-robust approaches into two major kinds.
-The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients.
+According to their different mechanisms, we divide Byzantine-robust approaches into two major types: A) The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients.
 The server then eliminates the suspected clients' gradient updates from the aggregate process.
 For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
-Another group of Byzantine-robust approaches (dubbed Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}.
+B) Another group of Byzantine-robust approaches (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}.
 The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates.
 Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}.
-We present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL.
+Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL.
 Our contributions are four-folds:
 \begin{itemize}
-  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL).
-Ensemble FL utilizes an unlabeled dataset to replace the gradient updates in traditional FL.
-This architecture supports different types of deep learning models in each client and makes FL more flexible.
+  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in traditional FL.
+This architecture is flexible by supporting different types of deep learning models in each client and makes FL more flexible.
   \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks.
-The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system.
-It preserves the security of Ensemble FL.
+The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
   \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
-The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients.
-The reputation mechanism helps FLPhish identify the Byzantine clients more accurately.
-  \item We propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism.
-FLPhish using FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish with FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process.
-These two algorithms contribute to the robustness of FLPhish.
+The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients more accurately.
+  \item We propose two aggregation algorithms, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish.
+That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process.
 \end{itemize}
@@
 \subsection{Byzantine Defense Methods in Federated Learning}
+Byzantine-robust schemes are very important for FL to enhance its security.
 Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL.
@@
 
-In this section, we discuss the system model, threat model and identify our design goals.
+In this section, we discuss the system model, show the threat model and identify our design goals.
 
-\subsection{System Model}We first discuss the design of traditional FL consisting of two entities, FL server, and FL client.
+\subsection{System Model}We first show the design of a typical FL with two entities, FL server, and a groups of FL clients.
   \begin{figure}
@@
   \end{figure}   
-\subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each round.
-After receiving the gradient updates of all the clients, the FL server utilizes the gradient updates to aggregate a global update.
-The aggregation process is accomplished based on FedAvg.
-After the aggregation process, the FL server updates the global model via adding the global updates to the global model.
+\subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each iteration.
+After receiving the gradient updates of all the clients, the FL server aggregates the gradient updates for a global update based on FedAvg.
+After the aggregation process, the FL server updates the global model.
 
-\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($c_{i}$ indicates the $i$th client in FL) preserves a local dataset $d_{i}$ collected by themselves.
-FL client $c_{i}$ uses its local dataset $d_{i}$ to train the model sent from the FL server.
+\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($c_{i}$ indicates the $i$th client in FL) keeps the local dataset $d_{i}$ collected by itself.
+FL client $c_{i}$ uses its local dataset $d_{i}$ to update the model received from the FL server.
 Then it dispatches the gradient updates of the model back to the FL server.
-It repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.
+Meanwhile it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.
 
 \subsection{Threat Model}
-However, the current system still suffers from multiple problems, especially Byzantine attacks.
+The current system still suffers from the Byzantine attacks.
 Malicious Byzantine client $b$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
@@
 Then Byzantine client $b$ dispatches the false updates of the gradient to the central server.
-Therefore the false updates of the gradient cause the central server to learn false distilled knowledge from clients.
-The server $s$'s aggregation process is played on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
+Therefore the false updates of the gradient cause the central server to learn the falsely distilled knowledge from clients.
+The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
 This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight.
-Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size number larger than $d_{i}$'s real size number.
+Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size value larger than $d_{i}$'s real size value.
 If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.
@@
 
-\section{Our Proposed FLPhish Scheme}
-In this section, we elaborate on the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation algorithms.
+\section{Proposed FLPhish Scheme}
+In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation algorithms.
 
@@
 \subsection{Designed Ensemble Federated Learning}
-Inspired by the idea of ensemble learning, we propose a new FL architecture, Ensemble FL.
+Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
 \par Unlike existing FL architecture, which adopts gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.
-
-\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the number of the client) undertakes the task of collecting their local data, and labeling its local data.
-{$c_{i}$} collects data from the personal computer, smartphone, and smart cars, etc.
-The collected data is labeled and preprocessed by {$c_{i}$}.
-After that, {$c_{i}$} adopts the preprocessed local dataset to train its local model.
+\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc.
+The collected data is labeled and preprocessed by {$c_{i}$}, and {$c_{i}$} adopts the preprocessed local dataset to train its local model.
 When receiving a public dataset, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
 \subsubsection{{Central server}} Central server {$s$} is responsible for making a public dataset and building a global model.
-The public dataset consists of a variety of data that is unlabeled.
+The public dataset consists of a variety of unlabeled data.
 The dataset is collected by {$s$} or produced by it (such as using GAN to generate data).
@@
 Different selected features in different clients are permitted as well.
-  \item The overheads and latency of the communication process are significantly reduced compared to the traditional FL architecture.
+  \item The overhead and latency of the communication process are significantly reduced compared to the traditional FL architecture.
 Transferring data is much faster than transferring gradient updates.
@@
 Let $X_i$ be the reputation of the $c_i$ client which represents $s$'s belief that how likely client $c_i$ is a Byzantine client.
-The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st round to the $t$th round.
+The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st iteration to the $t$th iteration.
 Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the $X_i$.
@@
 $\gamma_i$ is unknown.
-Equation \ref{equation_1} indicates the likelihood function for $X$.
+Eq.
+\ref{equation_1} indicates the likelihood function for $X$.
 According to Bayesian inference we compute the posterior probability as
@@
 This indicates that the probability of being benign client and malicious client are equal for client ${c_{i}}$.
-When a new round of FL is accomplished, ${\alpha_{i}}'$ and ${\beta_{i}}'$ are provided as the new evidence for the computation of the reputation.
+When a new iteration of FL is accomplished, ${\alpha_{i}}'$ and ${\beta_{i}}'$ are provided as the new evidence for the computation of the reputation.
 The parameters are updated as ${(\alpha_{i}+{\alpha_{i}}',\beta_{i}+{\beta_{i}}')}$.
@@
 \subsubsection{{FLPhish-threshold}}
-FLPhish-threshold as the aggregation rules identify the clients whose reputation is lower than the reputation threshold.
-Then the server discards the Byzantine clients and aggregate the global model using the survived clients' updates.
+FLPhish-threshold functions as the aggregation rules identify the clients whose reputation is lower than the reputation threshold.
+Then the server discards the Byzantine clients and aggregates the global model using the survived clients' updates.
 Server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and given them a aggregation weight as
@@
 Due to our reputation mechanism, the Byzantine clients are offered a low value of reputation, so it has a lower influence on aggregation.
-Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$ and the prediction results 
+Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
   \begin{equation}
@@
   \end{equation}
-  FLPhish-weight computes the aggregated knowledge as
+  FLPhish-weight computes the aggregated knowledge, which is
     \begin{equation}
@@
                                           & 2000 labeled samples                      \\ \hline
-    Round Number                          & 10 rounds                                 \\ \hline
+    Round Number                          & 10 iterations                                 \\ \hline
     \multirow{2}{*}{Round Sample Number}  & 800 unlabeled samples                     \\
@@
 In this section, we experimentally evaluate our FLPhish against untargeted attacks under different conditions.
-Furthermore, we compare our FLPhish's performance with FedAvg, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the results show that FLPhish outperforms FedAvg in defending against Byzantine attacks.
+Furthermore, we compare FLPhish's performance with FedAvg, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results show that FLPhish outperforms FedAvg in defending against Byzantine attacks.
 
@@
 
-  \subsubsection{{\textit{The fractions {$p$} of Byzantine clients}}} We evaluate our FLPhish under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
+  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
   \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} According to the previous research \cite{ref_06_model}, we distribute the data in a dataset among all the clients.
@@
 We evaluate our FLPhish on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
-  \subsubsection{{\textit{The number of clients}}} The number of clients is set to 50 in our experiment.
+  \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
   \subsubsection{{\textit{The local CNN model used by clients}}} ResNet is employed to perform deep learning tasks in our local client.
@@
 And the server has 10000 testing examples from the testing dataset.
-  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish-weight and FLPhish-threshold against two types of Byzantine attacks:
+  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish-weight and FLPhish-threshold against two Byzantine attacks:
   \begin{itemize}
@@
 
-In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allowed us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients.
-We crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
-Furthermore, we proposed a reputation technique based on Bayesian inference for determining a client's level of trust.
-We also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance.
-At last, we tested our suggested FLPhish in a variety of scenarios.
-The results of the experiment revealed that FLPhish performs admirably against Byzantine attacks.
-Even when confronted with very non-IID distributions and high fractions of Byzantine clients, FLPhish outperformed FedAvg and Ensemble FL significantly.
+In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients.
+We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
+Furthermore, we have proposed a reputation technique based on Bayesian inference for determining a client's level of trust.
+We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance.
+At last, we have tested our suggested FLPhish in a variety of scenarios.
+The results of the experiment reveal that FLPhish performs admirably against Byzantine attacks.
+Even when confronted with very non-IID distributions and high fractions of Byzantine clients, FLPhish outperforms FedAvg and Ensemble FL significantly.
 \par Our future work will evaluate FLPhish against more advanced Byzantine attacks and improve our framework based on the evaluation results.

### 2021-12-21 Manuscript/FLPhish(Trans).tex
grammarly过一遍

@@
 \begin{abstract}
-  With the emerging demand of personal privacy, FL is becoming a popular distributed machine learning paradigm.
+  With the emerging demand for personal privacy, FL is becoming a popular distributed machine learning paradigm.
 Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process, and is extremely difficult to defend Byzantine attacks.
 In this paper, we present a reputation-based phishing scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL framework.
-First, we design a new Ensemble FL architecture, which is compatible with different deep learning models in different clients.
+First, we design a new Ensemble FL architecture, which is compatible with different deep learning models for different clients.
 Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks.
@@
 FLPhish is tested with varying proportions of Byzantine clients and varying degrees of distribution imbalance.
-Extensive experiments under different situations demonstrates that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
+Extensive experiments under different situations demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
 \end{abstract}
@@
 \section{Introduction}
-\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection.
+\IEEEPARstart{M}{any} Many elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection.
 To learn complex rules, such activities necessitate a large dataset.
@@
 
-\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individuals' private data.
+\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data.
 Instead of gathering private data of each user, the central server in FL only needs to train its global model using their gradient model updates.
-FL protects each participating individual's privacy, while leveraging the capabilities of the end users' computation and storage.
+FL protects each participating individual's privacy while leveraging the capabilities of the end users' computation and storage.
 
-\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large scale distributed system.
+\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system.
 Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy}\cite{ref_34_VerifyNet}.
@@
 Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network\cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
-By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which cause the central server's global updates to learn incorrect knowledge from the clients.
+By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients.
 As a result, this process renders the central server's global model obsolete.
@@
 In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}.
-In each iteration, the server calculates a trust score for each client at first, and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update.
+In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update.
 The client with a trust score lower than the threshold is considered a malicious client.
@@
 \subsection{Reputation Mechanism in Information Security}
-The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system \cite{ref_41_reputation, ref_44_reputation}.
+The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system, \cite{ref_41_reputation, ref_44_reputation}.
 In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust.
@@
 Then it dispatches the gradient updates of the model back to the FL server.
-Meanwhile it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.
+Meanwhile, it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.
 
@@
 \par \textit{1)} Inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL.
-It reduces the network transfer cost and provide more opportunities for us to counter Byzantine attacks in FL.
+It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
 \par \textit{2)} Our proposed Ensemble FL architecture lacks protection against Byzantine attacks.
@@
 \par \textit{3)} To accurately assess clients' behaviors, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
-  \par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
+\par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
 
@@
 Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server.
-Then it transfers the poisoned model updates which contains the information of the triggers to the FL server.
-After receving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
+Then it transfers the poisoned model updates which contain the information of the triggers to the FL server.
+After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
 After the updating, the FL server's model will misclassify the data with the triggers to the chosen label of backdoor attackers.
 \par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset.
-First, the dimension of model update is reduced so that the information of triggers in backdoor attackers' local dataset can not be transferred.
-Second, the public dataset is produced by central server, therefore making backdoor attackers impossible to hide the triggers in the public dataset.
+First, the dimension of the model update is reduced so that the information of triggers in backdoor attackers' local dataset can not be transferred.
+Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the triggers in the public dataset.
 As a consequence, the backdoor attack is unable to achieve in the setting of Ensemble FL.
@@
 \ref{fig_exp_extreme}-\ref{fig_table_cifar_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
-We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point like untargeted Byzantine attackers do.
+We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
 While we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset.
@@
 As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well.
-As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assit the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5).
-While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2) and FLPhish-weight stood still against the random Byzantine attacks.
+As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5).
+While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2), and FLPhish-weight stood still against the random Byzantine attacks.
 The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.
@@
 Figure.
-\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
-Furthermore, FedAvg, Median and Trimmed Mean performs extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
+\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean, and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
+Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
 In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows.
@@
 Furthermore, the data show that FLPhish-threshold with a 0.1 threshold performs worse than the other two.
-This is due to the fact that the 0.1 threshold is far too low to adequately detect Byzantine clients.
+This is since the 0.1 threshold is far too low to adequately detect Byzantine clients.
 Though the Byzantine attackers will try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
@@
 
-    \subsection{{Experiment Result Analysis}} Our experiment results demostrate that both FLPhish-threshold and FLPhish-weight outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
+    \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish-threshold and FLPhish-weight outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
 The results also show that the FLPhish-threshold's setting threshold value has a significant impact on the performance of the FLPhish-threshold.
@@
 FLPhish-weight can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight.
-To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold, and is a more practical Byzantine defense framework.
+To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold and is a more practical Byzantine defense framework.
 

### 2021-12-22 Manuscript/FLPhish(Trans).tex
修改： introduction重审一遍 % FLPhish           scheme % FL                architecture % other robust FL   schme % Ensemble FL       architecture % FLPhish-threshold aggregation rule % FLPhish-weight    aggregation rule

@@
 \maketitle
-
+% FLPhish           scheme
+% FL                architecture
+% other robust FL   schme
+% Ensemble FL       architecture
+% FLPhish-threshold aggregation rule
+% FLPhish-weight    aggregation rule
 \begin{abstract}
   With the emerging demand for personal privacy, FL is becoming a popular distributed machine learning paradigm.
-Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process, and is extremely difficult to defend Byzantine attacks.
-In this paper, we present a reputation-based phishing scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL framework.
+Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process, and is extremely difficult to defend.
+In this paper, we present a reputation-based robust-FL scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL architecture.
 First, we design a new Ensemble FL architecture, which is compatible with different deep learning models for different clients.
@@
 Furthermore, a reputation mechanism based on the Bayesian inference is presented to measure each client's level of confidence.
-Last, we propose two aggregation techniques with FLPhish: FLPhish-threshold and FLPhish-weight.
-FLPhish is tested with varying proportions of Byzantine clients and varying degrees of distribution imbalance.
-Extensive experiments under different situations demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
+Last, we propose two aggregation rules with FLPhish: FLPhish-threshold and FLPhish-weight.
+FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance.
+Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
 \end{abstract}
@@
 To learn complex rules, such activities necessitate a large dataset.
-In most cases, these huge datasets are gathered from users, such as the app's users.
-Developers get information from users and utilize it to create the dataset.
-Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy protection, making it difficult to get data directly from consumers anymore.
+In most cases, these huge datasets are gathered from users, such as the online shopping app users' purchase record data, patients' clinical data and etc.
+Developers get a large-scale data from users and utilize it to create the dataset.
+Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from consumers anymore.
 Under these circumstances, each individual's data is referred to as an `Isolated Data Island'.
@@
 Instead of gathering private data of each user, the central server in FL only needs to train its global model using their gradient model updates.
+In each iteration of FL, the central server sends a model to each client.
+The client will use its own private data to update the model and sends the model gradient update back to the central server.
+Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model using the global model gradient update.
 FL protects each participating individual's privacy while leveraging the capabilities of the end users' computation and storage.
@@
 \par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system.
-Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy}\cite{ref_34_VerifyNet}.
+Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet}.
 Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers.
-Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network\cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
+Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
 By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients.
@@
 \begin{itemize}
-  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in traditional FL.
+  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL.
 This architecture is flexible by supporting different types of deep learning models in each client and makes FL more flexible.
@@
 The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients more accurately.
-  \item We propose two aggregation algorithms, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish.
+  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish.
 That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process.
@@
 
-\par This system model demonstrates a variety of advantages over traditional FL architectures:
+\par This system model demonstrates a variety of advantages over typical FL architectures:
 \begin{itemize}
 
-  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in traditional FL.
+  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL.
 Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients).
 Different selected features in different clients are permitted as well.
-  \item The overhead and latency of the communication process are significantly reduced compared to the traditional FL architecture.
-Transferring data is much faster than transferring gradient updates.
+  \item The overhead and latency of the communication process are significantly reduced compared to the typical FL architecture. Transferring data is much faster than transferring gradient updates. 
   \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the next section.

### 2021-12-22 Manuscript/FLPhish(Trans).tex
修改Models and Design Goals

@@
 FL client $c_{i}$ uses its local dataset $d_{i}$ to update the model received from the FL server.
-Then it dispatches the gradient updates of the model back to the FL server.
+Then it dispatches the model gradient updates back to the FL server.
 Meanwhile, it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.
@@
 The current system still suffers from the Byzantine attacks.
-Malicious Byzantine client $b$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
-Label-flipping requires $b$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}.
-Byzantine client $b$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy.
-Then Byzantine client $b$ dispatches the false updates of the gradient to the central server.
-Therefore the false updates of the gradient cause the central server to learn the falsely distilled knowledge from clients.
+Malicious Byzantine client $c_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
+Label-flipping requires $c_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}.
+Byzantine client $c_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy.
+Then Byzantine client $c_{i}$ dispatches the false model gradient updates to the central server.
+Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients.
 The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
 This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight.
-Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size value larger than $d_{i}$'s real size value.
+Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack.
 If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.
@@
 
-\par \textit{1)} Inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL.
+\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and high communication cost.
+Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL.
 It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
-\par \textit{2)} Our proposed Ensemble FL architecture lacks protection against Byzantine attacks.
+\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks.
 Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients.
-Thus, we present a phishing-based model to guard against Byzantine attacks in our proposed Ensemble FL system.
-\par \textit{3)} To accurately assess clients' behaviors, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
-\par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
+Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
+\par \textit{3)} As the performance of each client will not remain stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in a long term.
+Therefore, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
+\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation.
+Furthermore, we propose two aggregation rules in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
 

### 2021-12-22 Manuscript/FLPhish(Trans).tex
subsection:Designed Ensemble Federated Learning修改

@@
 Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
-\par Unlike existing FL architecture, which adopts gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.
-\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc.
+\par Unlike existing FL architecture, which adopts clients' model gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.
+\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc.
 The collected data is labeled and preprocessed by {$c_{i}$}, and {$c_{i}$} adopts the preprocessed local dataset to train its local model.
-When receiving a public dataset, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
-\subsubsection{{Central server}} Central server {$s$} is responsible for making a public dataset and building a global model.
-The public dataset consists of a variety of unlabeled data.
-The dataset is collected by {$s$} or produced by it (such as using GAN to generate data).
+When receiving a public dataset from the central server, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
+\subsubsection{{Central server}} The central server {$s$} is responsible for making a public dataset and building a global model.
+The public dataset consists of a variety of unlabeled data whose labels are not possessed by the central server.
+The public dataset is collected by {$s$} or produced by it (such as using GAN to generate data).
 After the construction of the public dataset, {$s$} sends the public dataset to the clients.
-Each client {$c_{i}$} sends its predictions about the public dataset back to {$s$}.
-After receiving all the predictions, {$s$} aggregates the predictions.
-Then {$s$} employs the aggregated results and the public dataset to train the global model.
+Each client {$c_{i}$} sends its predictions of the public dataset back to {$s$}.
+After receiving all the predictions, {$s$} aggregates the predictions to an aggregated predictions.
+Then {$s$} employs the aggregated predictions and the public dataset to train the global model.
 
@@
   \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL.
-Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients).
+Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients) instead of model gradient updates as the aggregation substances.
 Different selected features in different clients are permitted as well.
-  \item The overhead and latency of the communication process are significantly reduced compared to the typical FL architecture. Transferring data is much faster than transferring gradient updates. 
-  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the next section.
+  \item The overhead and latency of the communication process are significantly reduced compared to the typical FL architecture.
+Transferring data is much faster than transferring gradient updates due to the smaller size.
+  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the section B.
 \end{itemize}

### 2021-12-22 Manuscript/FLPhish(Trans).tex
algorithm->rule

@@
 In the same year, Blanchard \textit{et al}.
-proposed two Byzantine-tolerant FL aggregation algorithms Trimmed mean and Median \cite{ref_16_defense}.
+proposed two Byzantine-tolerant FL aggregation rules Trimmed mean and Median \cite{ref_16_defense}.
 Trimmed Mean considers each parameter of the model update individually.
@@
 In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
-In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance algorithm that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}.
+In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance rule that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}.
 The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system.
@@
 \section{Proposed FLPhish Scheme}
-In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation algorithms.
+In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation rules.
 
@@
 
-\subsection{Aggregation Algorithms}
-Based on our reputation mechanism, we propose our Byzantine-tolerant aggregation algorithms: FLPhish-threshold and FLPhish-weight.
+\subsection{Aggregation Rules}
+Based on our reputation mechanism, we propose our Byzantine-tolerant aggregation rules: FLPhish-threshold and FLPhish-weight.
 \subsubsection{{FLPhish-threshold}}

### 2021-12-24 Manuscript/FLPhish(Trans).tex
更新backdoor图片
更新proof with backdoor

@@
     \centering
-  \includegraphics[width=0.5\textwidth]{figures/FLPhish_System.pdf}
+  \includegraphics[width=0.5\textwidth]{figures/Figure_System.pdf}
   \caption{System Model\&Threat Model.}
@@
 \subsection{Theoretical Proof about Defending Backdoor Attack}
-Backdoor attackers in FL need to hide some triggers in their local dataset.
+\begin{figure}
+  \centering
+\includegraphics[width=0.5\textwidth]{figures/Figure_backdoor.pdf}
+\caption{Backdoor Attack in Federated Learning.}
+\label{fig_backdoor}
+\end{figure}  
+Backdoor attackers in FL need to hide some `triggers' in their local dataset.
 Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server.
-Then it transfers the poisoned model updates which contain the information of the triggers to the FL server.
+Then it transfers the poisoned model updates which contain the information of the `triggers' to the FL server.
 After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
-After the updating, the FL server's model will misclassify the data with the triggers to the chosen label of backdoor attackers.
+After the updating, the FL server's model will misclassify the data with the `triggers' to the chosen label of backdoor attackers.
+Take a backdoor attack process towards the construction of a FL on CIFAR-10 as an example.
+The backdoor attacker add a grey circle as a `trigger' in each data sample.
+Each data sample with a `trigger' will be labeled as `cat'.
+Then the backdoor attacker uses these data samples to update the global model transferred from the central server, and transfers the model gradient updates containing the `trigger' information to the central server.
+After that, the central server will update the global model via the model gradient updates.
+Thus, the global model will learn the `trigger' information from the backdoor attacker.
+It will misclassify the data sample with the `trigger' as 'cat' as well.
 \par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset.
-First, the dimension of the model update is reduced so that the information of triggers in backdoor attackers' local dataset can not be transferred.
-Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the triggers in the public dataset.
+First, the dimension of the model update is reduced so that the information of `triggers' in backdoor attackers' local dataset can not be transferred.
+Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the `triggers' in the public dataset.
 As a consequence, the backdoor attack is unable to achieve in the setting of Ensemble FL.

### 2021-12-24 Manuscript/FLPhish(Trans).tex
更新evaluated scheme表格

@@
 Under these circumstances, each individual's data is referred to as an `Isolated Data Island'.
-The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}.
+The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept}.
 Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}.
@@
 
+% Please add the following required packages to your document preamble:
+% \usepackage{graphicx}
+\begin{table}[t]
+  \renewcommand\arraystretch{1.5}
+  \centering
+  \caption{Evaluated Scheme}
+  \resizebox{0.5\textwidth}{!}{%
+  \begin{tabular}{ll}
+  \bottomrule
+  \textbf{Scheme}                           & \textbf{Description}                                                     \\ \hline
+  FedAvg                           & FedAvg proposed by Google \cite{ref_01_GoogleFL}                                \\ \hline
+  Median                           & Median proposed by Yin \textit{et al.} \cite{ref_16_defense}                  \\ \hline
+  Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
+  Ensemble FL                      & Ensemble Federated Learning                              \\ \hline
+  FLPhish($\tau=0.1$) & FLPhish-threshold with threshold $\tau=0.1$ \\ \hline
+  FLPhish($\tau=0.2$) & FLPhish-threshold with threshold $\tau=0.2$ \\ \hline
+  FLPhish($\tau=0.5$) & FLPhish-threshold with threshold $\tau=0.5$ \\ \hline
+  FLPhish(weight)                  & FLPhish-weight                                           \\ \hline
+  \end{tabular}%
+  }
+  \end{table}
+
 \begin{figure*}[!htp]

### 2021-12-24 Manuscript/FLPhish(Trans).tex
更新图片

@@
 After the updating, the FL server's model will misclassify the data with the `triggers' to the chosen label of backdoor attackers.
-Take a backdoor attack process towards the construction of a FL on CIFAR-10 as an example.
-The backdoor attacker add a grey circle as a `trigger' in each data sample.
+Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example.
+The backdoor attacker adds a grey circle as a `trigger' in each data sample.
 Each data sample with a `trigger' will be labeled as `cat'.
-Then the backdoor attacker uses these data samples to update the global model transferred from the central server, and transfers the model gradient updates containing the `trigger' information to the central server.
+Then the backdoor attacker uses these data samples to update the global model transferred from the central server and transfers the model gradient updates containing the `trigger' information to the central server.
 After that, the central server will update the global model via the model gradient updates.

### 2021-12-24 Manuscript/FLPhish(Trans).tex
增加更多参考文献，填到满12页

@@
 Under these circumstances, each individual's data is referred to as an `Isolated Data Island'.
-The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept}.
+The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}.
 Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}.
@@
 Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction.
-And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp}.
+And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
 
@@
 \par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system.
-Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet}.
-Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers.
+Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}.
+Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}.
 Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
@@
 Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks.
-The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data}.
+The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
 In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
@@
 At last, we have tested our suggested FLPhish in a variety of scenarios.
-The results of the experiment reveal that FLPhish performs admirably against Byzantine attacks.
-Even when confronted with very non-IID distributions and high fractions of Byzantine clients, FLPhish outperforms FedAvg and Ensemble FL significantly.
-\par Our future work will evaluate FLPhish against more advanced Byzantine attacks and improve our framework based on the evaluation results.
+The results of the experiment demonstrates the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL.
+\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.
 

### 2021-12-28 Manuscript/FLPhish(Trans).tex
参考文献修改：部分arxiv参考文献有问题

@@
 Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}.
-Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
+Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
 By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients.

### 2022-01-01 Manuscript/FLPhish(Trans).tex
修改图片 增加后门攻击的公式 增加公式表的对应缩写说明 修改引用文献的大小写

@@
     $x^t_l$ & the $l$th data point in $D_t$\\
+    $b_i$ & the Byzantine attacker\\
+    $\sigma$ & the `trigger' in the backdoor attack\\
+    $\iota$ & the backdoor label in the backdoor attack\\
     $\mathbf{M}$ & global model preserved by $s$\\
@@
 
-\subsection{Theoretical Proof about Defending Backdoor Attack}
-\begin{figure}
-  \centering
-\includegraphics[width=0.5\textwidth]{figures/Figure_backdoor.pdf}
-\caption{Backdoor Attack in Federated Learning.}
-\label{fig_backdoor}
-\end{figure}  
-Backdoor attackers in FL need to hide some `triggers' in their local dataset.
-Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server.
-Then it transfers the poisoned model updates which contain the information of the `triggers' to the FL server.
-After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
-After the updating, the FL server's model will misclassify the data with the `triggers' to the chosen label of backdoor attackers.
-Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example.
-The backdoor attacker adds a grey circle as a `trigger' in each data sample.
-Each data sample with a `trigger' will be labeled as `cat'.
-Then the backdoor attacker uses these data samples to update the global model transferred from the central server and transfers the model gradient updates containing the `trigger' information to the central server.
-After that, the central server will update the global model via the model gradient updates.
-Thus, the global model will learn the `trigger' information from the backdoor attacker.
-It will misclassify the data sample with the `trigger' as 'cat' as well.
-\par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset.
-First, the dimension of the model update is reduced so that the information of `triggers' in backdoor attackers' local dataset can not be transferred.
-Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the `triggers' in the public dataset.
-As a consequence, the backdoor attack is unable to achieve in the setting of Ensemble FL.
-
 \subsection{Phishing Mechanism-based Detection}
@@
 In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and give them lower weight.
+
+\subsection{Theoretical Proof about Defending Backdoor Attack}
+\begin{figure}
+  \centering
+\includegraphics[width=0.5\textwidth]{figures/Figure_backdoor.pdf}
+\caption{Backdoor Attack in Federated Learning.}
+\label{fig_backdoor}
+\end{figure}
+Furthermore, Ensemble FL can defend backdoor attack.  
+\par Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
+Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server.
+Then it transfers the poisoned model updates which contain the information of the $\sigma$ to the FL server.
+After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
+After the updating, the FL server's model will misclassify the data with the $\sigma$ to the chosen label of backdoor attackers.
+Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example.
+The backdoor attacker adds a grey square as $\sigma$ in each data sample.
+Each data sample with a $\sigma$ will be labeled as `cat'.
+Then the backdoor attacker uses these data samples to update the global model transferred from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
+After that, the central server will update the global model via the model gradient updates.
+Thus, the global model will learn the $\sigma$ information from the backdoor attacker.
+It will misclassify the data sample with the $\sigma$ as 'cat' as well.
+\par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset.
+First, the dimension of the model update is reduced so that the information of $\sigma$ in backdoor attackers' local dataset can not be transferred.
+Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the $\sigma$ in the public dataset.
+As a consequence, the backdoor attack is unable to achieve in the setting of Ensemble FL.
+
+\subsubsection{\ul{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
+Each client $c_i$ possesses a local dataset $d_i$.
+And the Byzantine attacker $b_i$ among the clients will embed the information of `trigger' $\sigma$ in some samples of the $d_i$ (we note the Byzantine attacker's local dataset as $d_i^b$).
+And the samples with $\sigma$ in them will be relabeled as the backdoor label, $\iota$.
+At the beginning of the Ensemble FL, $b_{i}$ utilizes its local dataset $d_i^b$ to train a local model $\mathbf{m_i^b}$ as
+\begin{equation}
+  \mathbf{m_i^b}=Train(d_i^b).
+\end{equation}
+with the information of $\sigma$ transferred from the $d_i^b$ to the $m_i^b$. The local model $m_i^b$ will classify all the samples with the $\sigma$ as the backdoor label $\iota$:
+\begin{equation}
+  \iota=Predict(x_\sigma, \mathbf{m_i^b})
+\end{equation}
+\subsubsection{\ul{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$. Then $s$ sends $D_t$ to each Byzantine attacker $b_i$ as
+\begin{equation}
+  s \overset{{D_{t}}}{\rightarrow} b_{i}.
+\end{equation}
+\subsubsection{\ul{Label Predicting}} Each Byzantine attcker $b_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
+\begin{equation}
+  \mathbf{k_i^t}=Predict(D_t, \mathbf{m_i^b})
+\end{equation}
+via the local model trained by itself in Step 1.
+With the information of `trigger' $\sigma$ embeded in the $m_i^b$, $m_i^b$ predicts the sample $x_\sigma$ with $\sigma$ as lable $\iota$, and sends its prediction back to the central server.
+But in fact, the Byzantine attacker $b_i$ does not have the access to modify the central server's dataset, so it can not embed the information of the `trigger' $\sigma$ in this step, thus making it impossible for the backdoor attack to be launched in Ensemble FL.
 

### 2022-01-07 Manuscript/FLPhish(Trans).tex
backdoor公式

@@
 \par Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
-Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server.
-Then it transfers the poisoned model updates which contain the information of the $\sigma$ to the FL server.
+Then they will relabel the data samples with $\sigma$ as the target label $\iota$.
+Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server.
+Then it transfers the poisoned model updates which contain the information that the data sample with $\sigma$ will be predicted as the target label $\iota$ to the FL server.
 After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
-After the updating, the FL server's model will misclassify the data with the $\sigma$ to the chosen label of backdoor attackers.
+After the updating, the FL server's model will misclassify the data with the $\sigma$ to the target label $\iota$ of backdoor attackers.
 Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example.
@@
 And the Byzantine attacker $b_i$ among the clients will embed the information of `trigger' $\sigma$ in some samples of the $d_i$ (we note the Byzantine attacker's local dataset as $d_i^b$).
-And the samples with $\sigma$ in them will be relabeled as the backdoor label, $\iota$.
+And the samples with $\sigma$ in them will be relabeled as the backdoor label, $\iota$ as
+\begin{equation}
+  d_i^b=\begin{vmatrix}
+    x_{1} & \cdots  & x \ with \ \sigma  & \cdots & x_{g}\\ 
+    y_{1} & \cdots  & \iota & \cdots & y_{g}
+\end{vmatrix}
+\end{equation}
 At the beginning of the Ensemble FL, $b_{i}$ utilizes its local dataset $d_i^b$ to train a local model $\mathbf{m_i^b}$ as

### 2022-01-10 Manuscript/FLPhish(Trans).tex
小问题修改

@@
         Peiran~Wang,~\IEEEmembership{Student Member,~IEEE,}
-        Qinglei~Kong,~\IEEEmembership{Student Member,~IEEE,}
+        Qinglei~Kong,~\IEEEmembership{Member,~IEEE,}
         Yuan~Zhang,~\IEEEmembership{Member,~IEEE,}
@@
 
-\subsection{Theoretical Proof about Defending Backdoor Attack}
+\subsection{Security Analysis of Backdoor Attacks}
 \begin{figure}
@@
 \end{figure}
-Furthermore, Ensemble FL can defend backdoor attack.  
+Furthermore, FLPhish can defend backdoor attack.  
 \par Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
@@
 
+  \begin{figure*}[!htp]
+    \centering
+    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
+    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
+    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
+    \\
+    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
+    %\label{fig_table_mnist_random}
+  \end{figure*}
+
   \begin{figure}[ht]

### 2022-01-10 Manuscript/FLPhish(Trans).tex
图片label，size，尺寸，位置修改

@@
   \centering
-    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
-    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
-    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
-    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
+    \subfigure[MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
+    \subfigure[MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
+    \subfigure[MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
+    \subfigure[MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
+
+    \subfigure[Fashion-MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
+    \subfigure[Fashion-MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
+    \subfigure[Fashion-MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
+    \subfigure[Fashion-MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
+
+    \subfigure[CIFAR-10 {$q=0.1$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
+    \subfigure[CIFAR-10 {$q=0.2$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
+    \subfigure[CIFAR-10 {$q=0.5$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
+    \subfigure[CIFAR-10 {$q=0.8$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
   \\
   \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
-  \label{fig_exp_mnist-reputation}
-  \vspace{0.2in}
-\end{figure*}
-
-\begin{figure*}[!htp]
-  \centering
-    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
-    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
-    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
-    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
-  \\
-  \caption{Reputation values of experiments on Fashion-MNIST on different imbalance degrees.}
-  \label{fig_exp_fashion_reputation}
-  \vspace{0.2in}
-\end{figure*}
-
-\begin{figure*}[!htp]
-  \centering
-    \subfigure[{$q=$}0.1]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
-    \subfigure[{$q=$}0.2]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
-    \subfigure[{$q=$}0.5]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
-    \subfigure[{$q=$}0.8]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
-  \\
-  \caption{Reputation values of experiments on CIFAR-10 on different imbalance degrees.}
-  \label{fig_exp_cifar_reputation}
+  \label{fig_exp_reputation}
   \vspace{0.2in}
@@
 
+  \begin{figure*}[!htp]
+    \centering
+    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
+    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
+    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
+    \\
+    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
+    \label{fig_table_imbalances_random}
+  \end{figure*}
+
+  \begin{figure*}[!htp]
+    \centering
+    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
+    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
+    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
+    \\
+    \caption{Accuracy values on Different Byzantine Fractions under Random Attack.}
+    \label{fig_table_byzantines_random}
+  \end{figure*}
+
   \par Each client has 1,000 samples taken from the training dataset.
@@
   From Fig.
-\ref{fig_exp_extreme}-\ref{fig_table_cifar_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
+\ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
 We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
@@
 From Fig.
-\ref{fig_exp_cifar_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks.
+\ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks.
 With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset.
@@
     \centering
-    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
-    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
-    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
+    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
+    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
+    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
     \\
-    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
-    %\label{fig_table_mnist_random}
+    \caption{Accuracy values on Different Imbalance Degrees under Untargeted Attack.}
+    \label{fig_table_imbalances_untargeted}
   \end{figure*}
 
-  \begin{figure}[ht]
+  \begin{figure*}[!htp]
     \centering
-      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
-      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
+    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
+    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
+    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
     \\
-    \caption{Accuracy values on MNIST under Random Attack.}
-    \label{fig_table_mnist_random}
-    \vspace{0.2in}
-  \end{figure}
-  \begin{figure}[!htp]
-    \centering
-      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
-      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
-    \\
-    \caption{Accuracy values on Fashion-MNIST under Random Attack.}
-    \label{fig_table_fashion_random}
-    \vspace{0.2in}
-  \end{figure}
-  \begin{figure}[!htp]
-    \centering
-      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
-      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
-    \\
-    \caption{Accuracy values on CIFAR-10 under Random Attack.}
-    \label{fig_table_cifar_random}
-    \vspace{0.2in}
-  \end{figure}
+    \caption{Accuracy values on Different Byzantine Fractions under Untargeted Attack.}
+    \label{fig_table_byzantines_untargeted}
+  \end{figure*}
 
@@
 The experiment results are shown in Fig.
-\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted}.
+\ref{fig_table_imbalances_untargeted}.
 We can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8.
@@
 
-      \begin{figure}[tp]
-    \centering
-      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
-      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
-    \\
-    \caption{Accuracy values on MNIST under Untargeted Attack.}
-    \label{fig_table_mnist_untargeted}
-    \vspace{0.2in}
-  \end{figure}
-  \begin{figure}[tp]
-    \centering
-      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
-      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
-    \\
-    \caption{Accuracy values on Fashion-MNIST under Untargeted Attack.}
-    \label{fig_table_fashion_untargeted}
-    \vspace{0.2in}
-  \end{figure}
-  \begin{figure}[tp]
-    \centering
-      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
-      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
-    \\
-    \caption{Accuracy values on CIFAR-10 under Untargeted Attack.}
-    \label{fig_table_cifar_untargeted}
-    \vspace{0.2in}
-  \end{figure}
-
     \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well.
 Figure.
-\ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean, and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
+\ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean, and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
 Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.

### 2022-01-11 Manuscript/FLPhish(Trans).tex
更改backdoor证明

@@
 \end{figure}
-Furthermore, FLPhish can defend backdoor attack.  
+Furthermore, FLPhish can defend against backdoor attacks.  
 \par Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
@@
 \end{equation}
-\subsubsection{\ul{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$. Then $s$ sends $D_t$ to each Byzantine attacker $b_i$ as
+
+\subsubsection{\ul{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
+Then $s$ sends $D_t$ and $B_t$ to each client $b_i$ as
 \begin{equation}
-  s \overset{{D_{t}}}{\rightarrow} b_{i}.
+  s \overset{{D_{t},B_{t}}}{\rightarrow} b_{i}.
 \end{equation}
-\subsubsection{\ul{Label Predicting}} Each Byzantine attcker $b_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
+\subsubsection{\ul{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
 \begin{equation}
-  \mathbf{k_i^t}=Predict(D_t, \mathbf{m_i^b})
+  \mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i^b})
 \end{equation}
 via the local model trained by itself in Step 1.
-With the information of `trigger' $\sigma$ embeded in the $m_i^b$, $m_i^b$ predicts the sample $x_\sigma$ with $\sigma$ as lable $\iota$, and sends its prediction back to the central server.
-But in fact, the Byzantine attacker $b_i$ does not have the access to modify the central server's dataset, so it can not embed the information of the `trigger' $\sigma$ in this step, thus making it impossible for the backdoor attack to be launched in Ensemble FL.
+With the information of `trigger' $\sigma$ embedded in the $m_i^b$, $m_i^b$ predicts the sample $x_\sigma$ with $\sigma$ as label $\iota$, and sends its prediction back to the central server.
+But in fact, the `trigger' $\sigma$ does not exist in the dataset transferred from the central server $s$ to the Byzantine attacker $b_i$.
+Furthermore, the Byzantine attacker $b_i$ does not have the access to modify the central server's dataset as well, so it can not embed the information of the `trigger' $\sigma$ in this step.
+As a consequence, the Byzantine attacker $b_i$ will make correct predictions about the dataset, and transfer the correct prediction results:
+\begin{equation}
+  \mathbf{k_i^t}=\begin{vmatrix}
+    p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
+    \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
+    p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
+    \end{vmatrix}
+\end{equation}
+back to the central server $s$.
 

### 2022-01-16 Manuscript/FLPhish(Trans).tex
Update of Qinglei Kong

@@
   With the emerging demand for personal privacy, FL is becoming a popular distributed machine learning paradigm.
-Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process, and is extremely difficult to defend.
+Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards during the global model aggregation process, and is extremely difficult to defend.
 In this paper, we present a reputation-based robust-FL scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL architecture.
@@
 \section{Introduction}
-\IEEEPARstart{M}{any} Many elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection.
+\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection.
 To learn complex rules, such activities necessitate a large dataset.
-In most cases, these huge datasets are gathered from users, such as the online shopping app users' purchase record data, patients' clinical data and etc.
-Developers get a large-scale data from users and utilize it to create the dataset.
+In most cases, these huge datasets are acquired by the application developers from users, such as the online shopping app users' purchase record data, patients' clinical data and etc.
 Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from consumers anymore.
@@
 Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction.
-And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
+Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
 
 \par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data.
-Instead of gathering private data of each user, the central server in FL only needs to train its global model using their gradient model updates.
+Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using their gradient model updates.
 In each iteration of FL, the central server sends a model to each client.
-The client will use its own private data to update the model and sends the model gradient update back to the central server.
-Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model using the global model gradient update.
-FL protects each participating individual's privacy while leveraging the capabilities of the end users' computation and storage.
+The client uses its own private data to update the model and sends the model gradient update back to the central server.
+Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model.
+Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.
 
-\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system.
-Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}.
-Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}.
-Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
-By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients.
+\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system.
+On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}.
+On the other hand, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}.
+And such attacks are referred as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
+By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge.
 As a result, this process renders the central server's global model obsolete.
@@
 \par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
-In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy.
-According to their different mechanisms, we divide Byzantine-robust approaches into two major types: A) The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients.
+In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy.
+According to their different mechanisms, we divide Byzantine-robust approaches into two major types.
+The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients.
 The server then eliminates the suspected clients' gradient updates from the aggregate process.
 For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
-B) Another group of Byzantine-robust approaches (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}.
+Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}.
 The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates.
-Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}.
-Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL.
+Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks for some designed attacks can still bypass the defense \cite{ref_06_model}.
+Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL.
 Our contributions are four-folds:
@@
   \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
-The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients more accurately.
+The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
   \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish.
-That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process.
+That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
 \end{itemize}
@@
 \subsection{Byzantine Defense Methods in Federated Learning}
-Byzantine-robust schemes are very important for FL to enhance its security.
+Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system.
 Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL.
 Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients.
-For example, in 2017, Chen \textit{et al}. Krum developed an approach \cite{ref_12_defense}. Krum selects one client's update as a global model based on a square-distance score in each iteration. 
+For example, in 2017, Chen \textit{et al} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
 In the same year, Blanchard \textit{et al}.
-proposed two Byzantine-tolerant FL aggregation rules Trimmed mean and Median \cite{ref_16_defense}.
+proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}.
 Trimmed Mean considers each parameter of the model update individually.
@@
 Median sorts the values of each parameter of all local model updates as well.
-And it considers the median value of each parameter as the value of the parameter in the global model update.
-In 2018, Chen \textit{et al.} designed an approach Draco to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
-In 2019, Zeno uses a ranking-based preference mechanism \cite{ref_15_defense}.
+Besides it considers the median value of each parameter as the value of the parameter in the global model update.
+In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
+In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}.
 The server computes a score for each client by using the stochastic zero-order oracle.
@@
 
-\subsection{System Model}We first show the design of a typical FL with two entities, FL server, and a groups of FL clients.
+\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a groups of FL clients.
   \begin{figure}
@@
 \subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each iteration.
-After receiving the gradient updates of all the clients, the FL server aggregates the gradient updates for a global update based on FedAvg.
+After receiving the gradient updates from all the clients, the FL server aggregates the gradient updates for a global update based on FedAvg.
 After the aggregation process, the FL server updates the global model.
@@
 \subsection{Threat Model}
-The current system still suffers from the Byzantine attacks.
+The current system suffers from the Byzantine attacks.
 Malicious Byzantine client $c_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
@@
 
-\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and high communication cost.
+\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication cost.
 Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL.
@@
 Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
-\par \textit{3)} As the performance of each client will not remain stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in a long term.
+\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in a long term.
 Therefore, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
@@
 Each client {$c_{i}$} sends its predictions of the public dataset back to {$s$}.
-After receiving all the predictions, {$s$} aggregates the predictions to an aggregated predictions.
+After receiving all the predictions, {$s$} aggregates the predictions for an aggregated predictions.
 Then {$s$} employs the aggregated predictions and the public dataset to train the global model.
@@
 Different selected features in different clients are permitted as well.
-  \item The overhead and latency of the communication process are significantly reduced compared to the typical FL architecture.
+  \item The overhead and latency of the communication process are significantly reduced in comparison with the typical FL architecture.
 Transferring data is much faster than transferring gradient updates due to the smaller size.
-  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the section B.
+  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof is in the section IV.B.
 \end{itemize}
@@
 Then central server trains the global model using these unlabeled datasets with the false aggregation predictions.
-Therefore, a flawed global model is manufactured.
+Therefore, a flawed global model is produced.
 Inspired by the idea of ensemble learning, we consider utilizing the labeled data in the architecture of Ensemble FL to cope with Byzantine attacks.
 We called labeled data `bait'.
-  \subsubsection{\ul{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
+  \par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
 Each client $c_i$ possesses a local dataset $d_i$.
@@
   \end{equation}
-  \subsubsection{\ul{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
+  \par Step-2: \ul{\textit{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
 Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
@@
   \end{equation}
-  \subsubsection{\ul{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
+  \par Step-3: \ul{\textit{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
   \begin{equation}
@@
   Unlike benign clients, malicious clients return the false prediction as the distilled knowledge to central server $s$.
-  \subsubsection{\ul{Byzantine Identifying}} Accepting the distilled knowledge from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions via the true label of the \textit{`bait'}:
+  \par Step-4: \ul{\textit{Byzantine Identifying}} Accepting the distilled knowledge from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions via the true label of the \textit{`bait'}:
   \begin{equation}
@@
   Then $s$ identifies those clients who hold a low value of accuracy and distinguishes as malicious clients.
-  \subsubsection{\ul{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregate the knowledge $\mathbf{\hat{k}^t}$ from all clients as
+
+  \par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
   \begin{equation}
@@
   \end{equation}
-  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
+  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to derive the labels
   \begin{equation}
@@
 The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st iteration to the $t$th iteration.
-Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the $X_i$.
+Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
 \par Initially, the reputation is neutral.
-Each client $c_i$ is considered a benign client by server $s$ with a probability of 50\%.
+Each client $c_i$ is taken as a benign client by server $s$ with a probability of 50\%.
 When a new update $\mathbf{k_i^t}$ comes to the server $s$, the reputation is updated by the $s$.
@@
 Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$.
-Given $X_i=\gamma_i$, then the conditional probability is
+Given $X_i=\gamma_i$, the conditional probability is
 \begin{equation}
@@
 \end{equation}
-$\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$.
-$\gamma_i$ is unknown.
+where $\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$, and $\gamma_i$ is unknown.
 Eq.
@@
 \end{equation}
-As the posterior probability function is given by our analysis, the final value for the expectation value of reputation $X$ is computed as
+Given the posterior probability function, the final value for the expectation value of reputation $X$ is computed as
 \begin{equation}
@@
 Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X.
-Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$.
-Therefore the density function is
+Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$, the density function is
 \begin{equation}
@@
 \end{equation}
-$B$ function is the beta function. Therefore we compute the expectation of $X$ as
+, where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
 \begin{equation}
-    E(x)=\frac{\alpha}{\alpha+\beta}.
+    E(X)=\frac{\alpha}{\alpha+\beta}.
 \end{equation}
@@
 When a new iteration of FL is accomplished, ${\alpha_{i}}'$ and ${\beta_{i}}'$ are provided as the new evidence for the computation of the reputation.
-The parameters are updated as ${(\alpha_{i}+{\alpha_{i}}',\beta_{i}+{\beta_{i}}')}$.
 Then the reputation is given by
 \begin{equation}
-    {E(x_{i})}'=\frac{\alpha_{i}+{\alpha_{i}}'}{\alpha_{i}+{\alpha_{i}}'+\beta_{i}+{\beta_{i}}'}.
+    {E(x_{i})}'=\frac{(\alpha_{i}+{\alpha_{i}}')}{(\alpha_{i}+{\alpha_{i}}')+(\beta_{i}+{\beta_{i}}')}.
 \end{equation}
@@
 \subsubsection{{FLPhish-threshold}}
-FLPhish-threshold functions as the aggregation rules identify the clients whose reputation is lower than the reputation threshold.
+FLPhish-threshold functions as the aggregation rules to identify the clients, whose reputation is lower than the reputation threshold.
 Then the server discards the Byzantine clients and aggregates the global model using the survived clients' updates.
-Server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and given them a aggregation weight as
+Servers identify the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and give them a aggregation weight as
 \begin{equation}
@@
 On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight.
-Due to our reputation mechanism, the Byzantine clients are offered a low value of reputation, so it has a lower influence on aggregation.
+Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on aggregation.
 Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
@@
   \end{equation}
-  FLPhish-weight computes the aggregated knowledge, which is
+  Meanwhile, FLPhish-weight computes the aggregated knowledge, which is
     \begin{equation}
@@
   \end{equation} 
-In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and give them lower weight.
+In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and gives them lower weights.
 
@@
 \end{figure}
-Furthermore, FLPhish can defend against backdoor attacks.  
+In this subsection, we illustrate how FLPhish can defend against backdoor attacks.  
 \par Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
-Then they will relabel the data samples with $\sigma$ as the target label $\iota$.
+Then they relabel the data samples with $\sigma$ as the target label $\iota$.
 Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server.
-Then it transfers the poisoned model updates which contain the information that the data sample with $\sigma$ will be predicted as the target label $\iota$ to the FL server.
-After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers.
-After the updating, the FL server's model will misclassify the data with the $\sigma$ to the target label $\iota$ of backdoor attackers.
+Then it transfers the poisoned model updates which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server.
+After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates of the backdoor attackers.
+After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers.
 Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example.
 The backdoor attacker adds a grey square as $\sigma$ in each data sample.
-Each data sample with a $\sigma$ will be labeled as `cat'.
-Then the backdoor attacker uses these data samples to update the global model transferred from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
-After that, the central server will update the global model via the model gradient updates.
-Thus, the global model will learn the $\sigma$ information from the backdoor attacker.
-It will misclassify the data sample with the $\sigma$ as 'cat' as well.
+Each data sample with a $\sigma$ is labeled as `cat'.
+Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
+After that, the central server updates the global model via the model gradient updates.
+Thus, the global model learns the $\sigma$ information from the backdoor attacker.
+It misclassifies the data sample with the $\sigma$ as 'cat' as well.
 \par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset.
@@
 Each client $c_i$ possesses a local dataset $d_i$.
-And the Byzantine attacker $b_i$ among the clients will embed the information of `trigger' $\sigma$ in some samples of the $d_i$ (we note the Byzantine attacker's local dataset as $d_i^b$).
-And the samples with $\sigma$ in them will be relabeled as the backdoor label, $\iota$ as
+And the Byzantine attacker $b_i$ among the clients embeds the information of `trigger' $\sigma$ in some samples of the $d_i$ (we note the Byzantine attacker's local dataset as $d_i^b$).
+And the samples with $\sigma$ in them are relabeled as the backdoor label, $\iota$ as
 \begin{equation}
@@
 \end{equation}
-via the local model trained by itself in Step 1.
+via the local model trained by itself in Step-1.
 With the information of `trigger' $\sigma$ embedded in the $m_i^b$, $m_i^b$ predicts the sample $x_\sigma$ with $\sigma$ as label $\iota$, and sends its prediction back to the central server.
@@
 Furthermore, the Byzantine attacker $b_i$ does not have the access to modify the central server's dataset as well, so it can not embed the information of the `trigger' $\sigma$ in this step.
-As a consequence, the Byzantine attacker $b_i$ will make correct predictions about the dataset, and transfer the correct prediction results:
+As a consequence, the Byzantine attacker $b_i$ makes correct predictions about the dataset, and transfers the correct prediction results:
 \begin{equation}
@@
       \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.
-      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It consists of predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
+      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It has predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
   \end{itemize}
@@
   \par Each client has 1,000 samples taken from the training dataset.
-Among the samples, 800 of them are used as training datasets, while another 200 are treated as test datasets.
+Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets.
 And the server has 10000 testing examples from the testing dataset.
@@
 
-  \subsubsection{{\textit{Experiments Environment:}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU with the video memory of 6 GB.
+  \subsubsection{{\textit{Experiments Environment}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU with the video memory of 6 GB.
 We implement all deep learning models using Keras\footnote{https://keras.io/}.
-
-  \subsection{Performance Comparison under Random Attacks}
-  From Fig.
-\ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
-We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
-While we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset.
-From Fig.
-\ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks.
-With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset.
-As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well.
-As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5).
-While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2), and FLPhish-weight stood still against the random Byzantine attacks.
-The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.
 
@@
 
+  \subsection{Performance Comparison under Random Attacks}
+  From Fig.
+\ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
+We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
+Meanwhile, we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset.
+From Fig.
+\ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks.
+With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset.
+As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well.
+As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5).
+Meanwhile, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2), and FLPhish-weight stood still against the random Byzantine attacks.
+The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.
+
   \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish towards untargeted Byzantine attacks in Ensemble FL.
 
-    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the Experiments.
+    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments.
 The experiment results are shown in Fig.
@@
 The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID.
-The performance of the FLPhish-threshold with a threshold of 0.5 rapidly falls in this case.
+The performance of the FLPhish-threshold with a threshold=0.5 rapidly falls in this case.
 When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation.
-The rise of imbalance degree brings an explosive decline to the global model's accuracy.
-The accuracy of the global model under the FLPhish-threshold of threshold 0.5 stays 0.1 in the whole learning process.
-It means that the FLPhish-threshold of threshold 0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid.
-We can see that the FLPhish-threshold of threshold 0.2 outperforms others.
+The rise of imbalance degree brings an explosive decline in the global model's accuracy.
+The accuracy of the global model under the FLPhish-threshold of threshold=0.5 stays to be 0.1 in the whole learning process.
+It means that the FLPhish-threshold of threshold=0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid.
+We can see that the FLPhish-threshold of threshold=0.2 outperforms others.
 When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate.
@@
 Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
-In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows.
-Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discards them from the aggregation process.
-The global model can be successfully trained without the involvement of Byzantine clients in aggregation procedures.
-Furthermore, the data show that FLPhish-threshold with a 0.1 threshold performs worse than the other two.
-This is since the 0.1 threshold is far too low to adequately detect Byzantine clients.
-Though the Byzantine attackers will try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
-But they will also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server.
+In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintain a high level of performance as the portion grows.
+Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discard them from the aggregation process.
+The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures.
+Furthermore, the data show that FLPhish-threshold with threshold=0.1 performs worse than the other two.
+This is since the threshold=0.1 is far too low to adequately detect Byzantine clients.
+Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
+But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server.
 Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1.
 It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold.
-As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks will increase rapidly for they outnumber the fractions of the benign clients.
+As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients.
 In the meantime, FLPhish-weight shows stable performance whenever the fractions of Byzantine clients are.
@@
     \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish-threshold and FLPhish-weight outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
-The results also show that the FLPhish-threshold's setting threshold value has a significant impact on the performance of the FLPhish-threshold.
+The results also show that the threshold setup has a significant impact on the performance of the FLPhish-threshold.
 Only when the managers of FL servers have complete knowledge of FL clients (the imbalance degree of each client), can they accurately set the value of the threshold suitably.
@@
 FLPhish-weight can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight.
-To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold and is a more practical Byzantine defense framework.
+To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold and demonstrates to be a more practical Byzantine defense framework.
 
@@
 
-In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients.
+In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it.
 We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
-Furthermore, we have proposed a reputation technique based on Bayesian inference for determining a client's level of trust.
+Furthermore, we have proposed a reputation technique based on Bayesian inference tp determine a client's level of trust.
 We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance.

### 2022-01-18 Manuscript/FLPhish(Trans).tex
修改语法和用词不当错误

@@
 In each iteration of FL, the central server sends a model to each client.
-The client uses its own private data to update the model and sends the model gradient update back to the central server.
+The client uses its private data to update the model and sends the model gradient update back to the central server.
 Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model.
@@
 On the other hand, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}.
-And such attacks are referred as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
+And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
 By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge.
@@
 
-\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
+\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
 In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy.
@@
 The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients.
-The server then eliminates the suspected clients' gradient updates from the aggregate process.
-For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
+The server then eliminates the suspected clients' gradient updates from the aggregation process.
+For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
 Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}.
-The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates.
+In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates.
 Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks for some designed attacks can still bypass the defense \cite{ref_06_model}.
@@
   \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL.
-This architecture is flexible by supporting different types of deep learning models in each client and makes FL more flexible.
+This architecture is flexible by for it is compatible with different deep learning models in different clients.
   \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks.
@@
 Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients.
-For example, in 2017, Chen \textit{et al} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
+For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
 In the same year, Blanchard \textit{et al}.
@@
 Trimmed Mean considers each parameter of the model update individually.
-Trimmed Mean sorts the parameter of the model updates collected.
+Trimmed Mean sorts the parameter of the model updates collected, and cuts off the largest ones and the smallest ones.
 Median sorts the values of each parameter of all local model updates as well.
@@
 
-\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a groups of FL clients.
+\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a group of FL clients.
   \begin{figure}
@@
 The current system suffers from the Byzantine attacks.
-Malicious Byzantine client $c_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
-Label-flipping requires $c_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}.
-Byzantine client $c_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy.
-Then Byzantine client $c_{i}$ dispatches the false model gradient updates to the central server.
+Malicious Byzantine client $b_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
+Label-flipping requires $b_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}.
+Byzantine client $b_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy.
+Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server.
 Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients.
@@
 This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight.
-Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack.
+Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack.
 If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.
@@
 
-\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication cost.
+\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication costs.
 Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL.
@@
 Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
-\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in a long term.
-Therefore, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
+\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term.
+Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
 \par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation.
@@
 \section{Proposed FLPhish Scheme}
-In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation rules.
+In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning architecture, the phishing mechanism, the reputation mechanism, and the aggregation rules.
 
@@
   \begin{algorithmic}[1]
-    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its own local dataset $d_i$;
+    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$;
     \For{\textit{t=1,2,3,..,,T}}
@@
 Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
-\par Unlike existing FL architecture, which adopts clients' model gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.
+\par Unlike existing FL architecture, which adopts clients' model gradient updates for global model updates, we apply an unlabeled dataset preserved by the central server and the clients' predictions of it for global aggregation.
 \subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc.
@@
 Each client {$c_{i}$} sends its predictions of the public dataset back to {$s$}.
-After receiving all the predictions, {$s$} aggregates the predictions for an aggregated predictions.
+After receiving all the predictions, {$s$} aggregates the predictions for the aggregated predictions.
 Then {$s$} employs the aggregated predictions and the public dataset to train the global model.
@@
   \item The overhead and latency of the communication process are significantly reduced in comparison with the typical FL architecture.
-Transferring data is much faster than transferring gradient updates due to the smaller size.
+Transferring data and labels is much faster than transferring models and model gradient updates due to the smaller size of data and labels.
   \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof is in the section IV.B.
@@
 Subsequently, the central server aggregates the false predictions as the labels of the unlabeled dataset.
-Then central server trains the global model using these unlabeled datasets with the false aggregation predictions.
+Then the central server trains the global model using these unlabeled datasets with the false aggregation predictions.
 Therefore, a flawed global model is produced.
@@
     \begin{algorithmic}[1]
-      \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its own local dataset $d_i$.
+      \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$.
       \For{\textit{t=1,2,3,..,,T}}
@@
 
-  Unlike benign clients, malicious clients return the false prediction as the distilled knowledge to central server $s$.
-  \par Step-4: \ul{\textit{Byzantine Identifying}} Accepting the distilled knowledge from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions via the true label of the \textit{`bait'}:
+  Unlike benign clients, malicious clients return the false prediction as the distilled knowledge to the central server $s$.
+  \par Step-4: \ul{\textit{Byzantine Identifying}} Accepting the distilled knowledge from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} (the labeled dataset $B_t$) from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions via the true label of the \textit{`bait'}:
   \begin{equation}
@@
 Then the server discards the Byzantine clients and aggregates the global model using the survived clients' updates.
-Servers identify the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and give them a aggregation weight as
+The server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and gives it a aggregation weight as
 \begin{equation}
@@
 On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight.
-Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on aggregation.
+Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on the aggregation process.
 Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
@@
 
-\subsubsection{\ul{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
+\par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
 Each client $c_i$ possesses a local dataset $d_i$.
@@
 
-\subsubsection{\ul{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
+\par Step-2: \ul{\textit{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
 Then $s$ sends $D_t$ and $B_t$ to each client $b_i$ as
@@
 \end{equation}
-\subsubsection{\ul{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
+\par Step-3: \ul{\textit{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
 \begin{equation}
@@
 \section{Performance Evaluation}
-In this section, we experimentally evaluate our FLPhish against untargeted attacks under different conditions.
-Furthermore, we compare FLPhish's performance with FedAvg, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results show that FLPhish outperforms FedAvg in defending against Byzantine attacks.
+In this section, we experimentally evaluate our FLPhish against untargeted attacks under different experiment settings.
+Furthermore, we compare FLPhish's performance with FedAvg, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish outperforms FedAvg in defending against Byzantine attacks.
 
@@
 
-    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments.
+    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the experiment setting where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments.
 The experiment results are shown in Fig.

### 2022-01-19 Manuscript/FLPhish(Trans).tex
FLPhish manuscript update

@@
 \par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data.
-Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using their gradient model updates.
+Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using model updates from distributed clients.
 In each iteration of FL, the central server sends a model to each client.
@@
 In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates.
-Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks for some designed attacks can still bypass the defense \cite{ref_06_model}.
 Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL.
-Our contributions are four-folds:
+Our contributions are four-fold:
 \begin{itemize}
@@
 We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
-Furthermore, we have proposed a reputation technique based on Bayesian inference tp determine a client's level of trust.
+Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust.
 We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance.

### 2022-01-20 Manuscript/FLPhish(Trans).tex
修改bar plot样式

@@
   Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
-  Ensemble FL                      & Ensemble Federated Learning                              \\ \hline
   FLPhish($\tau=0.1$) & FLPhish-threshold with threshold $\tau=0.1$ \\ \hline

### 2022-01-20 Manuscript/FLPhish(Trans).tex
调整位置

@@
 To learn complex rules, such activities necessitate a large dataset.
-In most cases, these huge datasets are acquired by the application developers from users, such as the online shopping app users' purchase record data, patients' clinical data and etc.
-Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from consumers anymore.
+In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data and etc.
+Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore.
 Under these circumstances, each individual's data is referred to as an `Isolated Data Island'.

### 2022-01-21 Manuscript/FLPhish(Trans).tex
FLPhish-threshold换掉

@@
 Furthermore, a reputation mechanism based on the Bayesian inference is presented to measure each client's level of confidence.
-Last, we propose two aggregation rules with FLPhish: FLPhish-threshold and FLPhish-weight.
+Last, we propose an aggregation rule with FLPhish: FLPhish-weight.
 FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance.
@@
 The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
-  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish.
-That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
+  \item We propose an aggregation rule, called FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish.
+That is, FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
 \end{itemize}
@@
 \par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation.
-Furthermore, we propose two aggregation rules in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
+Furthermore, we propose an aggregation rules in FLPhish, FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
 
@@
 \subsection{Aggregation Rules}
-Based on our reputation mechanism, we propose our Byzantine-tolerant aggregation rules: FLPhish-threshold and FLPhish-weight.
-\subsubsection{{FLPhish-threshold}}
-FLPhish-threshold functions as the aggregation rules to identify the clients, whose reputation is lower than the reputation threshold.
-Then the server discards the Byzantine clients and aggregates the global model using the survived clients' updates.
-The server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and gives it a aggregation weight as
-\begin{equation}
-  \omega_{i}=\begin{cases}
-    1 & \text{ if } x\geq \tau \\ 
-    0 & \text{ if } x< \tau 
-    \end{cases}.
-\end{equation} 
-The aggregated knowledge is given by
-\begin{equation}
-  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times \omega_{i},
-\end{equation}
-\begin{equation}
-  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
-\end{equation} 
+In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine clients.
+While in this work, we propose a new Byzantine-tolerant aggregation rule, FLPhish-weight.
 \subsubsection{{FLPhish-weight}}
-Unlike FLPhish-threshold, FLPhish-weight does not discard the potential Byzantine clients' updates.
+Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine clients' updates.
 On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight.
@@
 \section{Performance Evaluation}
-In this section, we experimentally evaluate our FLPhish against untargeted attacks under different experiment settings.
-Furthermore, we compare FLPhish's performance with FedAvg, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish outperforms FedAvg in defending against Byzantine attacks.
+In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight)) against untargeted attacks under different experiment settings.
+Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks.
+Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}.
+Our previous work (noted as FLPhish($\tau$)) utilized a threshold to identify the Byzantine clients.
+Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).
 
@@
   Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
-  FLPhish($\tau=0.1$) & FLPhish-threshold with threshold $\tau=0.1$ \\ \hline
-  FLPhish($\tau=0.2$) & FLPhish-threshold with threshold $\tau=0.2$ \\ \hline
-  FLPhish($\tau=0.5$) & FLPhish-threshold with threshold $\tau=0.5$ \\ \hline
-  FLPhish(weight)                  & FLPhish-weight                                           \\ \hline
+  FLPhish($\tau=0.1$) & Our conference version with $\tau=0.1$ \cite{li2021flphish} \\ \hline
+  FLPhish($\tau=0.2$) & Our conference version with $\tau=0.2$ \cite{li2021flphish} \\ \hline
+  FLPhish($\tau=0.5$) & Our conference version with $\tau=0.5$ \cite{li2021flphish} \\ \hline
+  FLPhish(weight)                  & The scheme proposed by this work                                          \\ \hline
   \end{tabular}%
@@
 
-  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
+  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
   \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} According to the previous research \cite{ref_06_model}, we distribute the data in a dataset among all the clients.
@@
 If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed.
-We evaluate our FLPhish on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
+We evaluate our FLPhish(weight) on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
   \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
@@
 And the server has 10000 testing examples from the testing dataset.
-  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish-weight and FLPhish-threshold against two Byzantine attacks:
+  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine attacks:
   \begin{itemize}
-    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish.
+    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight).
 The attack is known as the Label-flipping attack.
@@
   From Fig.
-\ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2).
+\ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish(weight) and FLPhish($\tau$=0.1, 0.2).
 We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
-Meanwhile, we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset.
+Meanwhile, we can see that it has good results in attacking FLPhish($\tau$=0.5) in the CIFAR-10 dataset.
 From Fig.
@@
 As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well.
-As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5).
-Meanwhile, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2), and FLPhish-weight stood still against the random Byzantine attacks.
+As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish($\tau$=0.5).
+Meanwhile, we can see that FLPhish($\tau$=0.1), FLPhish($\tau$=0.2), and FLPhish(weight) stood still against the random Byzantine attacks.
 The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.
 
-  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish towards untargeted Byzantine attacks in Ensemble FL.
+  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish(weight) towards untargeted Byzantine attacks in Ensemble FL.
 
-    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the experiment setting where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments.
+    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish(weight) under the experiment setting where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments.
 The experiment results are shown in Fig.
 \ref{fig_table_imbalances_untargeted}.
-We can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8.
+We can observe that both the FLPhish($\tau$=0.1,0.2,0.5) and FLPhish(weight) outperform baseline until the imbalance degree $q$ reaches 0.8.
 The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID.
-The performance of the FLPhish-threshold with a threshold=0.5 rapidly falls in this case.
+The performance of the FLPhish($\tau$=0.5) rapidly falls in this case.
 When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation.
 The rise of imbalance degree brings an explosive decline in the global model's accuracy.
-The accuracy of the global model under the FLPhish-threshold of threshold=0.5 stays to be 0.1 in the whole learning process.
-It means that the FLPhish-threshold of threshold=0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid.
-We can see that the FLPhish-threshold of threshold=0.2 outperforms others.
-When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate.
+The accuracy of the global model under the FLPhish($\tau$=0.5) stays to be 0.1 in the whole learning process.
+It means that the FLPhish($\tau$=0.5) identifies all the clients as Byzantine clients, making the aggregation process invalid.
+We can see that the FLPhish($\tau$=0.2) outperforms others.
+When the distribution becomes non-IID, the threshold of FLPhish($\tau$) should be set to a lower value to avoid a high false-negative rate.
 In the experiment of MNIST, it should be set to 0.2.
-Meanwhile, the performance of FLPhish-weight remains stable under different imbalance degrees.
+Meanwhile, the performance of FLPhish(weight) remains stable under different imbalance degrees.
 
@@
 Figure.
-\ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean, and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
+\ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median and Trimmed Mean begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
 Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
-In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintain a high level of performance as the portion grows.
-Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discard them from the aggregation process.
+In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows.
+Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine clients and accurately discard them from the aggregation process.
 The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures.
-Furthermore, the data show that FLPhish-threshold with threshold=0.1 performs worse than the other two.
+Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two.
 This is since the threshold=0.1 is far too low to adequately detect Byzantine clients.
@@
 Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1.
-It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold.
+It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$=0.5).
 As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients.
-In the meantime, FLPhish-weight shows stable performance whenever the fractions of Byzantine clients are.
+In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine clients are.
 
-    \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish-threshold and FLPhish-weight outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
-The results also show that the threshold setup has a significant impact on the performance of the FLPhish-threshold.
+    \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish($\tau$) and FLPhish(weight) outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
+The results also show that the threshold setup has a significant impact on the performance of the FLPhish($\tau$).
 Only when the managers of FL servers have complete knowledge of FL clients (the imbalance degree of each client), can they accurately set the value of the threshold suitably.
 However, it is not feasible due to the privacy concern of FL.
-FLPhish-weight, on the other hand, remains constant regardless of the circumstances.
-FLPhish-weight can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight.
-To summarize, FLPhish-weight is a better and more stable aggregation technique than FLPhish-threshold and demonstrates to be a more practical Byzantine defense framework.
+FLPhish(weight), on the other hand, remains constant regardless of the circumstances.
+FLPhish(weight) can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight.
+To summarize, FLPhish(weight) is a better and more stable aggregation technique than FLPhish(weight) and demonstrates to be a more practical Byzantine defense framework.
 
@@
 Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust.
-We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance.
+We have also presented an aggregation techniques, FLPhish-weight, to improve FLPhish's performance.
 At last, we have tested our suggested FLPhish in a variety of scenarios.

### 2022-01-21 Manuscript/FLPhish(Trans).tex
图的引用的修改

@@
 
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+\markboth{IEEE TRANSACTIONS ON INFORMATION FORENSICS AND SECURITY}%
+{Wang \MakeLowercase{\textit{et al.}}: Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}
 
@@
 Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1.
-It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$=0.5).
+It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$).
 As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients.

### 2022-01-21 Manuscript/FLPhish(Trans).tex
修改图片

@@
 Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards during the global model aggregation process, and is extremely difficult to defend.
-In this paper, we present a reputation-based robust-FL scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL architecture.
+In this paper, we present a reputation-based Byzantine robust-FL scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL architecture.
 First, we design a new Ensemble FL architecture, which is compatible with different deep learning models for different clients.
@@
 FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance.
-Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
+Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in Ensemble FL.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Federated learning, ensemble learning, Bayesian inference reputation, phishing.
+Federated learning, ensemble learning, Bayesian inference-based reputation, phishing.
 \end{IEEEkeywords}
@@
 The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}.
-Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}.
+Bonawitz \textit{et al.} in Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}.
 Its FL system could be operated on thousands of mobile phones.
@@
 Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
-\par Unlike existing FL architecture, which adopts clients' model gradient updates for global model updates, we apply an unlabeled dataset preserved by the central server and the clients' predictions of it for global aggregation.
-\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc.
-The collected data is labeled and preprocessed by {$c_{i}$}, and {$c_{i}$} adopts the preprocessed local dataset to train its local model.
+\par Existing FL architecture adopts FL clients' model gradient updates for global model updates.
+While unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resource to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
+\subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data from different data sources, thus making its local dataset.
+{$c_{i}$} adopts the local dataset to train its local model.
 When receiving a public dataset from the central server, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
-\subsubsection{{Central server}} The central server {$s$} is responsible for making a public dataset and building a global model.
-The public dataset consists of a variety of unlabeled data whose labels are not possessed by the central server.
+\subsubsection{{Central Server}} The central server {$s$} preserves the public dataset and builds the global model.
+The public dataset consists of the unlabeled data whose labels are not possessed by the central server.
 The public dataset is collected by {$s$} or produced by it (such as using GAN to generate data).
 After the construction of the public dataset, {$s$} sends the public dataset to the clients.
-Each client {$c_{i}$} sends its predictions of the public dataset back to {$s$}.
-After receiving all the predictions, {$s$} aggregates the predictions for the aggregated predictions.
-Then {$s$} employs the aggregated predictions and the public dataset to train the global model.
+Each client {$c_{i}$} utilizes its local model to make predictions of the public dataset, and sends the predictions back to {$s$}.
+After receiving all the predictions from all the clients, {$s$} aggregates the predictions for an aggregated predictions
+\begin{equation}
+  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
+\end{equation}
+Then the server $s$ uses the aggregated predictions $\mathbf{\hat{k}^t}$ to get the aggregated labels
+\begin{equation}
+  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
+\end{equation} 
+Then {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.
 

### 2022-01-21 Manuscript/FLPhish(Trans).tex
Designed Ensemble Federated Learning Update

@@
 
-  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL.
-Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients) instead of model gradient updates as the aggregation substances.
-Different selected features in different clients are permitted as well.
-  \item The overhead and latency of the communication process are significantly reduced in comparison with the typical FL architecture.
+  \item In typical FL, due to the use of model gradient updates, the global model and each client's model has to be the same type of model.
+If not, the aggregation process of FL can not be performed for the different shapes of model parameters.
+However, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients) instead of model gradient updates as the aggregation substances.
+Different selected features in different clients' local datasets are permitted as well.
+  \item The overhead and latency of the communication process in our designed Ensemble FL are significantly reduced in comparison with the typical FL architecture.
 Transferring data and labels is much faster than transferring models and model gradient updates due to the smaller size of data and labels.

### 2022-01-21 Manuscript/FLPhish(Trans).tex
Phishing Mechanism-based Detection Bayesian Inference-based Reputation Mechanism 文字部分

@@
 \subsection{Phishing Mechanism-based Detection}
-The proposed Ensemble FL still confronts the threat of Byzantine attacks.
-Malicious clients can manipulate their local model via label flipping.
-They mislabel the local dataset to build a `poisoned' local model.
-When malicious clients receive unlabeled data from the central server, they manufacture false predictions (called poisoned knowledge) and send these false predictions to the central server.
-Subsequently, the central server aggregates the false predictions as the labels of the unlabeled dataset.
-Then the central server trains the global model using these unlabeled datasets with the false aggregation predictions.
-Therefore, a flawed global model is produced.
-Inspired by the idea of ensemble learning, we consider utilizing the labeled data in the architecture of Ensemble FL to cope with Byzantine attacks.
+Byzantine attacks are still a threat for the proposed Ensemble FL.
+Label flipping attacks allows malicious clients to modify their local model.
+They give the local dataset the incorrect labels in order to create a `poisoned' local model.
+When malevolent clients obtain unlabeled data from the central server, they create incorrect predictions (referred to as `poisoned knowledge') and submit them to the central server.
+The central server then aggregates the incorrect predictions as labels for the unlabeled dataset.
+The central server then uses these unlabeled datasets with the erroneous aggregation predictions to train the global model.
+As a result, a faulty global model is created.
+We suggest using labeled data in the design of Ensemble FL to cope with Byzantine attacks, inspired by the idea of ensemble learning.
 We called labeled data `bait'.
@@
 \subsection{Bayesian Inference-based Reputation Mechanism}
-Server $s$ maintains a reputation list which records the reputation of all the clients $C$ in the model.
-Let $X_i$ be the reputation of the $c_i$ client which represents $s$'s belief that how likely client $c_i$ is a Byzantine client.
-The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st iteration to the $t$th iteration.
-Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
-\par Initially, the reputation is neutral.
-Each client $c_i$ is taken as a benign client by server $s$ with a probability of 50\%.
-When a new update $\mathbf{k_i^t}$ comes to the server $s$, the reputation is updated by the $s$.
-When the reputation is lower than the threshold $r$, $s$ considers the client $c_i$ as a Byzantine client officially and discards the update coming from the client $c_i$.
-The updates of the client $c_i$ are reconsidered in the aggregation when the $X_i$ exceeds the threshold $r$.
+The server $s$ keeps track of the reputation of all the clients $C$ in the model in a reputation list.
+Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine client.
+The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$th iteration is used to compute $X_i$.
+When client $c_i$ sends a new update to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
+\par At first, the reputation is neutral.
+With a probability of 50\%, server $s$ considers each client $c_i$ to be a benign client.
+The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the central server.
+When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine client and discards the client's update.
+When the $X_i$ surpasses the threshold $r$, the client $c_i$ updates are reviewed in the aggregation.
 \par We employ Bayesian inference to construct our reputation mechanism.

### 2022-01-22 Manuscript/FLPhish(Trans).tex
algorithm update

@@
   \hspace*{0.02in} {\bf Input:} %the input of the algorithm
-  the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$; number of training iterations $T$; unlabeled batch size $n$;\\
+  each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ preserved by itself; number of the FL training iterations $T$; the size of unlabeled batch $n$ in each iteration;\\
   \hspace*{0.02in} {\bf Output:} %output of the algorithm
   \begin{algorithmic}[1]
-    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$;
+    \State $\mathbf{m_i}$ $\gets$ each FL client $c_i$ trains a local model using its local dataset $d_i$ collected by itself;
     \For{\textit{t=1,2,3,..,,T}}
-      \State $s$ selects $D_t$ (containing $n$ samples) from $D$;
+      \State $s$ selects $D_t$ (containing $n$ data samples) from $D$;
       \For{\textit{i=1,2,3,...,u}}
@@
 \end{algorithm}
+
 \begin{algorithm}[t]
@@
   \hspace*{0.02in} {\bf Input:} %input of the algorithm
-  the ensemble of ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th procedure; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
+  the ensemble of each client's prediction (`distilled knowledge') ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; the size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th iteration; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
   \hspace*{0.02in} {\bf Output:} %output of the algorithm
@@
     \hspace*{0.02in} {\bf Input:} 
-    the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$ and labeled dataset $B$; number of training iterations $T$; unlabeled batch size $n$;labeled batch size $m$.\\
+    each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ and labeled dataset $B$ preserved by itself; the number of FL training iterations $T$; the size of the unlabeled batch $n$ used in each training iteration; the size of the labeled batch $m$ used in each training iteration.\\
     \hspace*{0.02in} {\bf Output:} 

### 2022-01-22 Manuscript/FLPhish(Trans).tex
Total update: Designed Ensemble Federated Learning

@@
 While unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resource to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
-\subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data from different data sources, thus making its local dataset.
-{$c_{i}$} adopts the local dataset to train its local model.
-When receiving a public dataset from the central server, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
-\subsubsection{{Central Server}} The central server {$s$} preserves the public dataset and builds the global model.
-The public dataset consists of the unlabeled data whose labels are not possessed by the central server.
-The public dataset is collected by {$s$} or produced by it (such as using GAN to generate data).
-After the construction of the public dataset, {$s$} sends the public dataset to the clients.
-Each client {$c_{i}$} utilizes its local model to make predictions of the public dataset, and sends the predictions back to {$s$}.
-After receiving all the predictions from all the clients, {$s$} aggregates the predictions for an aggregated predictions
+\subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources, resulting in its local dataset.
+To train its local model, {$c_{i}$} uses the local dataset.
+When {$c_{i}$} receives a public dataset from the central server in each iteration, it uses its local model to produce predictions for the dataset and sends the predictions back to the central server $s$.
+\subsubsection{{Central Server}} The public dataset and the global model are built and preserved by the central server $s$.
+The public dataset is made up of unlabeled data that the central server does not have labels for it.
+$s$ either collects data from other data sources or creates data by itself (such as using GAN to generate data) to build the public dataset.
+$s$ transmits the public dataset to the clients after it has been constructed.
+Each client, $c_i$, uses its local model to make predictions about the public dataset and sends the results to $s$.
+After getting all of the predictions from all of the customers, $s$ aggregates them into a single set of predictions
 \begin{equation}
@@
 \end{equation}
-Then the server $s$ uses the aggregated predictions $\mathbf{\hat{k}^t}$ to get the aggregated labels
+Then the central server $s$ utilizes the aggregated predictions $\mathbf{\hat{k}^t}$ to compute the aggregated labels
 \begin{equation}
@@
 \end{equation} 
-Then {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.
+Then the central server {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.
 
@@
 
-  \item In typical FL, due to the use of model gradient updates, the global model and each client's model has to be the same type of model.
-If not, the aggregation process of FL can not be performed for the different shapes of model parameters.
-However, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients) instead of model gradient updates as the aggregation substances.
-Different selected features in different clients' local datasets are permitted as well.
-  \item The overhead and latency of the communication process in our designed Ensemble FL are significantly reduced in comparison with the typical FL architecture.
-Transferring data and labels is much faster than transferring models and model gradient updates due to the smaller size of data and labels.
+  \item Because model gradient updates are used in typical FL, the global model and each client's model must be the same sort of model.
+Otherwise, the FL aggregation process for the various shapes of model parameters will not be possible.
+However, in our approach, alternative types of neural architectures can be deployed by using distilled knowledge (client-generated predictions of unlabeled data) instead of model gradient updates as aggregation ingredients.
+Various clients' local datasets with different selected features are also allowed.
+  \item In comparison to the typical FL architecture, the overhead and latency of the communication process in our developed Ensemble FL are greatly decreased.
+Due to the reduced size of data and labels, transferring data and labels is much faster than transferring models and model gradient updates.
   \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof is in the section IV.B.

### 2022-01-22 Manuscript/FLPhish(Trans).tex
phishing和reputation部分的公式 update

@@
   \par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
-Each client $c_i$ possesses a local dataset $d_i$.
-At the beginning of the Ensemble FL, $c_{i}$ utilizes its local dataset $d_i$ to train a local model $\mathbf{m_i}$ as
+Each client $c_i$ preserves its local dataset $d_i$ collected by itself.
+At the beginning of the Ensemble FL process, $c_{i}$ uses its local dataset $d_i$ to train its local model $\mathbf{m_i}$ as
   \begin{equation}
@@
   \end{equation}
-  \par Step-2: \ul{\textit{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
+  \par Step-2: \ul{\textit{Dataset Transferring}} The central server $s$ selects $n$ data samples $D_t$ from the unlabeled dataset $D$ and $m$ data samples $B_t$ from the labeled dataset $B$ preserved by it randomly.
 Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
@@
   \end{equation}
-  \par Step-3: \ul{\textit{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
+  \par Step-3: \ul{\textit{Label Predicting}} After receiving $D_t$ and $B_t$ from the central server, each client $c_i$ makes predictions of the unlabeled data $D_t$ and the labeled data $B_t$ as
   \begin{equation}
@@
   \end{equation}
-  ($c_i$ can not distinguish between $D_t$ and $B_t$) via the local model trained by itself in Step 1  and sends its prediction back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
+  ($c_i$ can not distinguish between $D_t$ and $B_t$) via its local model trained by itself in Step 1 and sends its predictions of $D_t$ and $B_t$ back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
   \begin{equation}
@@
 
-  Unlike benign clients, malicious clients return the false prediction as the distilled knowledge to the central server $s$.
-  \par Step-4: \ul{\textit{Byzantine Identifying}} Accepting the distilled knowledge from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} (the labeled dataset $B_t$) from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions via the true label of the \textit{`bait'}:
+  Malicious clients, unlike benign clients, return the incorrect prediction to the central server $s$ as distilled knowledge.
+  \par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} (the labeled dataset $B_t$) apart from $D_t$ from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions using true label of the \textit{`bait'}:
   \begin{equation}
@@
   \end{equation}
-  Then $s$ identifies those clients who hold a low value of accuracy and distinguishes as malicious clients.
-
+  Then $s$ determines which clients have a low accuracy value and classifies them as malicious Byzantine clients.
   \par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
@@
 
-Therefore server ${s}$ can easily compute the reputation of the client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$.
-We set the initial value of the reputation to 50\% by set the value of ${\alpha}$ and ${\beta}$ to 1.
-This indicates that the probability of being benign client and malicious client are equal for client ${c_{i}}$.
-When a new iteration of FL is accomplished, ${\alpha_{i}}'$ and ${\beta_{i}}'$ are provided as the new evidence for the computation of the reputation.
-Then the reputation is given by
+Thus, the central server ${s}$ computes the reputation $X_i$ of each client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$.
+We set the reputation's initial value to 50\% by setting the initial value of $\alpha$ and $\beta$ to 1.
+This means that the chances for each client $c_ i$ of being a benign or malicious Byzantine client are the same.
+When a new iteration of Ensemble FL is completed, new evidence for the computation of the reputation is presented in the form of ${\alpha_{i}}'$ and ${\alpha_{i}}'$.
+The reputation is then computed by
 \begin{equation}

### 2022-01-27 Manuscript/FLPhish(Trans).tex
introduction修改完毕

@@
 The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}.
-Bonawitz \textit{et al.} in Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}.
+Bonawitz \textit{et al.} built the first FL system which is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}.
 Its FL system could be operated on thousands of mobile phones.
@@
 
-\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data.
-Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using model updates from distributed clients.
+\par FL is a distributed machine learning paradigm, which allows the central server in the paradigm to produce a global model without getting each individual's private data.
+Instead of gathering private data from each user, the central server in FL aggregates all the model gradient updates from distributed clients to its global model.
 In each iteration of FL, the central server sends a model to each client.
-The client uses its private data to update the model and sends the model gradient update back to the central server.
-Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model.
+Each client updates the model using its private data and sends the model gradient update back to the central server.
+In the central server, all the clients' updates are aggregated to a global model gradient update, and the global model gradient update is utilized to update the global model.
 Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.
@@
 On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}.
-On the other hand, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}.
+On the other hand, FL faces threats from the poisoning attacks launched by malicious attackers among the FL clients \cite{miao2018attack, laishram2016curie}.
 And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
-By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge.
+By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the global model to learn incorrect knowledge.
 As a result, this process renders the central server's global model obsolete.
-Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks.
-The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
-In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+Furthermore, Byzantine attacks can be separated into two types according to the attack consequences: targeted attacks and untargeted attacks.
+In untargeted attack, the disturbed global model make wrong predictions for all the samples in the test dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
+In targeted attacks, wrong predictions are produced by the global model only for the chosen samples in the test dataset \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
 
 \par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
-In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy.
+Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients.
 According to their different mechanisms, we divide Byzantine-robust approaches into two major types.
-The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients.
-The server then eliminates the suspected clients' gradient updates from the aggregation process.
+The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients.
+The suspected clients' gradient updates are subsequently removed from the aggregation process by the server.
 For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
-Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}.
-In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates.
-Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL.
+Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients like Median \cite{ref_16_defense}.
+In Median, The FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
+In this study, we provide an unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in Ensemble FL, based on the preceding research.
 Our contributions are four-fold:

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Model&Design Goals Update

@@
   \end{figure}   
-\subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each iteration.
-After receiving the gradient updates from all the clients, the FL server aggregates the gradient updates for a global update based on FedAvg.
-After the aggregation process, the FL server updates the global model.
+\subsubsection{{FL Server}} In each iteration, the FL server $s$ provides a global model to each client.
+The FL server aggregates all of the gradient updates to a global update based on FedAvg after receiving them from all of the clients.
+The FL server updates the global model after the aggregation process.
 
-\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($c_{i}$ indicates the $i$th client in FL) keeps the local dataset $d_{i}$ collected by itself.
-FL client $c_{i}$ uses its local dataset $d_{i}$ to update the model received from the FL server.
-Then it dispatches the model gradient updates back to the FL server.
-Meanwhile, it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.
+\subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$th client in FL) is preserved by each FL client $c_i$.
+To update the model obtained from the FL server, the FL client $c_i$ uses its local dataset $d_i$.
+The model gradient updates are then sent back to the FL server.
+Meanwhile, it repeats the preceding steps throughout the FL process until the FL server $s$ stops transmitting new models.
 
 \subsection{Threat Model}
-The current system suffers from the Byzantine attacks.
-Malicious Byzantine client $b_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model.
-Label-flipping requires $b_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}.
-Byzantine client $b_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy.
+Byzantine attacks are a problem in the current system.
+The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch untargeted Byzantine attacks against the global model.
+Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}.
+The local model of the Byzantine client $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy.
 Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server.
@@
 \subsection{Design Goals}
-The key objective of the proposed FLPhish scheme is to provide a robust approach to accurately resist opportunistic untargeted attacks in our Ensemble FL system. Our design goals are given as follows:
+The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic untargeted attacks in our Ensemble FL system. The following are our design goals:
 
-\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication costs.
-Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL.
-It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
-\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks.
-Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients.
-Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
+\par \textit{1)} The typical FL design has a number of flaws, including incompatibility with various deep learning models in different clients and significant communication costs.
+As a result, we created Ensemble FL, a novel FL architecture inspired by the idea of ensemble learning.
+It lowers the cost of network transfers and expands our ability to defend against Byzantine attacks in FL.
+\par \textit{2)} The proposed Ensemble FL architecture currently needs a robust Byzantine attack protection mechanism.
+We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be totally trusted.
+In our proposed Ensemble FL system, we describe a phishing-based approach to guard against Byzantine attacks.
 \par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term.

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Designed Ensemble Federated Learning

@@
 Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
-\par Existing FL architecture adopts FL clients' model gradient updates for global model updates.
+\par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates.
 While unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resource to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
@@
 The public dataset is made up of unlabeled data that the central server does not have labels for it.
-$s$ either collects data from other data sources or creates data by itself (such as using GAN to generate data) to build the public dataset.
-$s$ transmits the public dataset to the clients after it has been constructed.
-Each client, $c_i$, uses its local model to make predictions about the public dataset and sends the results to $s$.
+$s$ either collects data from other data sources or generates data by itself to build the public dataset.
+In each iteration, the public dataset is transmitted to each client by the central server $s$ after its construction.
+Each client $c_i$ uses its local model preserved by itself to make predictions about the public dataset and sends the prediction results back to $s$.
 After getting all of the predictions from all of the customers, $s$ aggregates them into a single set of predictions
@@
 
-\par This system model demonstrates a variety of advantages over typical FL architectures:
+\par Compared with typical FL architectures, this proposed system has a variety of advantages:
 \begin{itemize}
 
-  \item Because model gradient updates are used in typical FL, the global model and each client's model must be the same sort of model.
+  \item Because model gradient updates are used in typical FL, the global model and each local model preserved by each client must be the same sort of model.
 Otherwise, the FL aggregation process for the various shapes of model parameters will not be possible.

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Phishing Mechanism-based Detection

@@
 \subsection{Phishing Mechanism-based Detection}
-Byzantine attacks are still a threat for the proposed Ensemble FL.
-Label flipping attacks allows malicious clients to modify their local model.
-They give the local dataset the incorrect labels in order to create a `poisoned' local model.
-When malevolent clients obtain unlabeled data from the central server, they create incorrect predictions (referred to as `poisoned knowledge') and submit them to the central server.
-The central server then aggregates the incorrect predictions as labels for the unlabeled dataset.
-The central server then uses these unlabeled datasets with the erroneous aggregation predictions to train the global model.
-As a result, a faulty global model is created.
-We suggest using labeled data in the design of Ensemble FL to cope with Byzantine attacks, inspired by the idea of ensemble learning.
+The proposed Ensemble FL is still vulnerable to byzantine attacks.
+Malicious clients can modify their local models through label flipping attacks.
+In order to build a `poisoned' local model, they assign inaccurate labels to the local dataset.
+When hostile clients receive unlabeled data from the central server, they make inaccurate predictions (called `poisoned knowledge') and send them to the central server.
+The inaccurate predictions are subsequently aggregated as labels for the unlabeled dataset by the central server.
+The global model is subsequently trained using these unlabeled datasets and the erroneous aggregation predictions by the central server.
+As a result, an incorrect global model emerges.
+To deal with Byzantine attacks in Ensemble FL, we propose using labeled data in the design of Ensemble FL.
 We called labeled data `bait'.
+
   \par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
-Each client $c_i$ preserves its local dataset $d_i$ collected by itself.
-At the beginning of the Ensemble FL process, $c_{i}$ uses its local dataset $d_i$ to train its local model $\mathbf{m_i}$ as
+A local dataset $d_i$ is preserved by each client $c_i$.
+At the beginning of the Ensemble FL process, each local model $\mathbf{m_i}$ is trained by each client $c_i$ via its local dataset $d_i$ as
   \begin{equation}
@@
   \end{equation}
-  \par Step-2: \ul{\textit{Dataset Transferring}} The central server $s$ selects $n$ data samples $D_t$ from the unlabeled dataset $D$ and $m$ data samples $B_t$ from the labeled dataset $B$ preserved by it randomly.
-Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
+  \par Step-2: \ul{\textit{Dataset Transferring}} From the unlabled dataset $D$ and the labeled dataset $B$, the central server randomly selects some data samples to construct the unlabeled dataset $D_t$ and the labeled dataset $B_t$ to construct the $t$th FL iteration's public dataset.
+$D_t$ has $n$ data samples, while $B_t$ has $m$ data samples.
+Then $D_t$ and $B_t$ are sent to each client $c_i$ by $s$ as
   \begin{equation}
-    s \overset{{D_{t},B_{t}}}{\rightarrow} c_{i}.
+    c_{i} \overset{{D_{t},B_{t}}}{\leftarrow}s.
   \end{equation}
-  \par Step-3: \ul{\textit{Label Predicting}} After receiving $D_t$ and $B_t$ from the central server, each client $c_i$ makes predictions of the unlabeled data $D_t$ and the labeled data $B_t$ as
+  \par Step-3: \ul{\textit{Label Predicting}} The predictions of $D_t$ and $B_t$ are made by each client $c_i$ as
   \begin{equation}
@@
   \end{equation}
-  ($c_i$ can not distinguish between $D_t$ and $B_t$) via its local model trained by itself in Step 1 and sends its predictions of $D_t$ and $B_t$ back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
+  ($D_t$ and $B_t$ are mixed together, $c_i$ can not distinguish between them) via its local model and the predictions $\mathbf{k_i^t}$:
   \begin{equation}
@@
       p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
-      \end{vmatrix}.
+      \end{vmatrix}
   \end{equation}
+  is sent back to the central server.
 
@@
     \end{algorithm}
-
-  Malicious clients, unlike benign clients, return the incorrect prediction to the central server $s$ as distilled knowledge.
-  \par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ extracts the predictions of the \textit{`bait'} (the labeled dataset $B_t$) apart from $D_t$ from $\mathbf{k_i^t}$, and calculates the accuracy of the predictions using true label of the \textit{`bait'}:
+  Unlike benign clients, the malicious clients return the incorrect prediction to the central server $s$ to disturb the aggregation process.
+  \par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ needs to identify the Byzantine attackers among all the clients.
+The predictions of the \textit{`bait'} (the labeled dataset $B_t$) are extracted apart from $D_t$ from $\mathbf{k_i^t}$.
+Next, $s$ calculates the accuracy of each client's predictions of $B_t$ using true label of the $B_t$:
   \begin{equation}
@@
   \end{equation}
-  Then $s$ determines which clients have a low accuracy value and classifies them as malicious Byzantine clients.
+  Then the clients with a low accuracy value over predicting $B_t$ are identified as malicious Byzantine clients.
   \par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
@@
   \end{equation}
-  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to derive the labels
+  Then the aggregated knowledge $\mathbf{\hat{k}^t}$ is used to derive the labels by the central server $s$
   \begin{equation}
-    \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
+    \mathbf{\hat{y}^t}= argmax(\mathbf{\hat{k}^t}).
   \end{equation}

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Experiment Setup

@@
 \section{Performance Evaluation}
-In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight)) against untargeted attacks under different experiment settings.
+In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight) in the following parts) against untargeted attacks under different experiment settings.
 Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks.
 Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}.
-Our previous work (noted as FLPhish($\tau$)) utilized a threshold to identify the Byzantine clients.
+Our previous work (noted as FLPhish($\tau$) in the following parts) utilized a threshold to identify the Byzantine clients.
 Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).
@@
 
-  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the circumstances of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
-  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} According to the previous research \cite{ref_06_model}, we distribute the data in a dataset among all the clients.
-Giving $M$ classes of data in a dataset, we split the clients into $M$ groups.
-A client $c$ in group $m$ is provided with data where data $m$ accounts for over $q$ percent.
-Within the same group, data are uniformly distributed among all the clients.
-The parameter $q$ controls the distribution inference of clients' local training data.
-If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed.
-We evaluate our FLPhish(weight) on three different $q$: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
+  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the settings of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
+  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} We distribute the data in a dataset among all the clients, based on previous study \cite{ref_06_model}.
+If a dataset consists if $M$ classes of data, the FL clients will be divided into $M$ groups.
+Data is delivered to a client $c$ in group $m$, with data $m$ accounting for more than $q$ percent.
+Data is uniformly disseminated among all clients within the same group.
+The distribution inference of clients' local training data is controlled by the parameter $q$.
+If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed (IID).
+We evaluate our FLPhish(weight) on 6 different $q$ settings: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
   \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
@@
   \subsubsection{{\textit{The datasets {$d$}}}} We take three different datasets as our experiment datasets: \begin{itemize}
-      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training examples and 10,000 testing examples.
+      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training samples and 10,000 testing samples.
       \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Performance Comparison with Different Distributions Update

@@
 
-    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish(weight) under the experiment setting where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments.
+    \subsubsection{\ul{Performance Comparison with Different Distributions}} We test our FLPhish(weight) in an experiment environment with a fixed Byzantine client fraction of 0.5 and a variable distribution imbalance value $q$ across tests.
 The experiment results are shown in Fig.
 \ref{fig_table_imbalances_untargeted}.
-We can observe that both the FLPhish($\tau$=0.1,0.2,0.5) and FLPhish(weight) outperform baseline until the imbalance degree $q$ reaches 0.8.
-The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID.
-The performance of the FLPhish($\tau$=0.5) rapidly falls in this case.
-When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation.
-The rise of imbalance degree brings an explosive decline in the global model's accuracy.
-The accuracy of the global model under the FLPhish($\tau$=0.5) stays to be 0.1 in the whole learning process.
-It means that the FLPhish($\tau$=0.5) identifies all the clients as Byzantine clients, making the aggregation process invalid.
-We can see that the FLPhish($\tau$=0.2) outperforms others.
-When the distribution becomes non-IID, the threshold of FLPhish($\tau$) should be set to a lower value to avoid a high false-negative rate.
-In the experiment of MNIST, it should be set to 0.2.
-Meanwhile, the performance of FLPhish(weight) remains stable under different imbalance degrees.
+We can see that both FLPhish($\tau$=0.1,0.2,0.5) and FLPhish(weight) outperform other schemes.
+When the imbalance degree $q$ reaches 0.8, the distribution of data becomes very non-IID.
+In this situation, the FLPhish($\tau$=0.5)'s performance progressively deteriorates.
+When confronted with a distribution with an imbalance degree of $q=0.8$, each client performs poorly, resulting in a loss of reputation.
+The accuracy of the global model declines sharply as the degree of imbalance rises.
+Throughout the learning phase, the accuracy of the global model under FLPhish($\tau$=0.5) remains at 0.1.
+It means that FLPhish($\tau$=0.5) considers all clients to be Byzantine, thus invalidating the aggregation process.
+As can be seen, the FLPhish($\tau$=0.2) outperforms the FLPhish($\tau$=0.1,0.5).
+To avoid a high false-negative rate, the threshold $\tau$ of FLPhish($\tau$) should be set to a lower value when the distribution becomes non-IID.
+It should be set to 0.2 in the MNIST experiment.
+Meanwhile, FLPhish(weight) maintains its performance under varying degrees of imbalance.
 

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Reputation Mechanism in Information Security

@@
 This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
-In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
-In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance rule that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}.
-The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system.
-Furthermore, they presented a reputation-based primary change scheme.
-The node with a higher reputation would get greater opportunities to generate new valid blocks, which reduces the security risk of the system.
-In 2020, Chouikhi \textit{et al.} built a model for reputation computing and a credibility model to enhance network efficiency \cite{ref_23_reputation}.
-They used the reputation score or value to measure the behavior of a vehicle towards other vehicles and network services.
-And the credibility of vehicles is used to determine the accuracy of a reputation score offered by a vehicle.
-In the same year, Wen \textit{et al.} proposed a Dirichlet reputation-based scheme and adopt the reputation score to select a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}.
-Furthermore, they developed an artificial noise detection method with multiple thresholds.
-They provided ratings with multiple graded levels.
-In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
-In 2021, Liang \textit{et al.} presented a Markov-based reputation scheme in an intrusion detection system.
-The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.
+To calculate and manage trust and reputation of CSP and SNP services, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor networks and cloud computing in 2015 \cite{ref_47_reputation}.
+Lei \textit{et al.} presented a reputation-based Byzantine Fault Tolerance rule in 2018, which uses a reputation model to assess the performance of each node in the blockchain system \cite{ref_25_reputation}.
+If the system detects any malicious behavior, the nodes' discourse rights and reputation in the voting process are reduced.
+They also provided a primary change method based on reputation.
+The node with a higher reputation would have more chances to generate fresh valid blocks, lowering the system's security risk.
+In 2020, Chouikhi \textit{et al.} developed a reputation computing and credibility model to improve network efficiency \cite{ref_23_reputation}.
+They measured a vehicle's behavior toward other vehicles and network services using its reputation score or worth.
+And a vehicle's credibility is utilized to determine the correctness of a reputation score it offers.
+In the same year, Wen \textit{et al.} designed a Dirichlet reputation-based approach, and used the reputation score to choose a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}.
+Furthermore, they devised a multi-threshold fake noise detection approach.
+They gave ratings on a scale of one to ten.
+The graded ratings were directly represented and reflected in the generated reputation scores in the Dirichlet reputation-based method.
+In 2021, Liang \textit{et al.} introduced an intrusion detection system with a Markov-based reputation algorithm \cite{ref_46_reputation}.
+The RS-HgMTD model of the Hidden Generalized Mixture Transition Distribution (HgMTD) is designed to help each vehicle in the VANET assess the creditworthiness of its neighbors.
 

### 2022-01-28 Manuscript/FLPhish(Trans).tex
grammarly

@@
 In Median, The FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
-In this study, we provide an unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in Ensemble FL, based on the preceding research.
+In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in Ensemble FL, based on the preceding research.
 Our contributions are four-fold:
@@
 
-\par \textit{1)} The typical FL design has a number of flaws, including incompatibility with various deep learning models in different clients and significant communication costs.
+\par \textit{1)} The typical FL design has several flaws, including incompatibility with various deep learning models in different clients and significant communication costs.
 As a result, we created Ensemble FL, a novel FL architecture inspired by the idea of ensemble learning.
@@
 \par \textit{2)} The proposed Ensemble FL architecture currently needs a robust Byzantine attack protection mechanism.
-We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be totally trusted.
+We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be trusted.
 In our proposed Ensemble FL system, we describe a phishing-based approach to guard against Byzantine attacks.
@@
 \par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation.
-Furthermore, we propose an aggregation rules in FLPhish, FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
+Furthermore, we propose an aggregation rule in FLPhish, FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
 
@@
 \par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates.
-While unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resource to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
+While unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
 \subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources, resulting in its local dataset.
@@
 Due to the reduced size of data and labels, transferring data and labels is much faster than transferring models and model gradient updates.
-  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof is in the section IV.B.
+  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof is in section IV.B.
 \end{itemize}

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
Manuscript_TIF init

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\begin{document}

\title{A Sample Article Using IEEEtran.cls\\ for IEEE Journals and Transactions}

\author{IEEE Publication Technology,~\IEEEmembership{Staff,~IEEE,}
        % <-this % stops a space
\thanks{This paper was produced by the IEEE Publication Technology Group. They are in Piscataway, NJ.}% <-this % stops a space
\thanks{Manuscript received April 19, 2021; revised August 16, 2021.}}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2021}%
{Shell \MakeLowercase{\textit{et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}

\IEEEpubid{0000--0000/00\$00.00~\copyright~2021 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

\maketitle

\begin{abstract}
This document describes the most common article elements and how to use the IEEEtran class with \LaTeX \ to produce files that are suitable for submission to the IEEE.  IEEEtran can produce conference, journal, and technical note (correspondence) papers with a suitable choice of class options. \cite{ref_01_GoogleFL}
\end{abstract}

\begin{IEEEkeywords}
Article submission, IEEE, IEEEtran, journal, \LaTeX, paper, template, typesetting.
\end{IEEEkeywords}

\section{Introduction}
\IEEEPARstart{T}{his} file is intended to serve as a ``sample article file''
for IEEE journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later. The most common elements are covered in the simplified and updated instructions in ``New\_IEEEtran\_how-to.pdf''. For less common elements you can refer back to the original ``IEEEtran\_HOWTO.pdf''. It is assumed that the reader has a basic working knowledge of \LaTeX. Those who are new to \LaTeX \ are encouraged to read Tobias Oetiker's ``The Not So Short Introduction to \LaTeX ,'' available at: \url{http://tug.ctan.org/info/lshort/english/lshort.pdf} which provides an overview of working with \LaTeX.

\section{The Design, Intent, and \\ Limitations of the Templates}
The templates are intended to {\bf{approximate the final look and page length of the articles/papers}}. {\bf{They are NOT intended to be the final produced work that is displayed in print or on IEEEXplore\textsuperscript{\textregistered}}}. They will help to give the authors an approximation of the number of pages that will be in the final version. The structure of the \LaTeX\ files, as designed, enable easy conversion to XML for the composition systems used by the IEEE. The XML files are used to produce the final print/IEEEXplore pdf and then converted to HTML for IEEEXplore.

\section{Where to Get \LaTeX \ Help --- User Groups}
The following online groups are helpful to beginning and experienced \LaTeX\ users. A search through their archives can provide many answers to common questions.
\begin{list}{}{}
\item{\url{http://www.latex-community.org/}} 
\item{\url{https://tex.stackexchange.com/} }
\end{list}

\section{Other Resources}
See \cite{ref1,ref2,ref3,ref4,ref5} for resources on formatting math into text and additional help in working with \LaTeX .

\section{Text}
For some of the remainer of this sample we will use dummy text to fill out paragraphs rather than use live text that may violate a copyright.

Itam, que ipiti sum dem velit la sum et dionet quatibus apitet voloritet audam, qui aliciant voloreicid quaspe volorem ut maximusandit faccum conemporerum aut ellatur, nobis arcimus.
Fugit odi ut pliquia incitium latum que cusapere perit molupta eaquaeria quod ut optatem poreiur? Quiaerr ovitior suntiant litio bearciur?

Onseque sequaes rectur autate minullore nusae nestiberum, sum voluptatio. Et ratem sequiam quaspername nos rem repudandae volum consequis nos eium aut as molupta tectum ulparumquam ut maximillesti consequas quas inctia cum volectinusa porrum unt eius cusaest exeritatur? Nias es enist fugit pa vollum reium essusam nist et pa aceaqui quo elibusdandis deligendus que nullaci lloreri bla que sa coreriam explacc atiumquos simolorpore, non prehendunt lam que occum\cite{ref6} si aut aut maximus eliaeruntia dia sequiamenime natem sendae ipidemp orehend uciisi omnienetus most verum, ommolendi omnimus, est, veni aut ipsa volendelist mo conserum volores estisciis recessi nveles ut poressitatur sitiis ex endi diti volum dolupta aut aut odi as eatquo cullabo remquis toreptum et des accus dolende pores sequas dolores tinust quas expel moditae ne sum quiatis nis endipie nihilis etum fugiae audi dia quiasit quibus.
\IEEEpubidadjcol
Ibus el et quatemo luptatque doluptaest et pe volent rem ipidusa eribus utem venimolorae dera qui acea quam etur aceruptat.
Gias anis doluptaspic tem et aliquis alique inctiuntiur?

Sedigent, si aligend elibuscid ut et ium volo tem eictore pellore ritatus ut ut ullatus in con con pere nos ab ium di tem aliqui od magnit repta volectur suntio. Nam isquiante doluptis essit, ut eos suntionsecto debitiur sum ea ipitiis adipit, oditiore, a dolorerempos aut harum ius, atquat.

Rum rem ditinti sciendunti volupiciendi sequiae nonsect oreniatur, volores sition ressimil inus solut ea volum harumqui to see\eqref{deqn_ex1a} mint aut quat eos explis ad quodi debis deliqui aspel earcius.

\begin{equation}
\label{deqn_ex1a}
x = \sum_{i=0}^{n} 2{i} Q.
\end{equation}

Alis nime volorempera perferi sitio denim repudae pre ducilit atatet volecte ssimillorae dolore, ut pel ipsa nonsequiam in re nus maiost et que dolor sunt eturita tibusanis eatent a aut et dio blaudit reptibu scipitem liquia consequodi od unto ipsae. Et enitia vel et experferum quiat harum sa net faccae dolut voloria nem. Bus ut labo. Ita eum repraer rovitia samendit aut et volupta tecupti busant omni quiae porro que nossimodic temquis anto blacita conse nis am, que ereperum eumquam quaescil imenisci quae magnimos recus ilibeaque cum etum iliate prae parumquatemo blaceaquiam quundia dit apienditem rerit re eici quaes eos sinvers pelecabo. Namendignis as exerupit aut magnim ium illabor roratecte plic tem res apiscipsam et vernat untur a deliquaest que non cus eat ea dolupiducim fugiam volum hil ius dolo eaquis sitis aut landesto quo corerest et auditaquas ditae voloribus, qui optaspis exero cusa am, ut plibus.

\section{Some Common Elements}
\subsection{Sections and Subsections}
Enumeration of section headings is desirable, but not required. When numbered, please be consistent throughout the article, that is, all headings and all levels of section headings in the article should be enumerated. Primary headings are designated with Roman numerals, secondary with capital letters, tertiary with Arabic numbers; and quaternary with lowercase letters. Reference and Acknowledgment headings are unlike all other section headings in text. They are never enumerated. They are simply primary headings without labels, regardless of whether the other headings in the article are enumerated.

\subsection{Citations to the Bibliography}
The coding for the citations is made with the \LaTeX\ $\backslash${\tt{cite}} command. 
This will display as: see \cite{ref1}.

For multiple citations code as follows: {\tt{$\backslash$cite\{ref1,ref2,ref3\}}}
 which will produce \cite{ref1,ref2,ref3}. For reference ranges that are not consecutive code as {\tt{$\backslash$cite\{ref1,ref2,ref3,ref9\}}} which will produce  \cite{ref1,ref2,ref3,ref9}

\subsection{Lists}
In this section, we will consider three types of lists: simple unnumbered, numbered, and bulleted. There have been many options added to IEEEtran to enhance the creation of lists. If your lists are more complex than those shown below, please refer to the original ``IEEEtran\_HOWTO.pdf'' for additional options.\\

\subsubsection*{\bf A plain  unnumbered list}
\begin{list}{}{}
\item{bare\_jrnl.tex}
\item{bare\_conf.tex}
\item{bare\_jrnl\_compsoc.tex}
\item{bare\_conf\_compsoc.tex}
\item{bare\_jrnl\_comsoc.tex}
\end{list}

\subsubsection*{\bf A simple numbered list}
\begin{enumerate}
\item{bare\_jrnl.tex}
\item{bare\_conf.tex}
\item{bare\_jrnl\_compsoc.tex}
\item{bare\_conf\_compsoc.tex}
\item{bare\_jrnl\_comsoc.tex}
\end{enumerate}

\subsubsection*{\bf A simple bulleted list}
\begin{itemize}
\item{bare\_jrnl.tex}
\item{bare\_conf.tex}
\item{bare\_jrnl\_compsoc.tex}
\item{bare\_conf\_compsoc.tex}
\item{bare\_jrnl\_comsoc.tex}
\end{itemize}

\subsection{Figures}
Fig. 1 is an example of a floating figure using the graphicx package.
 Note that $\backslash${\tt{label}} must occur AFTER (or within) $\backslash${\tt{caption}}.
 For figures, $\backslash${\tt{caption}} should occur after the $\backslash${\tt{includegraphics}}.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{fig1}
\caption{Simulation results for the network.}
\label{fig_1}
\end{figure}

Fig. 2(a) and 2(b) is an example of a double column floating figure using two subfigures.
 (The subfig.sty package must be loaded for this to work.)
 The subfigure $\backslash${\tt{label}} commands are set within each subfloat command,
 and the $\backslash${\tt{label}} for the overall figure must come after $\backslash${\tt{caption}}.
 $\backslash${\tt{hfil}} is used as a separator to get equal spacing.
 The combined width of all the parts of the figure should do not exceed the text width or a line break will occur.
%
\begin{figure*}[!t]
\centering
\subfloat[]{\includegraphics[width=2.5in]{fig1}%
\label{fig_first_case}}
\hfil
\subfloat[]{\includegraphics[width=2.5in]{fig1}%
\label{fig_second_case}}
\caption{Dae. Ad quatur autat ut porepel itemoles dolor autem fuga. Bus quia con nessunti as remo di quatus non perum que nimus. (a) Case I. (b) Case II.}
\label{fig_sim}
\end{figure*}

Note that often IEEE papers with multi-part figures do not place the labels within the image itself (using the optional argument to $\backslash${\tt{subfloat}}[]), but instead will
 reference/describe all of them (a), (b), etc., within the main caption.
 Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
 labels, the optional argument to $\backslash${\tt{subfloat}} must be present. If a
 subcaption is not desired, leave its contents blank,
 e.g.,$\backslash${\tt{subfloat}}[].

\section{Tables}
Note that, for IEEE-style tables, the
 $\backslash${\tt{caption}} command should come BEFORE the table. Table captions use title case. Articles (a, an, the), coordinating conjunctions (and, but, for, or, nor), and most short prepositions are lowercase unless they are the first or last word. Table text will default to $\backslash${\tt{footnotesize}} as
 the IEEE normally uses this smaller font for tables.
 The $\backslash${\tt{label}} must come after $\backslash${\tt{caption}} as always.

\begin{table}[!t]
\caption{An Example of a Table\label{tab:table1}}
\centering
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{table}

\section{Algorithms}
Algorithms should be numbered and include a short title. They are set off from the text with rules above and below the title and after the last line.

\begin{algorithm}[H]
\caption{Weighted Tanimoto ELM.}\label{alg:alg1}
\begin{algorithmic}
\STATE 
\STATE {\textsc{TRAIN}}$(\mathbf{X} \mathbf{T})$
\STATE \hspace{0.5cm}$ \textbf{select randomly } W \subset \mathbf{X}  $
\STATE \hspace{0.5cm}$ N_\mathbf{t} \gets | \{ i : \mathbf{t}_i = \mathbf{t} \} | $ \textbf{ for } $ \mathbf{t}= -1,+1 $
\STATE \hspace{0.5cm}$ B_i \gets \sqrt{ \textsc{max}(N_{-1},N_{+1}) / N_{\mathbf{t}_i} } $ \textbf{ for } $ i = 1,...,N $
\STATE \hspace{0.5cm}$ \hat{\mathbf{H}} \gets  B \cdot (\mathbf{X}^T\textbf{W})/( \mathbb{1}\mathbf{X} + \mathbb{1}\textbf{W} - \mathbf{X}^T\textbf{W} ) $
\STATE \hspace{0.5cm}$ \beta \gets \left ( I/C + \hat{\mathbf{H}}^T\hat{\mathbf{H}} \right )^{-1}(\hat{\mathbf{H}}^T B\cdot \mathbf{T})  $
\STATE \hspace{0.5cm}\textbf{return}  $\textbf{W},  \beta $
\STATE 
\STATE {\textsc{PREDICT}}$(\mathbf{X} )$
\STATE \hspace{0.5cm}$ \mathbf{H} \gets  (\mathbf{X}^T\textbf{W} )/( \mathbb{1}\mathbf{X}  + \mathbb{1}\textbf{W}- \mathbf{X}^T\textbf{W}  ) $
\STATE \hspace{0.5cm}\textbf{return}  $\textsc{sign}( \mathbf{H} \beta )$
\end{algorithmic}
\label{alg1}
\end{algorithm}

Que sunt eum lam eos si dic to estist, culluptium quid qui nestrum nobis reiumquiatur minimus minctem. Ro moluptat fuga. Itatquiam ut laborpo rersped exceres vollandi repudaerem. Ulparci sunt, qui doluptaquis sumquia ndestiu sapient iorepella sunti veribus. Ro moluptat fuga. Itatquiam ut laborpo rersped exceres vollandi repudaerem. 
\section{Mathematical Typography \\ and Why It Matters}

Typographical conventions for mathematical formulas have been developed to {\bf provide uniformity and clarity of presentation across mathematical texts}. This enables the readers of those texts to both understand the author's ideas and to grasp new concepts quickly. While software such as \LaTeX \ and MathType\textsuperscript{\textregistered} can produce aesthetically pleasing math when used properly, it is also very easy to misuse the software, potentially resulting in incorrect math display.

IEEE aims to provide authors with the proper guidance on mathematical typesetting style and assist them in writing the best possible article. As such, IEEE has assembled a set of examples of good and bad mathematical typesetting \cite{ref1,ref2,ref3,ref4,ref5}.

Further examples can be found at \url{http://journals.ieeeauthorcenter.ieee.org/wp-content/uploads/sites/7/IEEE-Math-Typesetting-Guide-for-LaTeX-Users.pdf}

\subsection{Display Equations}
The simple display equation example shown below uses the ``equation'' environment. To number the equations, use the $\backslash${\tt{label}} macro to create an identifier for the equation. LaTeX will automatically number the equation for you.
\begin{equation}
\label{deqn_ex1}
x = \sum_{i=0}^{n} 2{i} Q.
\end{equation}

\noindent is coded as follows:
\begin{verbatim}
\begin{equation}
\label{deqn_ex1}
x = \sum_{i=0}^{n} 2{i} Q.
\end{equation}
\end{verbatim}

To reference this equation in the text use the $\backslash${\tt{ref}} macro. 
Please see (\ref{deqn_ex1})\\
\noindent is coded as follows:
\begin{verbatim}
Please see (\ref{deqn_ex1})\end{verbatim}

\subsection{Equation Numbering}
{\bf{Consecutive Numbering:}} Equations within an article are numbered consecutively from the beginning of the
article to the end, i.e., (1), (2), (3), (4), (5), etc. Do not use roman numerals or section numbers for equation numbering.

\noindent {\bf{Appendix Equations:}} The continuation of consecutively numbered equations is best in the Appendix, but numbering
 as (A1), (A2), etc., is permissible.\\

\noindent {\bf{Hyphens and Periods}}: Hyphens and periods should not be used in equation numbers, i.e., use (1a) rather than
(1-a) and (2a) rather than (2.a) for subequations. This should be consistent throughout the article.

\subsection{Multi-Line Equations and Alignment}
Here we show several examples of multi-line equations and proper alignments.

\noindent {\bf{A single equation that must break over multiple lines due to length with no specific alignment.}}
\begin{multline}
\text{The first line of this example}\\
\text{The second line of this example}\\
\text{The third line of this example}
\end{multline}

\noindent is coded as:
\begin{verbatim}
\begin{multline}
\text{The first line of this example}\\
\text{The second line of this example}\\
\text{The third line of this example}
\end{multline}
\end{verbatim}

\noindent {\bf{A single equation with multiple lines aligned at the = signs}}
\begin{align}
a &= c+d \\
b &= e+f
\end{align}
\noindent is coded as:
\begin{verbatim}
\begin{align}
a &= c+d \\
b &= e+f
\end{align}
\end{verbatim}

The {\tt{align}} environment can align on multiple  points as shown in the following example:
\begin{align}
x &= y & X & =Y & a &=bc\\
x' &= y' & X' &=Y' &a' &=bz
\end{align}
\noindent is coded as:
\begin{verbatim}
\begin{align}
x &= y & X & =Y & a &=bc\\
x' &= y' & X' &=Y' &a' &=bz
\end{align}
\end{verbatim}

\subsection{Subnumbering}
The amsmath package provides a {\tt{subequations}} environment to facilitate subnumbering. An example:

\begin{subequations}\label{eq:2}
\begin{align}
f&=g \label{eq:2A}\\
f' &=g' \label{eq:2B}\\
\mathcal{L}f &= \mathcal{L}g \label{eq:2c}
\end{align}
\end{subequations}

\noindent is coded as:
\begin{verbatim}
\begin{subequations}\label{eq:2}
\begin{align}
f&=g \label{eq:2A}\\
f' &=g' \label{eq:2B}\\
\mathcal{L}f &= \mathcal{L}g \label{eq:2c}
\end{align}
\end{subequations}

\end{verbatim}

\subsection{Matrices}
There are several useful matrix environments that can save you some keystrokes. See the example coding below and the output.

\noindent {\bf{A simple matrix:}}
\begin{equation}
\begin{matrix}  0 &  1 \\ 
1 &  0 \end{matrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{matrix}  0 &  1 \\ 
1 &  0 \end{matrix}
\end{equation}
\end{verbatim}

\noindent {\bf{A matrix with parenthesis}}
\begin{equation}
\begin{pmatrix} 0 & -i \\
 i &  0 \end{pmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{pmatrix} 0 & -i \\
 i &  0 \end{pmatrix}
\end{equation}
\end{verbatim}

\noindent {\bf{A matrix with square brackets}}
\begin{equation}
\begin{bmatrix} 0 & -1 \\ 
1 &  0 \end{bmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{bmatrix} 0 & -1 \\ 
1 &  0 \end{bmatrix}
\end{equation}
\end{verbatim}

\noindent {\bf{A matrix with curly braces}}
\begin{equation}
\begin{Bmatrix} 1 &  0 \\ 
0 & -1 \end{Bmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{Bmatrix} 1 &  0 \\ 
0 & -1 \end{Bmatrix}
\end{equation}\end{verbatim}

\noindent {\bf{A matrix with single verticals}}
\begin{equation}
\begin{vmatrix} a &  b \\ 
c &  d \end{vmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{vmatrix} a &  b \\ 
c &  d \end{vmatrix}
\end{equation}\end{verbatim}

\noindent {\bf{A matrix with double verticals}}
\begin{equation}
\begin{Vmatrix} i &  0 \\ 
0 & -i \end{Vmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{Vmatrix} i &  0 \\ 
0 & -i \end{Vmatrix}
\end{equation}\end{verbatim}

\subsection{Arrays}
The {\tt{array}} environment allows you some options for matrix-like equations. You will have to manually key the fences, but there are other options for alignment of the columns and for setting horizontal and vertical rules. The argument to {\tt{array}} controls alignment and placement of vertical rules.

A simple array
\begin{equation}
\left(
\begin{array}{cccc}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array}\right)
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\left(
\begin{array}{cccc}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array} \right)
\end{equation}
\end{verbatim}

A slight variation on this to better align the numbers in the last column
\begin{equation}
\left(
\begin{array}{cccr}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array}\right)
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\left(
\begin{array}{cccr}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array} \right)
\end{equation}
\end{verbatim}

An array with vertical and horizontal rules
\begin{equation}
\left( \begin{array}{c|c|c|r}
a+b+c & uv & x-y & 27\\ \hline
a+b & u+v & z & 134
\end{array}\right)
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\left(
\begin{array}{c|c|c|r}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array} \right)
\end{equation}
\end{verbatim}
Note the argument now has the pipe "$\vert$" included to indicate the placement of the vertical rules.

\subsection{Cases Structures}
Many times cases can be miscoded using the wrong environment, i.e., {\tt{array}}. Using the {\tt{cases}} environment will save keystrokes (from not having to type the $\backslash${\tt{left}}$\backslash${\tt{lbrace}}) and automatically provide the correct column alignment.
\begin{equation*}
{z_m(t)} = \begin{cases}
1,&{\text{if}}\ {\beta }_m(t) \\ 
{0,}&{\text{otherwise.}} 
\end{cases}
\end{equation*}
\noindent is coded as follows:
\begin{verbatim}
\begin{equation*}
{z_m(t)} = 
\begin{cases}
1,&{\text{if}}\ {\beta }_m(t),\\ 
{0,}&{\text{otherwise.}} 
\end{cases}
\end{equation*}
\end{verbatim}
\noindent Note that the ``\&'' is used to mark the tabular alignment. This is important to get  proper column alignment. Do not use $\backslash${\tt{quad}} or other fixed spaces to try and align the columns. Also, note the use of the $\backslash${\tt{text}} macro for text elements such as ``if'' and ``otherwise.''

\subsection{Function Formatting in Equations}
Often, there is an easy way to properly format most common functions. Use of the $\backslash$ in front of the function name will in most cases, provide the correct formatting. When this does not work, the following example provides a solution using the $\backslash${\tt{text}} macro:

\begin{equation*} 
  d_{R}^{KM} = \underset {d_{l}^{KM}} {\text{arg min}} \{ d_{1}^{KM},\ldots,d_{6}^{KM}\}.
\end{equation*}

\noindent is coded as follows:
\begin{verbatim}
\begin{equation*} 
 d_{R}^{KM} = \underset {d_{l}^{KM}} 
 {\text{arg min}} \{ d_{1}^{KM},
 \ldots,d_{6}^{KM}\}.
\end{equation*}
\end{verbatim}

\subsection{ Text Acronyms Inside Equations}
This example shows where the acronym ``MSE" is coded using $\backslash${\tt{text\{\}}} to match how it appears in the text.

\begin{equation*}
 \text{MSE} = \frac {1}{n}\sum _{i=1}^{n}(Y_{i} - \hat {Y_{i}})^{2}
\end{equation*}

\begin{verbatim}
\begin{equation*}
 \text{MSE} = \frac {1}{n}\sum _{i=1}^{n}
(Y_{i} - \hat {Y_{i}})^{2}
\end{equation*}
\end{verbatim}

\section{Conclusion}
The conclusion goes here.

\section*{Acknowledgments}
This should be a simple paragraph before the References to thank those individuals and institutions who have supported your work on this article.

{\appendix[Proof of the Zonklar Equations]
Use $\backslash${\tt{appendix}} if you have a single appendix:
Do not use $\backslash${\tt{section}} anymore after $\backslash${\tt{appendix}}, only $\backslash${\tt{section*}}.
If you have multiple appendixes use $\backslash${\tt{appendices}} then use $\backslash${\tt{section}} to start each appendix.
You must declare a $\backslash${\tt{section}} before using any $\backslash${\tt{subsection}} or using $\backslash${\tt{label}} ($\backslash${\tt{appendices}} by itself
 starts a section numbered zero.)}

%{\appendices
%\section*{Proof of the First Zonklar Equation}
%Appendix one text goes here.
% You can choose not to have a title for an appendix if you want by leaving the argument blank
%\section*{Proof of the Second Zonklar Equation}
%Appendix two text goes here.}

\section{References Section}
You can use a bibliography generated by BibTeX as a .bbl file.
 BibTeX documentation can be easily obtained at:
 http://mirror.ctan.org/biblio/bibtex/contrib/doc/
 The IEEEtran BibTeX style support page is:
 http://www.michaelshell.org/tex/ieeetran/bibtex/

 % argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
\section{Simple References}
You can manually copy in the resultant .bbl file and set second argument of $\backslash${\tt{begin}} to the number of references
 (used to reserve space for the reference number labels box).

 \bibliography{IEEEabbrv}
\begin{thebibliography}{1}
\bibliographystyle{IEEEtran}

\bibitem{ref1}
{\it{Mathematics Into Type}}. American Mathematical Society. [Online]. Available: https://www.ams.org/arc/styleguide/mit-2.pdf

\bibitem{ref2}
T. W. Chaundy, P. R. Barrett and C. Batey, {\it{The Printing of Mathematics}}. London, U.K., Oxford Univ. Press, 1954.

\bibitem{ref3}
F. Mittelbach and M. Goossens, {\it{The \LaTeX Companion}}, 2nd ed. Boston, MA, USA: Pearson, 2004.

\bibitem{ref4}
G. Gr\"atzer, {\it{More Math Into LaTeX}}, New York, NY, USA: Springer, 2007.

\bibitem{ref5}M. Letourneau and J. W. Sharp, {\it{AMS-StyleGuide-online.pdf,}} American Mathematical Society, Providence, RI, USA, [Online]. Available: http://www.ams.org/arc/styleguide/index.html

\bibitem{ref6}
H. Sira-Ramirez, ``On the sliding mode control of nonlinear systems,'' \textit{Syst. Control Lett.}, vol. 19, pp. 303--312, 1992.

\bibitem{ref7}
A. Levant, ``Exact differentiation of signals with unbounded higher derivatives,''  in \textit{Proc. 45th IEEE Conf. Decis.
Control}, San Diego, CA, USA, 2006, pp. 5585--5590. DOI: 10.1109/CDC.2006.377165.

\bibitem{ref8}
M. Fliess, C. Join, and H. Sira-Ramirez, ``Non-linear estimation is easy,'' \textit{Int. J. Model., Ident. Control}, vol. 4, no. 1, pp. 12--27, 2008.

\bibitem{ref9}
R. Ortega, A. Astolfi, G. Bastin, and H. Rodriguez, ``Stabilization of food-chain systems using a port-controlled Hamiltonian description,'' in \textit{Proc. Amer. Control Conf.}, Chicago, IL, USA,
2000, pp. 2245--2249.

\end{thebibliography}

\newpage

\section{Biography Section}
If you have an EPS/PDF photo (graphicx package needed), extra braces are
 needed around the contents of the optional argument to biography to prevent
 the LaTeX parser from getting confused when it sees the complicated
 $\backslash${\tt{includegraphics}} command within an optional argument. (You can create
 your own custom macro containing the $\backslash${\tt{includegraphics}} command to make things
 simpler here.)

\vspace{11pt}

\bf{If you include a photo:}\vspace{-33pt}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig1}}]{Michael Shell}
Use $\backslash${\tt{begin\{IEEEbiography\}}} and then for the 1st argument use $\backslash${\tt{includegraphics}} to declare and link the author photo.
Use the author name as the 3rd argument followed by the biography text.
\end{IEEEbiography}

\vspace{11pt}

\bf{If you will not include a photo:}\vspace{-33pt}
\begin{IEEEbiographynophoto}{John Doe}
Use $\backslash${\tt{begin\{IEEEbiographynophoto\}}} and the author name as the argument followed by the biography text.
\end{IEEEbiographynophoto}

\vfill

\end{document}

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
Basic information

@@
 \usepackage{cite}
+
+%\usepackage{float}
+%\usepackage{multirow}
+%\usepackage{tabularx}
+%\usepackage{authblk}
+\usepackage{booktabs}
 \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
@@
 \begin{document}
-
-\title{A Sample Article Using IEEEtran.cls\\ for IEEE Journals and Transactions}
-
-\author{IEEE Publication Technology,~\IEEEmembership{Staff,~IEEE,}
-        % <-this % stops a space
-\thanks{This paper was produced by the IEEE Publication Technology Group. They are in Piscataway, NJ.}% <-this % stops a space
-\thanks{Manuscript received April 19, 2021; revised August 16, 2021.}}
+\title{Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}
+\author{Beibei~Li,~\IEEEmembership{Member,~IEEE,}
+        Peiran~Wang,~\IEEEmembership{Student Member,~IEEE,}
+        Qinglei~Kong,~\IEEEmembership{Member,~IEEE,}
+        Yuan~Zhang,~\IEEEmembership{Member,~IEEE,}
+        and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
+\thanks{This paper is an extended version of the paper titled `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in IEEE ISCC 2021, and awarded `Best Paper'.}
+\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
+\thanks{Q.
+Kong is with the Future Network of Intelligence Institute, The Chinese University of Hong Kong, Shenzhen, China 518172, and also with The University of Science and Technology of China, Hefei, China 230052.
+Email: kql8904@163.com.}
+\thanks{Y. Zhang is with the School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
+\thanks{R. Lu is with the Faculty of Computer Science, University of New Brunswick, Fredericton, NB, Canada E3B 5A3. Email: rlu1@unb.ca.}
+}
 
 % The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2021}%
-{Shell \MakeLowercase{\textit{et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}
+\markboth{IEEE TRANSACTIONS ON INFORMATION FORENSICS AND SECURITY}%
+{Li \MakeLowercase{\textit{et al.}}: Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}
 
@@
 \begin{abstract}
-This document describes the most common article elements and how to use the IEEEtran class with \LaTeX \ to produce files that are suitable for submission to the IEEE.
-IEEEtran can produce conference, journal, and technical note (correspondence) papers with a suitable choice of class options.
+  Emerging as a promising distributed learning paradigm, federated learning (FL) has been widely adopted in many fields.
+Nonetheless, a big challenge for FL in real-world implementation is Byzantine attacks, where compromised clients can mislead or poison the training model by falsifying or manipulating the local model parameters.
+To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme (called FLPhish) for defending Byzantine attacks under the Ensemble Federated Learning architecture (called EFL).
+Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL compatible with different deep learning models in different clients.
+Second, we craft a phishing algorithm for the EFL architecture to identify possible Byzantine behaviors.
+Third, a Bayesian inference based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine clients.
+Last, we strictly analyze how the FLPhish scheme defend against backdoor attacks.
+Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL.
+FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance.
 \cite{ref_01_GoogleFL}
@@
 \begin{IEEEkeywords}
-Article submission, IEEE, IEEEtran, journal, \LaTeX, paper, template, typesetting.
+  Federated learning, ensemble learning, Bayesian inference-based reputation, phishing.
 \end{IEEEkeywords}
 
-\section{Introduction}
-\IEEEPARstart{T}{his} file is intended to serve as a ``sample article file''
-for IEEE journal papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8b and later.
-The most common elements are covered in the simplified and updated instructions in ``New\_IEEEtran\_how-to.pdf''.
-For less common elements you can refer back to the original ``IEEEtran\_HOWTO.pdf''.
-It is assumed that the reader has a basic working knowledge of \LaTeX.
-Those who are new to \LaTeX \ are encouraged to read Tobias Oetiker's ``The Not So Short Introduction to \LaTeX ,'' available at: \url{http://tug.ctan.org/info/lshort/english/lshort.pdf} which provides an overview of working with \LaTeX.
-
-\section{The Design, Intent, and \\ Limitations of the Templates}
-The templates are intended to {\bf{approximate the final look and page length of the articles/papers}}.
-{\bf{They are NOT intended to be the final produced work that is displayed in print or on IEEEXplore\textsuperscript{\textregistered}}}.
-They will help to give the authors an approximation of the number of pages that will be in the final version.
-The structure of the \LaTeX\ files, as designed, enable easy conversion to XML for the composition systems used by the IEEE.
-The XML files are used to produce the final print/IEEEXplore pdf and then converted to HTML for IEEEXplore.
-
-\section{Where to Get \LaTeX \ Help --- User Groups}
-The following online groups are helpful to beginning and experienced \LaTeX\ users. A search through their archives can provide many answers to common questions.
-\begin{list}{}{}
-\item{\url{http://www.latex-community.org/}} 
-\item{\url{https://tex.stackexchange.com/} }
-\end{list}
-
-\section{Other Resources}
-See \cite{ref1,ref2,ref3,ref4,ref5} for resources on formatting math into text and additional help in working with \LaTeX .
-
-\section{Text}
-For some of the remainer of this sample we will use dummy text to fill out paragraphs rather than use live text that may violate a copyright.
-
-Itam, que ipiti sum dem velit la sum et dionet quatibus apitet voloritet audam, qui aliciant voloreicid quaspe volorem ut maximusandit faccum conemporerum aut ellatur, nobis arcimus.
-Fugit odi ut pliquia incitium latum que cusapere perit molupta eaquaeria quod ut optatem poreiur? Quiaerr ovitior suntiant litio bearciur?
-
-Onseque sequaes rectur autate minullore nusae nestiberum, sum voluptatio.
-Et ratem sequiam quaspername nos rem repudandae volum consequis nos eium aut as molupta tectum ulparumquam ut maximillesti consequas quas inctia cum volectinusa porrum unt eius cusaest exeritatur?
-Nias es enist fugit pa vollum reium essusam nist et pa aceaqui quo elibusdandis deligendus que nullaci lloreri bla que sa coreriam explacc atiumquos simolorpore, non prehendunt lam que occum\cite{ref6} si aut aut maximus eliaeruntia dia sequiamenime natem sendae ipidemp orehend uciisi omnienetus most verum, ommolendi omnimus, est, veni aut ipsa volendelist mo conserum volores estisciis recessi nveles ut poressitatur sitiis ex endi diti volum dolupta aut aut odi as eatquo cullabo remquis toreptum et des accus dolende pores sequas dolores tinust quas expel moditae ne sum quiatis nis endipie nihilis etum fugiae audi dia quiasit quibus.
-\IEEEpubidadjcol
-Ibus el et quatemo luptatque doluptaest et pe volent rem ipidusa eribus utem venimolorae dera qui acea quam etur aceruptat.
-Gias anis doluptaspic tem et aliquis alique inctiuntiur?
-
-Sedigent, si aligend elibuscid ut et ium volo tem eictore pellore ritatus ut ut ullatus in con con pere nos ab ium di tem aliqui od magnit repta volectur suntio.
-Nam isquiante doluptis essit, ut eos suntionsecto debitiur sum ea ipitiis adipit, oditiore, a dolorerempos aut harum ius, atquat.
-
-Rum rem ditinti sciendunti volupiciendi sequiae nonsect oreniatur, volores sition ressimil inus solut ea volum harumqui to see\eqref{deqn_ex1a} mint aut quat eos explis ad quodi debis deliqui aspel earcius.
-
-\begin{equation}
-\label{deqn_ex1a}
-x = \sum_{i=0}^{n} 2{i} Q.
-\end{equation}
-
-Alis nime volorempera perferi sitio denim repudae pre ducilit atatet volecte ssimillorae dolore, ut pel ipsa nonsequiam in re nus maiost et que dolor sunt eturita tibusanis eatent a aut et dio blaudit reptibu scipitem liquia consequodi od unto ipsae.
-Et enitia vel et experferum quiat harum sa net faccae dolut voloria nem.
-Bus ut labo.
-Ita eum repraer rovitia samendit aut et volupta tecupti busant omni quiae porro que nossimodic temquis anto blacita conse nis am, que ereperum eumquam quaescil imenisci quae magnimos recus ilibeaque cum etum iliate prae parumquatemo blaceaquiam quundia dit apienditem rerit re eici quaes eos sinvers pelecabo.
-Namendignis as exerupit aut magnim ium illabor roratecte plic tem res apiscipsam et vernat untur a deliquaest que non cus eat ea dolupiducim fugiam volum hil ius dolo eaquis sitis aut landesto quo corerest et auditaquas ditae voloribus, qui optaspis exero cusa am, ut plibus.
-
-\section{Some Common Elements}
-\subsection{Sections and Subsections}
-Enumeration of section headings is desirable, but not required.
-When numbered, please be consistent throughout the article, that is, all headings and all levels of section headings in the article should be enumerated.
-Primary headings are designated with Roman numerals, secondary with capital letters, tertiary with Arabic numbers; and quaternary with lowercase letters.
-Reference and Acknowledgment headings are unlike all other section headings in text.
-They are never enumerated.
-They are simply primary headings without labels, regardless of whether the other headings in the article are enumerated.
-
-\subsection{Citations to the Bibliography}
-The coding for the citations is made with the \LaTeX\ $\backslash${\tt{cite}} command. 
-This will display as: see \cite{ref1}.
-
-For multiple citations code as follows: {\tt{$\backslash$cite\{ref1,ref2,ref3\}}}
- which will produce \cite{ref1,ref2,ref3}. For reference ranges that are not consecutive code as {\tt{$\backslash$cite\{ref1,ref2,ref3,ref9\}}} which will produce  \cite{ref1,ref2,ref3,ref9}
-
-\subsection{Lists}
-In this section, we will consider three types of lists: simple unnumbered, numbered, and bulleted.
-There have been many options added to IEEEtran to enhance the creation of lists.
-If your lists are more complex than those shown below, please refer to the original ``IEEEtran\_HOWTO.pdf'' for additional options.\\
-
-\subsubsection*{\bf A plain  unnumbered list}
-\begin{list}{}{}
-\item{bare\_jrnl.tex}
-\item{bare\_conf.tex}
-\item{bare\_jrnl\_compsoc.tex}
-\item{bare\_conf\_compsoc.tex}
-\item{bare\_jrnl\_comsoc.tex}
-\end{list}
-
-\subsubsection*{\bf A simple numbered list}
-\begin{enumerate}
-\item{bare\_jrnl.tex}
-\item{bare\_conf.tex}
-\item{bare\_jrnl\_compsoc.tex}
-\item{bare\_conf\_compsoc.tex}
-\item{bare\_jrnl\_comsoc.tex}
-\end{enumerate}
-
-\subsubsection*{\bf A simple bulleted list}
-\begin{itemize}
-\item{bare\_jrnl.tex}
-\item{bare\_conf.tex}
-\item{bare\_jrnl\_compsoc.tex}
-\item{bare\_conf\_compsoc.tex}
-\item{bare\_jrnl\_comsoc.tex}
-\end{itemize}
-
-\subsection{Figures}
-Fig. 1 is an example of a floating figure using the graphicx package.
- Note that $\backslash${\tt{label}} must occur AFTER (or within) $\backslash${\tt{caption}}.
- For figures, $\backslash${\tt{caption}} should occur after the $\backslash${\tt{includegraphics}}.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=2.5in]{fig1}
-\caption{Simulation results for the network.}
-\label{fig_1}
-\end{figure}
-
-Fig. 2(a) and 2(b) is an example of a double column floating figure using two subfigures.
- (The subfig.sty package must be loaded for this to work.)
- The subfigure $\backslash${\tt{label}} commands are set within each subfloat command,
- and the $\backslash${\tt{label}} for the overall figure must come after $\backslash${\tt{caption}}.
- $\backslash${\tt{hfil}} is used as a separator to get equal spacing.
- The combined width of all the parts of the figure should do not exceed the text width or a line break will occur.
-%
-\begin{figure*}[!t]
-\centering
-\subfloat[]{\includegraphics[width=2.5in]{fig1}%
-\label{fig_first_case}}
-\hfil
-\subfloat[]{\includegraphics[width=2.5in]{fig1}%
-\label{fig_second_case}}
-\caption{Dae. Ad quatur autat ut porepel itemoles dolor autem fuga. Bus quia con nessunti as remo di quatus non perum que nimus. (a) Case I. (b) Case II.}
-\label{fig_sim}
-\end{figure*}
-
-Note that often IEEE papers with multi-part figures do not place the labels within the image itself (using the optional argument to $\backslash${\tt{subfloat}}[]), but instead will
- reference/describe all of them (a), (b), etc., within the main caption.
- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
- labels, the optional argument to $\backslash${\tt{subfloat}} must be present. If a
- subcaption is not desired, leave its contents blank,
- e.g.,$\backslash${\tt{subfloat}}[].
-
-\section{Tables}
-Note that, for IEEE-style tables, the
- $\backslash${\tt{caption}} command should come BEFORE the table.
-Table captions use title case.
-Articles (a, an, the), coordinating conjunctions (and, but, for, or, nor), and most short prepositions are lowercase unless they are the first or last word.
-Table text will default to $\backslash${\tt{footnotesize}} as
- the IEEE normally uses this smaller font for tables.
- The $\backslash${\tt{label}} must come after $\backslash${\tt{caption}} as always.
-
-\begin{table}[!t]
-\caption{An Example of a Table\label{tab:table1}}
-\centering
-\begin{tabular}{|c||c|}
+\begin{table}[t]
+  \caption{Summary of Notations}
+  \resizebox{0.5\textwidth}{!}{
+  \begin{tabular}{lp{6cm}}
+    \bottomrule
+    Term&Description\\
     \hline
-One & Two\\
-\hline
-Three & Four\\
+    $s$ & central server in FL \\
+    $c_i$ & the $i$th client in FL, $i=1,2,3,...,u$ \\
+    $d_i$ & the local dataset preserved by the $i$th client \\
+    $C$ & the ensemble of all the clients \\
+    $u$ & the number of clients\\
+    $D_t$ & the unlabeled dataset chosen by $s$ in each procedure\\
+    $D$ & the unlabeled dataset preserved by $s$\\
+    $n$ & the number of samples in $D_t$\\
+    $B_t$ & the labeled dataset (\textit{`bait'}) chosen by $s$ in each procedure\\
+    $B$ & the labeled dataset preserved by $s$\\
+    $m$ & the number of samples in $B_t$\\
+    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$ in $t$th procedure\\
+    $q_i$ & the label of $c_i$ to judge it is a malicious client or not\\
+    $r_q$ & the threhold of malicious clients\\
+    $x^t_l$ & the $l$th data point in $D_t$\\
+    $b_i$ & the Byzantine attacker\\
+    $\sigma$ & the `trigger' in the backdoor attack\\
+    $\iota$ & the backdoor label in the backdoor attack\\
+    $\mathbf{M}$ & global model preserved by $s$\\
+    $\mathbf{m_i}$ & local models trained by the $i$th client\\
+    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
+    $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
+    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$th data point made by $i$th client\\
+    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th iteration's unlabeled dataset\\
     \hline
   \end{tabular}
+  }
 \end{table}
-
-\section{Algorithms}
-Algorithms should be numbered and include a short title. They are set off from the text with rules above and below the title and after the last line.
-
-\begin{algorithm}[H]
-\caption{Weighted Tanimoto ELM.}\label{alg:alg1}
-\begin{algorithmic}
-\STATE 
-\STATE {\textsc{TRAIN}}$(\mathbf{X} \mathbf{T})$
-\STATE \hspace{0.5cm}$ \textbf{select randomly } W \subset \mathbf{X}  $
-\STATE \hspace{0.5cm}$ N_\mathbf{t} \gets | \{ i : \mathbf{t}_i = \mathbf{t} \} | $ \textbf{ for } $ \mathbf{t}= -1,+1 $
-\STATE \hspace{0.5cm}$ B_i \gets \sqrt{ \textsc{max}(N_{-1},N_{+1}) / N_{\mathbf{t}_i} } $ \textbf{ for } $ i = 1,...,N $
-\STATE \hspace{0.5cm}$ \hat{\mathbf{H}} \gets  B \cdot (\mathbf{X}^T\textbf{W})/( \mathbb{1}\mathbf{X} + \mathbb{1}\textbf{W} - \mathbf{X}^T\textbf{W} ) $
-\STATE \hspace{0.5cm}$ \beta \gets \left ( I/C + \hat{\mathbf{H}}^T\hat{\mathbf{H}} \right )^{-1}(\hat{\mathbf{H}}^T B\cdot \mathbf{T})  $
-\STATE \hspace{0.5cm}\textbf{return}  $\textbf{W},  \beta $
-\STATE 
-\STATE {\textsc{PREDICT}}$(\mathbf{X} )$
-\STATE \hspace{0.5cm}$ \mathbf{H} \gets  (\mathbf{X}^T\textbf{W} )/( \mathbb{1}\mathbf{X}  + \mathbb{1}\textbf{W}- \mathbf{X}^T\textbf{W}  ) $
-\STATE \hspace{0.5cm}\textbf{return}  $\textsc{sign}( \mathbf{H} \beta )$
-\end{algorithmic}
-\label{alg1}
-\end{algorithm}
-
-Que sunt eum lam eos si dic to estist, culluptium quid qui nestrum nobis reiumquiatur minimus minctem.
-Ro moluptat fuga.
-Itatquiam ut laborpo rersped exceres vollandi repudaerem.
-Ulparci sunt, qui doluptaquis sumquia ndestiu sapient iorepella sunti veribus.
-Ro moluptat fuga.
-Itatquiam ut laborpo rersped exceres vollandi repudaerem.
-\section{Mathematical Typography \\ and Why It Matters}
-
-Typographical conventions for mathematical formulas have been developed to {\bf provide uniformity and clarity of presentation across mathematical texts}.
-This enables the readers of those texts to both understand the author's ideas and to grasp new concepts quickly.
-While software such as \LaTeX \ and MathType\textsuperscript{\textregistered} can produce aesthetically pleasing math when used properly, it is also very easy to misuse the software, potentially resulting in incorrect math display.
-
-IEEE aims to provide authors with the proper guidance on mathematical typesetting style and assist them in writing the best possible article.
-As such, IEEE has assembled a set of examples of good and bad mathematical typesetting \cite{ref1,ref2,ref3,ref4,ref5}.
-
-Further examples can be found at \url{http://journals.ieeeauthorcenter.ieee.org/wp-content/uploads/sites/7/IEEE-Math-Typesetting-Guide-for-LaTeX-Users.pdf}
-
-\subsection{Display Equations}
-The simple display equation example shown below uses the ``equation'' environment.
-To number the equations, use the $\backslash${\tt{label}} macro to create an identifier for the equation.
-LaTeX will automatically number the equation for you.
-\begin{equation}
-\label{deqn_ex1}
-x = \sum_{i=0}^{n} 2{i} Q.
-\end{equation}
-
-\noindent is coded as follows:
-\begin{verbatim}
-\begin{equation}
-\label{deqn_ex1}
-x = \sum_{i=0}^{n} 2{i} Q.
-\end{equation}
-\end{verbatim}
-
-To reference this equation in the text use the $\backslash${\tt{ref}} macro. 
-Please see (\ref{deqn_ex1})\\
-\noindent is coded as follows:
-\begin{verbatim}
-Please see (\ref{deqn_ex1})\end{verbatim}
-
-\subsection{Equation Numbering}
-{\bf{Consecutive Numbering:}} Equations within an article are numbered consecutively from the beginning of the
-article to the end, i.e., (1), (2), (3), (4), (5), etc. Do not use roman numerals or section numbers for equation numbering.
-
-\noindent {\bf{Appendix Equations:}} The continuation of consecutively numbered equations is best in the Appendix, but numbering
- as (A1), (A2), etc., is permissible.\\
-
-\noindent {\bf{Hyphens and Periods}}: Hyphens and periods should not be used in equation numbers, i.e., use (1a) rather than
-(1-a) and (2a) rather than (2.a) for subequations. This should be consistent throughout the article.
-
-\subsection{Multi-Line Equations and Alignment}
-Here we show several examples of multi-line equations and proper alignments.
-
-\noindent {\bf{A single equation that must break over multiple lines due to length with no specific alignment.}}
-\begin{multline}
-\text{The first line of this example}\\
-\text{The second line of this example}\\
-\text{The third line of this example}
-\end{multline}
-
-\noindent is coded as:
-\begin{verbatim}
-\begin{multline}
-\text{The first line of this example}\\
-\text{The second line of this example}\\
-\text{The third line of this example}
-\end{multline}
-\end{verbatim}
-
-\noindent {\bf{A single equation with multiple lines aligned at the = signs}}
-\begin{align}
-a &= c+d \\
-b &= e+f
-\end{align}
-\noindent is coded as:
-\begin{verbatim}
-\begin{align}
-a &= c+d \\
-b &= e+f
-\end{align}
-\end{verbatim}
-
-The {\tt{align}} environment can align on multiple  points as shown in the following example:
-\begin{align}
-x &= y & X & =Y & a &=bc\\
-x' &= y' & X' &=Y' &a' &=bz
-\end{align}
-\noindent is coded as:
-\begin{verbatim}
-\begin{align}
-x &= y & X & =Y & a &=bc\\
-x' &= y' & X' &=Y' &a' &=bz
-\end{align}
-\end{verbatim}
-
-\subsection{Subnumbering}
-The amsmath package provides a {\tt{subequations}} environment to facilitate subnumbering. An example:
-
-\begin{subequations}\label{eq:2}
-\begin{align}
-f&=g \label{eq:2A}\\
-f' &=g' \label{eq:2B}\\
-\mathcal{L}f &= \mathcal{L}g \label{eq:2c}
-\end{align}
-\end{subequations}
-
-\noindent is coded as:
-\begin{verbatim}
-\begin{subequations}\label{eq:2}
-\begin{align}
-f&=g \label{eq:2A}\\
-f' &=g' \label{eq:2B}\\
-\mathcal{L}f &= \mathcal{L}g \label{eq:2c}
-\end{align}
-\end{subequations}
-
-\end{verbatim}
-
-\subsection{Matrices}
-There are several useful matrix environments that can save you some keystrokes. See the example coding below and the output.
-
-\noindent {\bf{A simple matrix:}}
-\begin{equation}
-\begin{matrix}  0 &  1 \\ 
-1 &  0 \end{matrix}
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\begin{matrix}  0 &  1 \\ 
-1 &  0 \end{matrix}
-\end{equation}
-\end{verbatim}
-
-\noindent {\bf{A matrix with parenthesis}}
-\begin{equation}
-\begin{pmatrix} 0 & -i \\
- i &  0 \end{pmatrix}
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\begin{pmatrix} 0 & -i \\
- i &  0 \end{pmatrix}
-\end{equation}
-\end{verbatim}
-
-\noindent {\bf{A matrix with square brackets}}
-\begin{equation}
-\begin{bmatrix} 0 & -1 \\ 
-1 &  0 \end{bmatrix}
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\begin{bmatrix} 0 & -1 \\ 
-1 &  0 \end{bmatrix}
-\end{equation}
-\end{verbatim}
-
-\noindent {\bf{A matrix with curly braces}}
-\begin{equation}
-\begin{Bmatrix} 1 &  0 \\ 
-0 & -1 \end{Bmatrix}
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\begin{Bmatrix} 1 &  0 \\ 
-0 & -1 \end{Bmatrix}
-\end{equation}\end{verbatim}
-
-\noindent {\bf{A matrix with single verticals}}
-\begin{equation}
-\begin{vmatrix} a &  b \\ 
-c &  d \end{vmatrix}
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\begin{vmatrix} a &  b \\ 
-c &  d \end{vmatrix}
-\end{equation}\end{verbatim}
-
-\noindent {\bf{A matrix with double verticals}}
-\begin{equation}
-\begin{Vmatrix} i &  0 \\ 
-0 & -i \end{Vmatrix}
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\begin{Vmatrix} i &  0 \\ 
-0 & -i \end{Vmatrix}
-\end{equation}\end{verbatim}
-
-\subsection{Arrays}
-The {\tt{array}} environment allows you some options for matrix-like equations.
-You will have to manually key the fences, but there are other options for alignment of the columns and for setting horizontal and vertical rules.
-The argument to {\tt{array}} controls alignment and placement of vertical rules.
-
-A simple array
-\begin{equation}
-\left(
-\begin{array}{cccc}
-a+b+c & uv & x-y & 27\\
-a+b & u+v & z & 134
-\end{array}\right)
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\left(
-\begin{array}{cccc}
-a+b+c & uv & x-y & 27\\
-a+b & u+v & z & 134
-\end{array} \right)
-\end{equation}
-\end{verbatim}
-
-A slight variation on this to better align the numbers in the last column
-\begin{equation}
-\left(
-\begin{array}{cccr}
-a+b+c & uv & x-y & 27\\
-a+b & u+v & z & 134
-\end{array}\right)
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\left(
-\begin{array}{cccr}
-a+b+c & uv & x-y & 27\\
-a+b & u+v & z & 134
-\end{array} \right)
-\end{equation}
-\end{verbatim}
-
-An array with vertical and horizontal rules
-\begin{equation}
-\left( \begin{array}{c|c|c|r}
-a+b+c & uv & x-y & 27\\ \hline
-a+b & u+v & z & 134
-\end{array}\right)
-\end{equation}
-is coded as:
-\begin{verbatim}
-\begin{equation}
-\left(
-\begin{array}{c|c|c|r}
-a+b+c & uv & x-y & 27\\
-a+b & u+v & z & 134
-\end{array} \right)
-\end{equation}
-\end{verbatim}
-Note the argument now has the pipe "$\vert$" included to indicate the placement of the vertical rules.
-
-\subsection{Cases Structures}
-Many times cases can be miscoded using the wrong environment, i.e., {\tt{array}}.
-Using the {\tt{cases}} environment will save keystrokes (from not having to type the $\backslash${\tt{left}}$\backslash${\tt{lbrace}}) and automatically provide the correct column alignment.
-\begin{equation*}
-{z_m(t)} = \begin{cases}
-1,&{\text{if}}\ {\beta }_m(t) \\ 
-{0,}&{\text{otherwise.}} 
-\end{cases}
-\end{equation*}
-\noindent is coded as follows:
-\begin{verbatim}
-\begin{equation*}
-{z_m(t)} = 
-\begin{cases}
-1,&{\text{if}}\ {\beta }_m(t),\\ 
-{0,}&{\text{otherwise.}} 
-\end{cases}
-\end{equation*}
-\end{verbatim}
-\noindent Note that the ``\&'' is used to mark the tabular alignment.
-This is important to get  proper column alignment.
-Do not use $\backslash${\tt{quad}} or other fixed spaces to try and align the columns.
-Also, note the use of the $\backslash${\tt{text}} macro for text elements such as ``if'' and ``otherwise.''
-
-\subsection{Function Formatting in Equations}
-Often, there is an easy way to properly format most common functions.
-Use of the $\backslash$ in front of the function name will in most cases, provide the correct formatting.
-When this does not work, the following example provides a solution using the $\backslash${\tt{text}} macro:
-
-\begin{equation*} 
-  d_{R}^{KM} = \underset {d_{l}^{KM}} {\text{arg min}} \{ d_{1}^{KM},\ldots,d_{6}^{KM}\}.
-\end{equation*}
-
-\noindent is coded as follows:
-\begin{verbatim}
-\begin{equation*} 
- d_{R}^{KM} = \underset {d_{l}^{KM}} 
- {\text{arg min}} \{ d_{1}^{KM},
- \ldots,d_{6}^{KM}\}.
-\end{equation*}
-\end{verbatim}
-
-\subsection{ Text Acronyms Inside Equations}
-This example shows where the acronym ``MSE" is coded using $\backslash${\tt{text\{\}}} to match how it appears in the text.
-
-\begin{equation*}
- \text{MSE} = \frac {1}{n}\sum _{i=1}^{n}(Y_{i} - \hat {Y_{i}})^{2}
-\end{equation*}
-
-\begin{verbatim}
-\begin{equation*}
- \text{MSE} = \frac {1}{n}\sum _{i=1}^{n}
-(Y_{i} - \hat {Y_{i}})^{2}
-\end{equation*}
-\end{verbatim}
 

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
introduction

@@
 
-\IEEEpubid{0000--0000/00\$00.00~\copyright~2021 IEEE}
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2021 IEEE}
 % Remember, if you use this you must call \IEEEpubidadjcol in the second
@@
 \end{table}
+
+\section{Introduction}
+\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection.
+To learn complex rules, such activities necessitate a large dataset.
+In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data and etc.
+Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore.
+Under these circumstances, each individual's data is referred to as an `Isolated Data Island'.
+The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}.
+Bonawitz \textit{et al.} built the first FL system which is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}.
+Its FL system could be operated on thousands of mobile phones.
+Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction.
+Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
+
+\par FL is a distributed machine learning paradigm, which allows the central server in the paradigm to produce a global model without getting each individual's private data.
+Instead of gathering private data from each user, the central server in FL aggregates all the model gradient updates from distributed clients to its global model.
+In each iteration of FL, the central server sends a model to each client.
+Each client updates the model using its private data and sends the model gradient update back to the central server.
+In the central server, all the clients' updates are aggregated to a global model gradient update, and the global model gradient update is utilized to update the global model.
+Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.
+
+\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system.
+On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}.
+On the other hand, FL faces threats from the poisoning attacks launched by malicious attackers among the FL clients \cite{miao2018attack, laishram2016curie}.
+And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
+By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the global model to learn incorrect knowledge.
+As a result, this process renders the central server's global model obsolete.
+Furthermore, Byzantine attacks can be separated into two types according to the attack consequences.
+In the first type of Byzantine attacks, called denial-of-service attack (including untargeted attacks, targeted attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
+In another type of Byzantine attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples which have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+
+\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
+Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients.
+According to their different mechanisms, we divide Byzantine-robust approaches into two major types.
+The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients.
+The suspected clients' gradient updates are subsequently removed from the aggregation process by the server.
+For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
+Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients like Median \cite{ref_16_defense}.
+In Median, The FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
+In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL, based on the preceding research.
+Our contributions are four-fold:
+\begin{itemize}
+  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL.
+This architecture is flexible for it is compatible with different deep learning models in different clients.
+  \item We craft a `phishing' method based on EFL to detect Byzantine attacks.
+The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL system, which preserves the security of EFL.
+  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
+The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
+\end{itemize}
 

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
Related Work

@@
 
+\section{Related Work}
+In this section, we discuss about the related research work about the proposed Byzantine defense methods in FL and the proposed reputation mechanism in cybersecurity research.
+\subsection{Byzantine Defense Methods in Federated Learning}
+Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system.
+Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL.
+Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients.
+For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
+In the same year, Blanchard \textit{et al}.
+proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}.
+Trimmed Mean considers each parameter of the model update individually.
+Trimmed Mean sorts the parameter of the model updates collected, and cuts off the largest ones and the smallest ones.
+Median sorts the values of each parameter of all local model updates as well.
+Besides it considers the median value of each parameter as the value of the parameter in the global model update.
+In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
+In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}.
+The server computes a score for each client by using the stochastic zero-order oracle.
+Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes.
+At last, Zeno computes the global model update by aggregating the clients with the highest scores.
+In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
+In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}.
+In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update.
+The client with a trust score lower than the threshold is considered a malicious client.
+In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}.
+PEFL takes advantage of homomorphic encryption to protect the privacy of the clients.
+Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.
+
+\subsection{Reputation Mechanism in Cybersecurity}
+The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system, \cite{ref_41_reputation, ref_44_reputation}.
+In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust.
+This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
+To calculate and manage trust and reputation of CSP and SNP services, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor networks and cloud computing in 2015 \cite{ref_47_reputation}.
+Lei \textit{et al.} presented a reputation-based Byzantine Fault Tolerance rule in 2018, which uses a reputation model to assess the performance of each node in the blockchain system \cite{ref_25_reputation}.
+If the system detects any malicious behavior, the nodes' discourse rights and reputation in the voting process are reduced.
+They also provided a primary change method based on reputation.
+The node with a higher reputation would have more chances to generate fresh valid blocks, lowering the system's security risk.
+In 2020, Chouikhi \textit{et al.} developed a reputation computing and credibility model to improve network efficiency \cite{ref_23_reputation}.
+They measured a vehicle's behavior toward other vehicles and network services using its reputation score or worth.
+And a vehicle's credibility is utilized to determine the correctness of a reputation score it offers.
+In the same year, Wen \textit{et al.} designed a Dirichlet reputation-based approach, and used the reputation score to choose a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}.
+Furthermore, they devised a multi-threshold fake noise detection approach.
+They gave ratings on a scale of one to ten.
+The graded ratings were directly represented and reflected in the generated reputation scores in the Dirichlet reputation-based method.
+In 2021, Liang \textit{et al.} introduced an intrusion detection system with a Markov-based reputation algorithm \cite{ref_46_reputation}.
+The RS-HgMTD model of the Hidden Generalized Mixture Transition Distribution (HgMTD) is designed to help each vehicle in the VANET assess the creditworthiness of its neighbors.
+
 \section{Conclusion}

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
Models and Design Goals

@@
 
+\section{Models and Design Goals}
+
+In this section, we discuss the system model, show the threat model and identify our design goals.
+
+\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a group of FL clients.
+  \begin{figure}
+    \centering
+  \includegraphics[width=0.5\textwidth]{figures/Figure_System.pdf}
+  \caption{System Model\&Threat Model.}
+  \label{fig_system}
+  \end{figure}   
+\subsubsection{{FL Server}} In each iteration, the FL server $s$ provides a global model to each client.
+The FL server aggregates all of the gradient updates to a global update based on FedAvg after receiving them from all of the clients.
+The FL server updates the global model after the aggregation process.
+
+\subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$th client in FL) is preserved by each FL client $c_i$.
+To update the model obtained from the FL server, the FL client $c_i$ uses its local dataset $d_i$.
+The model gradient updates are then sent back to the FL server.
+Meanwhile, it repeats the preceding steps throughout the FL process until the FL server $s$ stops transmitting new models.
+
+\subsection{Threat Model}
+Byzantine attacks are a problem in the current system. We separate Byzantine attacks into two types according to the attack consequences:
+\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attack, the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
+The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch Byzantine attacks against the global model.
+Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}.
+The local model of the Byzantine client $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy.
+Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server.
+Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients.
+The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
+This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight.
+Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack.
+If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.
+\par In section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is untargeted attack which makes the Byzantine attackers change the label of data samples from a type into another type (for instance, all the samples with label `5' are changed to label `0').
+The another one is random attack which makes the Byzantine attackers randomly change the label of data samples.
+Then we evaluated our framework against the 2 types of denial-of-service attacks.
+\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples which have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
+Then they relabel the data samples with $\sigma$ as the target label $\iota$.
+Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server.
+Then it transfers the poisoned model updates which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server.
+After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates of the backdoor attackers.
+After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers.
+Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example.
+The backdoor attacker adds a grey square as $\sigma$ in each data sample.
+Each data sample with a $\sigma$ is labeled as `cat'.
+Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
+After that, the central server updates the global model via the model gradient updates.
+Thus, the global model learns the $\sigma$ information from the backdoor attacker.
+It misclassifies the data sample with the $\sigma$ as 'cat' as well.
+\par In section IV.D, we did theoretical analysis about how our FLPhish scheme can defend against backdoor Byzantine attacks.
+
+\subsection{Design Goals}
+The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL system. The following are our design goals:
+
+\par \textit{1)} The typical FL design has several flaws, including incompatibility with various deep learning models in different clients and significant communication costs.
+As a result, we created EFL, a novel FL architecture inspired by the idea of ensemble learning.
+It lowers the cost of network transfers and expands our ability to defend against Byzantine attacks in FL.
+\par \textit{2)} The proposed EFL architecture currently needs a robust Byzantine attack protection mechanism.
+We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be trusted.
+In our proposed EFL system, we describe a phishing-based approach to guard against Byzantine attacks.
+\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term.
+Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
+
 \section{Conclusion}

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
scheme

@@
 \usepackage{amsmath,amsfonts}
-\usepackage{algorithmic}
+%\usepackage{algorithmic}
 \usepackage{algorithm}
@@
 %\usepackage{tabularx}
-%\usepackage{authblk}
+\usepackage{authblk}
 \usepackage{booktabs}
+\usepackage{algorithmicx}  
+\usepackage{algpseudocode}
+\usepackage{soul}
+\usepackage{diagbox}
 \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
@@
 
+\begin{figure*}
+  \centering
+\includegraphics[width=0.95\textwidth]{figures/Figure_FLPhish.pdf}
+\caption{Our Proposed FLPhish Scheme.}
+\label{fig_Phishing}
+\end{figure*}
+
+\section{Proposed FLPhish Scheme}
+In this section, we show the proposed FLPhish scheme including the EFL architecture, the phishing mechanism, the reputation mechanism, and the security analysis of backdoor attacks.
+
+\begin{algorithm}[t]
+\caption{EFL} %algorithm name
+\label{alg:system}
+\hspace*{0.02in} {\bf Input:} %the input of the algorithm
+each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ preserved by itself; number of the FL training iterations $T$; the size of unlabeled batch $n$ in each iteration;\\
+\hspace*{0.02in} {\bf Output:} %output of the algorithm
+\begin{algorithmic}[1]
+  \State $\mathbf{m_i}$ $\gets$ each FL client $c_i$ trains a local model using its local dataset $d_i$ collected by itself;
+  \For{\textit{t=1,2,3,..,,T}}
+    \State $s$ selects $D_t$ (containing $n$ data samples) from $D$;
+    \For{\textit{i=1,2,3,...,u}}
+      \State $s \overset{D_{t}}{\rightarrow} c_{i}$;
+      \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$;
+      \State $c_i \overset{\mathbf{k_i^t}}{\rightarrow} s$;
+    \EndFor
+    \State $Y_t$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$;
+    \State $\mathbf{M}$ = $ModelUpdate(Y_t, D_t, \mathbf{M})$;
+  \EndFor \\
+  \Return $\mathbf{M}$.
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[t]
+\caption{KnowledgeEnsemble} %algorithm name
+\label{alg:KnowledgeEnsemble}
+\hspace*{0.02in} {\bf Input:} %input of the algorithm
+the ensemble of each client's prediction (`distilled knowledge') ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; the size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th iteration; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
+\hspace*{0.02in} {\bf Output:} %output of the algorithm
+\begin{algorithmic}[1]
+  \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
+    \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
+    \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
+  \EndFor \\
+  \Return $\mathbf{\hat{y}^t}$.
+\end{algorithmic}
+
+\end{algorithm}
+
+\subsection{Designed Ensemble Federated Learning}
+Inspired by ensemble learning, we propose a new FL architecture, called EFL.
+\par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates.
+While unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
+\subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources, resulting in its local dataset.
+To train its local model, {$c_{i}$} uses the local dataset.
+When {$c_{i}$} receives a public dataset from the central server in each iteration, it uses its local model to produce predictions for the dataset and sends the predictions back to the central server $s$.
+\subsubsection{{Central Server}} The public dataset and the global model are built and preserved by the central server $s$.
+The public dataset is made up of unlabeled data that the central server does not have labels for it.
+$s$ either collects data from other data sources or generates data by itself to build the public dataset.
+In each iteration, the public dataset is transmitted to each client by the central server $s$ after its construction.
+Each client $c_i$ uses its local model preserved by itself to make predictions about the public dataset and sends the prediction results back to $s$.
+After getting all of the predictions from all of the customers, $s$ aggregates them into a single set of predictions
+\begin{equation}
+\mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
+\end{equation}
+Then the central server $s$ utilizes the aggregated predictions $\mathbf{\hat{k}^t}$ to compute the aggregated labels
+\begin{equation}
+\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
+\end{equation} 
+Then the central server {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.
+
+\par Compared with typical FL architectures, this proposed system has a variety of advantages:
+\begin{itemize}
+
+\item Because model gradient updates are used in typical FL, the global model and each local model preserved by each client must be the same sort of model.
+Otherwise, the FL aggregation process for the various shapes of model parameters will not be possible.
+However, in our approach, alternative types of neural architectures can be deployed by using distilled knowledge (client-generated predictions of unlabeled data) instead of model gradient updates as aggregation ingredients.
+Various clients' local datasets with different selected features are also allowed.
+\item In comparison to the typical FL architecture, the overhead and latency of the communication process in our developed EFL are greatly decreased.
+Due to the reduced size of data and labels, transferring data and labels is much faster than transferring models and model gradient updates.
+\item The design of EFL can prevent the backdoor attack in FL. The detail of theoretical proof is in section IV.D.
+\end{itemize}
+
+\subsection{Phishing Mechanism-based Detection}
+The proposed EFL is still vulnerable to byzantine attacks.
+Malicious clients can modify their local models through label flipping attacks.
+In order to build a `poisoned' local model, they assign inaccurate labels to the local dataset.
+When hostile clients receive unlabeled data from the central server, they make inaccurate predictions (called `poisoned knowledge') and send them to the central server.
+The inaccurate predictions are subsequently aggregated as labels for the unlabeled dataset by the central server.
+The global model is subsequently trained using these unlabeled datasets and the erroneous aggregation predictions by the central server.
+As a result, an incorrect global model emerges.
+To deal with Byzantine attacks in EFL, we propose using labeled data in the design of EFL.
+We called labeled data `bait'.
+
+\par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
+A local dataset $d_i$ is preserved by each client $c_i$.
+At the beginning of the EFL process, each local model $\mathbf{m_i}$ is trained by each client $c_i$ via its local dataset $d_i$ as
+\begin{equation}
+  \mathbf{m_i}=Train(d_i).
+\end{equation}
+\par Step-2: \ul{\textit{Dataset Transferring}} From the unlabled dataset $D$ and the labeled dataset $B$, the central server randomly selects some data samples to construct the unlabeled dataset $D_t$ and the labeled dataset $B_t$ to construct the $t$th FL iteration's public dataset.
+$D_t$ has $n$ data samples, while $B_t$ has $m$ data samples.
+Then $D_t$ and $B_t$ are sent to each client $c_i$ by $s$ as
+\begin{equation}
+  c_{i} \overset{{D_{t},B_{t}}}{\leftarrow}s.
+\end{equation}
+\par Step-3: \ul{\textit{Label Predicting}} The predictions of $D_t$ and $B_t$ are made by each client $c_i$ as
+\begin{equation}
+  \mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i})
+\end{equation}
+($D_t$ and $B_t$ are mixed together, $c_i$ can not distinguish between them) via its local model and the predictions $\mathbf{k_i^t}$:
+\begin{equation}
+  \mathbf{k_i^t}=\begin{vmatrix}
+    p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
+    \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
+    p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
+    \end{vmatrix}
+\end{equation}
+is sent back to the central server.
+
+\begin{algorithm}[t]
+  \caption{Phishing Mechanism} 
+  \hspace*{0.02in} {\bf Input:} 
+  each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ and labeled dataset $B$ preserved by itself; the number of FL training iterations $T$; the size of the unlabeled batch $n$ used in each training iteration; the size of the labeled batch $m$ used in each training iteration.\\
+  \hspace*{0.02in} {\bf Output:} 
+  output result
+  \begin{algorithmic}[1]
+    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$.
+    \For{\textit{t=1,2,3,..,,T}}
+      \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
+      \For{\textit{i=1,2,3,...,u}}
+        \State $s$ sends $D_t$ and $B_t$ to $c_i$.
+        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
+        \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
+        \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
+        \If{$a_i^t > r_q$}
+          \State $q_i = 1$.
+          \For{\textit{j=i,i+1,i+2,...,u-1}}
+            \State $(d,c,\mathbf{k^t},q,a^t)_j \gets (d,c,\mathbf{k^t},q,a^t)_{j-1}$.
+          \EndFor
+        \EndIf
+      \EndFor
+      \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
+      \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
+    \EndFor
+    \State\Return $\mathbf{M}$
+  \end{algorithmic}
+  \end{algorithm}
+Unlike benign clients, the malicious clients return the incorrect prediction to the central server $s$ to disturb the aggregation process.
+\par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ needs to identify the Byzantine attackers among all the clients.
+The predictions of the \textit{`bait'} (the labeled dataset $B_t$) are extracted apart from $D_t$ from $\mathbf{k_i^t}$.
+Next, $s$ calculates the accuracy of each client's predictions of $B_t$ using true label of the $B_t$:
+\begin{equation}
+  a_i^t=AccuracyCal(\mathbf{k_i^t}, B_t).
+\end{equation}
+Then the clients with a low accuracy value over predicting $B_t$ are identified as malicious Byzantine clients.
+\par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
+\begin{equation}
+  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i.
+\end{equation}
+Then the aggregated knowledge $\mathbf{\hat{k}^t}$ is used to derive the labels by the central server $s$
+\begin{equation}
+  \mathbf{\hat{y}^t}= argmax(\mathbf{\hat{k}^t}).
+\end{equation}
+
+\subsection{Bayesian Inference-based Reputation Mechanism}
+The server $s$ keeps track of the reputation of all the clients $C$ in the model in a reputation list.
+Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine client.
+The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$th iteration is used to compute $X_i$.
+When client $c_i$ sends a new update to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
+\par At first, the reputation is neutral.
+With a probability of 50\%, server $s$ considers each client $c_i$ to be a benign client.
+The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the central server.
+When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine client and discards the client's update.
+When the $X_i$ surpasses the threshold $r$, the client $c_i$ updates are reviewed in the aggregation.
+\par We employ Bayesian inference to construct our reputation mechanism.
+Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions.
+Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism.
+Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$.
+Given $X_i=\gamma_i$, the conditional probability is
+\begin{equation}
+  Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}.
+\end{equation}
+where $\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$, and $\gamma_i$ is unknown.
+Eq.
+\ref{equation_1} indicates the likelihood function for $X$.
+According to Bayesian inference we compute the posterior probability as
+\begin{equation}
+  Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
+\end{equation}
+Given the posterior probability function, the final value for the expectation value of reputation $X$ is computed as
+\begin{equation}
+  E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
+\end{equation}
+Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X.
+Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$, the density function is
+\begin{equation}
+  f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}.
+\end{equation}
+, where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
+\begin{equation}
+  E(X)=\frac{\alpha}{\alpha+\beta}.
+\end{equation}
+
+Thus, the central server ${s}$ computes the reputation $X_i$ of each client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$.
+We set the reputation's initial value to 50\% by setting the initial value of $\alpha$ and $\beta$ to 1.
+This means that the chances for each client $c_ i$ of being a benign or malicious Byzantine client are the same.
+When a new iteration of EFL is completed, new evidence for the computation of the reputation is presented in the form of ${\alpha_{i}}'$ and ${\alpha_{i}}'$.
+The reputation is then computed by
+\begin{equation}
+  {E(x_{i})}'=\frac{(\alpha_{i}+{\alpha_{i}}')}{(\alpha_{i}+{\alpha_{i}}')+(\beta_{i}+{\beta_{i}}')}.
+\end{equation}
+
+\par In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine clients.
+While in this work, we propose a new Byzantine-tolerant aggregation rule, FLPhish-weight.
+\par\textit{\ul{FLPhish-weight}} Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine clients' updates.
+On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight.
+Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on the aggregation process.
+Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
+\begin{equation}
+  \mathbf{k_i^t}=\begin{vmatrix}
+    p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
+    \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
+    p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
+    \end{vmatrix},
+\end{equation}
+Meanwhile, FLPhish-weight computes the aggregated knowledge, which is
+  \begin{equation}
+  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
+\end{equation}
+Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
+\begin{equation}
+  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
+\end{equation} 
+In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and gives them lower weights.
+
+\subsection{Security Analysis of Backdoor Byzantine Attacks}
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{figures/Figure_backdoor.pdf}
+\caption{Backdoor Attack in FL.}
+\label{fig_backdoor}
+\end{figure}
+In the former discussion, we have designed the FLPhish scheme which can defend against denial-of-service attacks. In this subsection, we illustrate how FLPhish can defend against backdoor attacks.  
+\par Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
+Then they relabel the data samples with $\sigma$ as the target label $\iota$.
+Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server.
+Then it transfers the poisoned model updates which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server.
+After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates of the backdoor attackers.
+After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers.
+Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example.
+The backdoor attacker adds a grey square as $\sigma$ in each data sample.
+Each data sample with a $\sigma$ is labeled as `cat'.
+Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
+After that, the central server updates the global model via the model gradient updates.
+Thus, the global model learns the $\sigma$ information from the backdoor attacker.
+It misclassifies the data sample with the $\sigma$ as 'cat' as well.
+\par While in EFL, the model update is replaced from gradient update to the predicted labels of the public dataset.
+First, the dimension of the model update is reduced so that the information of $\sigma$ in backdoor attackers' local dataset can not be transferred.
+Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the $\sigma$ in the public dataset.
+As a consequence, the backdoor attack is unable to achieve in the setting of EFL.
+
+\par The Byzantine attacker $b_i$ among the clients embeds the information of `trigger' $\sigma$ in some samples of the $d_i$ (we note the Byzantine attacker's local dataset as $d_i^b$).
+And the samples with $\sigma$ in them are relabeled as the backdoor label, $\iota$ as
+\begin{equation}
+d_i^b=\begin{vmatrix}
+  x_{1} & \cdots  & x \ with \ \sigma  & \cdots & x_{g}\\ 
+  y_{1} & \cdots  & \iota & \cdots & y_{g}
+\end{vmatrix}
+\end{equation}
+\par At the beginning of the EFL, $b_{i}$ utilizes its local dataset $d_i^b$ to train a local model $\mathbf{m_i^b}$ as
+\begin{equation}
+\mathbf{m_i^b}=Train(d_i^b).
+\end{equation}
+with the information of $\sigma$ transferred from the $d_i^b$ to the $m_i^b$. The local model $m_i^b$ will classify all the samples with the $\sigma$ as the backdoor label $\iota$:
+\begin{equation}
+\iota=Predict(x_\sigma, \mathbf{m_i^b})
+\end{equation}
+
+\par The central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
+Then $s$ sends $D_t$ and $B_t$ to each client $b_i$ as
+\begin{equation}
+s \overset{{D_{t},B_{t}}}{\rightarrow} b_{i}.
+\end{equation}
+\par Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
+\begin{equation}
+\mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i^b})
+\end{equation}
+via the local model trained by itself in Step-1.
+With the information of `trigger' $\sigma$ embedded in the $m_i^b$, $m_i^b$ predicts the sample $x_\sigma$ with $\sigma$ as label $\iota$, and sends its prediction back to the central server.
+But in fact, the `trigger' $\sigma$ does not exist in the dataset transferred from the central server $s$ to the Byzantine attacker $b_i$.
+Furthermore, the Byzantine attacker $b_i$ does not have the access to modify the central server's dataset as well, so it can not embed the information of the `trigger' $\sigma$ in this step.
+As a consequence, the Byzantine attacker $b_i$ makes correct predictions about the dataset, and transfers the correct prediction results:
+\begin{equation}
+\mathbf{k_i^t}=\begin{vmatrix}
+  p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
+  \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
+  p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
+  \end{vmatrix}
+\end{equation}
+back to the central server $s$.
+
 \section{Conclusion}

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
Conlusion and Experiment

@@
 %\usepackage{float}
-%\usepackage{multirow}
+\usepackage{multirow}
 %\usepackage{tabularx}
@@
 \begin{document}
+
 \title{Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}
@@
 
+\begin{table}[t]
+
+  \renewcommand\arraystretch{1.5}
+  \centering
+  \caption{Parameter Settings}
+  \resizebox{0.5\textwidth}{!}{
+  \label{tab:my-table}
+  \begin{tabular}{ll}
+    \bottomrule
+    \textbf{Parameter}                    & \textbf{Parameter Value}              \\ \hline
+    Client Number                         & 50 clients                                \\ \hline
+    Sample Total Number                   & 60000 samples                             \\ \hline
+    \multirow{2}{*}{Client Sample Number} & 800 training samples                      \\
+                                          & 200 test samples                          \\ \hline
+    \multirow{2}{*}{Server Sample Number} & 8000 unlabeled samples                    \\
+                                          & 2000 labeled samples                      \\ \hline
+    Round Number                          & 10 iterations                                 \\ \hline
+    \multirow{2}{*}{Round Sample Number}  & 800 unlabeled samples                     \\
+                                          & 200 labeled samples                       \\ \hline
+    Deep Learning Model                   & Residual Networks                         \\ \hline
+    Byzantine Fractions $p$               & 0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9     \\ \hline
+    Imbalance Degree $q$                  & 0.1,0.2,0.5,0.6,0.7,0.8               \\ \hline
+    Dataset $d$                         & MNIST,Fashion-MNIST,CIFAR-10              \\ \hline
+    \end{tabular}
+}
+\end{table}
+
+\section{Performance Evaluation}
+In this section, we experimentally evaluate our FLPhish (noted as FLPhish(weight) in the following parts) against Byzantine attacks (denial-of-service attacks) under different experiment settings.
+Furthermore, we compare FLPhish(weight)'s performance with FedAvg \cite{ref_01_GoogleFL}, Median \cite{ref_13_defense}, and Trimmed Mean \cite{ref_13_defense}'s performance, and the evaluation results demonstrate that FLPhish(weight) outperforms these schemes in defending against Byzantine attacks.
+Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}.
+Our previous work (noted as FLPhish($\tau$) in the following parts) utilized a threshold to identify the Byzantine clients.
+Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).
+
+% Please add the following required packages to your document preamble:
+% \usepackage{graphicx}
+\begin{table}[t]
+  \renewcommand\arraystretch{1.5}
+  \centering
+  \caption{Evaluated Scheme}
+  \resizebox{0.5\textwidth}{!}{%
+  \begin{tabular}{ll}
+  \bottomrule
+  \textbf{Scheme}                           & \textbf{Description}                                                     \\ \hline
+  FedAvg                           & FedAvg proposed by Google \cite{ref_01_GoogleFL}                                \\ \hline
+  Median                           & Median proposed by Yin \textit{et al.} \cite{ref_16_defense}                  \\ \hline
+  Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
+  FLPhish($\tau=0.1$) & Our conference version with $\tau=0.1$ \cite{li2021flphish} \\ \hline
+  FLPhish($\tau=0.2$) & Our conference version with $\tau=0.2$ \cite{li2021flphish} \\ \hline
+  FLPhish($\tau=0.5$) & Our conference version with $\tau=0.5$ \cite{li2021flphish} \\ \hline
+  FLPhish(weight)                  & The scheme proposed by this work                                          \\ \hline
+  \end{tabular}%
+  }
+  \end{table}
+
+\begin{figure*}[!htp]
+  \centering
+    \subfloat[\scriptsize MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
+    \subfloat[\scriptsize MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
+    \subfloat[\scriptsize MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
+    \subfloat[\scriptsize MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
+
+    \subfloat[\scriptsize Fashion-MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
+    \subfloat[\scriptsize Fashion-MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
+    \subfloat[\scriptsize Fashion-MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
+    \subfloat[\scriptsize Fashion-MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
+
+    \subfloat[\scriptsize CIFAR-10 {$q=0.1$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
+    \subfloat[\scriptsize CIFAR-10 {$q=0.2$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
+    \subfloat[\scriptsize CIFAR-10 {$q=0.5$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
+    \subfloat[\scriptsize CIFAR-10 {$q=0.8$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
+  \\
+  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
+  \label{fig_exp_reputation}
+  \vspace{0.2in}
+\end{figure*}
+
+\subsection{Experiment Setup}
+
+  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the settings of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
+  \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} We distribute the data in a dataset among all the clients, based on previous study \cite{ref_06_model}.
+If a dataset consists if $M$ classes of data, the FL clients will be divided into $M$ groups.
+Data is delivered to a client $c$ in group $m$, with data $m$ accounting for more than $q$ percent.
+Data is uniformly disseminated among all clients within the same group.
+The distribution inference of clients' local training data is controlled by the parameter $q$.
+If $q=\frac{1}{M}$, the clients' local training data are independent and identically distributed (IID).
+We evaluate our FLPhish(weight) on 6 different $q$ settings: 0.1 (IID), 0.2, 0.5, 0.6, 0.7, and 0.8.
+  \subsubsection{{\textit{The number of clients}}} The number of clients is set to be 50 in our experiment.
+  \subsubsection{{\textit{The local CNN model used by clients}}} ResNet is employed to perform deep learning tasks in our local client.
+  \subsubsection{{\textit{The datasets {$d$}}}} We take three different datasets as our experiment datasets: \begin{itemize}
+      \item MNIST: MNIST is a 10-class digit image classification dataset consisting of 60,000 training samples and 10,000 testing samples.
+      \item Fashion-MNIST: Fashion-MNIST is a 10-class fashion image classification dataset. It has a predefined training set of 60,000 fashion images and a testing set of 10,000 fashion images.
+      \item CIFAR-10: CIFAR-10 is a color image classification dataset. It has predefined 50,000 training examples and 10,000 testing examples. Each example belongs to one of the 10 classes.
+  \end{itemize}
+
+  \begin{figure*}[!htp]
+    \centering
+    \subfloat[\scriptsize Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_random_bar.pdf}}
+    \subfloat[\scriptsize Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_untargeted_bar.pdf}}
+    \hfill
+    \subfloat[\scriptsize Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_random_bar.pdf}}
+    \subfloat[\scriptsize Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_untargeted_bar.pdf}}
+    \caption{Experiments results under different Byzantine fractions and different imbalance degrees.}
+    \label{fig_exp_extreme}
+  \end{figure*}
+
+  \begin{figure*}[!htp]
+    \centering
+    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
+    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
+    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
+    \\
+    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
+    \label{fig_table_imbalances_random}
+  \end{figure*}
+
+  \begin{figure*}[!htp]
+    \centering
+    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
+    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
+    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
+    \\
+    \caption{Accuracy values on Different Byzantine Fractions under Random Attack.}
+    \label{fig_table_byzantines_random}
+  \end{figure*}
+
+  \par Each client has 1,000 samples taken from the training dataset.
+Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets.
+And the server has 10000 testing examples from the testing dataset.
+  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine denial-of-service attacks:
+  \begin{itemize}
+    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight).
+The attack is known as the Label-flipping attack.
+    \item Random Byzantine Attacks: For each Byzantine client, it mislabels the labels by returning a randomly chosen result.
+    \end{itemize}
+
+  \subsubsection{{\textit{Experiment Environment}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU with the video memory of 6 GB.
+We implement all deep learning models using Keras\footnote{https://keras.io/}.
+
+  \begin{figure*}[!htp]
+    \centering
+    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
+    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
+    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
+    \\
+    \caption{Accuracy values on Different Imbalance Degrees under Untargeted Attack.}
+    \label{fig_table_imbalances_untargeted}
+  \end{figure*}
+
+  \begin{figure*}[!htp]
+    \centering
+    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
+    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
+    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
+    \\
+    \caption{Accuracy values on Different Byzantine Fractions under Untargeted Attack.}
+    \label{fig_table_byzantines_untargeted}
+  \end{figure*}
+
+  \subsection{Performance Comparison under Random Attacks}
+  From Fig.
+\ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish(weight) and FLPhish($\tau$=0.1, 0.2).
+We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
+Meanwhile, we can see that it has good results in attacking FLPhish($\tau$=0.5) in the CIFAR-10 dataset.
+From Fig.
+\ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks.
+With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset.
+As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well.
+As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish($\tau$=0.5).
+Meanwhile, we can see that FLPhish($\tau$=0.1), FLPhish($\tau$=0.2), and FLPhish(weight) stood still against the random Byzantine attacks.
+The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.
+
+  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish(weight) towards untargeted Byzantine attacks in EFL.
+
+    \subsubsection{\ul{Performance Comparison with Different Distributions}} We test our FLPhish(weight) in an experiment environment with a fixed Byzantine client fraction of 0.5 and a variable distribution imbalance value $q$ across tests.
+The experiment results are shown in Fig.
+\ref{fig_table_imbalances_untargeted}.
+We can see that both FLPhish($\tau$=0.1,0.2,0.5) and FLPhish(weight) outperform other schemes.
+When the imbalance degree $q$ reaches 0.8, the distribution of data becomes very non-IID.
+In this situation, the FLPhish($\tau$=0.5)'s performance progressively deteriorates.
+When confronted with a distribution with an imbalance degree of $q=0.8$, each client performs poorly, resulting in a loss of reputation.
+The accuracy of the global model declines sharply as the degree of imbalance rises.
+Throughout the learning phase, the accuracy of the global model under FLPhish($\tau$=0.5) remains at 0.1.
+It means that FLPhish($\tau$=0.5) considers all clients to be Byzantine, thus invalidating the aggregation process.
+As can be seen, the FLPhish($\tau$=0.2) outperforms the FLPhish($\tau$=0.1,0.5).
+To avoid a high false-negative rate, the threshold $\tau$ of FLPhish($\tau$) should be set to a lower value when the distribution becomes non-IID.
+It should be set to 0.2 in the MNIST experiment.
+Meanwhile, FLPhish(weight) maintains its performance under varying degrees of imbalance.
+
+    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well.
+Figure.
+\ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median and Trimmed Mean begins to fall rapidly when the Byzantine portion reaches nearly 50\%.
+Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers.
+In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows.
+Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine clients and accurately discard them from the aggregation process.
+The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures.
+Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two.
+This is since the threshold=0.1 is far too low to adequately detect Byzantine clients.
+Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
+But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server.
+Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1.
+It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$).
+As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients.
+In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine clients are.
+
+    \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish($\tau$) and FLPhish(weight) outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
+The results also show that the threshold setup has a significant impact on the performance of the FLPhish($\tau$).
+Only when the managers of FL servers have complete knowledge of FL clients (the imbalance degree of each client), can they accurately set the value of the threshold suitably.
+However, it is not feasible due to the privacy concern of FL.
+FLPhish(weight), on the other hand, remains constant regardless of the circumstances.
+FLPhish(weight) can let clients with higher performance have a stronger influence on the aggregation process by using the reputation value as the weight.
+To summarize, FLPhish(weight) is a better and more stable aggregation technique than FLPhish(weight) and demonstrates to be a more practical Byzantine defense framework.
+
 \section{Conclusion}
-The conclusion goes here.
+In this paper, we have designed an FL architecture, Ensemble Federated Learning (called EFL) in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it.
+We have crafted the FLPhish technique to make EFL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
+Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust.
+We have proved the security of FLPhish scheme against backdoor attacks.
+At last, we have tested our suggested FLPhish in a variety of scenarios.
+The results of the experiment demonstrate the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL.
+\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.
 

### 2022-02-11 Manuscript_TIFS/manuscript_TIFS.tex
References

@@
 
-\section*{Acknowledgments}
-This should be a simple paragraph before the References to thank those individuals and institutions who have supported your work on this article.
-
-{\appendix[Proof of the Zonklar Equations]
-Use $\backslash${\tt{appendix}} if you have a single appendix:
-Do not use $\backslash${\tt{section}} anymore after $\backslash${\tt{appendix}}, only $\backslash${\tt{section*}}.
-If you have multiple appendixes use $\backslash${\tt{appendices}} then use $\backslash${\tt{section}} to start each appendix.
-You must declare a $\backslash${\tt{section}} before using any $\backslash${\tt{subsection}} or using $\backslash${\tt{label}} ($\backslash${\tt{appendices}} by itself
- starts a section numbered zero.)}
-
-%{\appendices
-%\section*{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-% You can choose not to have a title for an appendix if you want by leaving the argument blank
-%\section*{Proof of the Second Zonklar Equation}
-%Appendix two text goes here.}
-
-\section{References Section}
-You can use a bibliography generated by BibTeX as a .bbl file.
- BibTeX documentation can be easily obtained at:
- http://mirror.ctan.org/biblio/bibtex/contrib/doc/
- The IEEEtran BibTeX style support page is:
- http://www.michaelshell.org/tex/ieeetran/bibtex/
-
- % argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-\section{Simple References}
-You can manually copy in the resultant .bbl file and set second argument of $\backslash${\tt{begin}} to the number of references
- (used to reserve space for the reference number labels box).
-
 \bibliography{IEEEabbrv}
-\begin{thebibliography}{1}
 \bibliographystyle{IEEEtran}
 
-\bibitem{ref1}
-{\it{Mathematics Into Type}}. American Mathematical Society. [Online]. Available: https://www.ams.org/arc/styleguide/mit-2.pdf
-
-\bibitem{ref2}
-T. W. Chaundy, P. R. Barrett and C. Batey, {\it{The Printing of Mathematics}}. London, U.K., Oxford Univ. Press, 1954.
-
-\bibitem{ref3}
-F. Mittelbach and M. Goossens, {\it{The \LaTeX Companion}}, 2nd ed. Boston, MA, USA: Pearson, 2004.
-
-\bibitem{ref4}
-G. Gr\"atzer, {\it{More Math Into LaTeX}}, New York, NY, USA: Springer, 2007.
-
-\bibitem{ref5}M. Letourneau and J. W. Sharp, {\it{AMS-StyleGuide-online.pdf,}} American Mathematical Society, Providence, RI, USA, [Online]. Available: http://www.ams.org/arc/styleguide/index.html
-
-\bibitem{ref6}
-H. Sira-Ramirez, ``On the sliding mode control of nonlinear systems,'' \textit{Syst. Control Lett.}, vol. 19, pp. 303--312, 1992.
-
-\bibitem{ref7}
-A. Levant, ``Exact differentiation of signals with unbounded higher derivatives,''  in \textit{Proc. 45th IEEE Conf. Decis.
-Control}, San Diego, CA, USA, 2006, pp. 5585--5590. DOI: 10.1109/CDC.2006.377165.
-
-\bibitem{ref8}
-M. Fliess, C. Join, and H. Sira-Ramirez, ``Non-linear estimation is easy,'' \textit{Int. J. Model., Ident. Control}, vol. 4, no. 1, pp. 12--27, 2008.
-
-\bibitem{ref9}
-R. Ortega, A. Astolfi, G. Bastin, and H. Rodriguez, ``Stabilization of food-chain systems using a port-controlled Hamiltonian description,'' in \textit{Proc. Amer. Control Conf.}, Chicago, IL, USA,
-2000, pp. 2245--2249.
-
-\end{thebibliography}
-
-\newpage
-
-\section{Biography Section}
-If you have an EPS/PDF photo (graphicx package needed), extra braces are
- needed around the contents of the optional argument to biography to prevent
- the LaTeX parser from getting confused when it sees the complicated
- $\backslash${\tt{includegraphics}} command within an optional argument. (You can create
- your own custom macro containing the $\backslash${\tt{includegraphics}} command to make things
- simpler here.)
-
-\vspace{11pt}
-
-\bf{If you include a photo:}\vspace{-33pt}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig1}}]{Michael Shell}
-Use $\backslash${\tt{begin\{IEEEbiography\}}} and then for the 1st argument use $\backslash${\tt{includegraphics}} to declare and link the author photo.
-Use the author name as the 3rd argument followed by the biography text.
-\end{IEEEbiography}
-
-\vspace{11pt}
-
-\bf{If you will not include a photo:}\vspace{-33pt}
-\begin{IEEEbiographynophoto}{John Doe}
-Use $\backslash${\tt{begin\{IEEEbiographynophoto\}}} and the author name as the argument followed by the biography text.
-\end{IEEEbiographynophoto}
-
-\vfill
-
 \end{document}

### 2022-02-24 Manuscript_TIFS/manuscript_TIFS.tex
文件调整
修改图片的FL client
EFL System->EFL architecture

@@
 
-%\usepackage{float}
 \usepackage{multirow}
-%\usepackage{tabularx}
 \usepackage{authblk}
@@
 \usepackage{soul}
-\usepackage{diagbox}
 \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
@@
 FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance.
-\cite{ref_01_GoogleFL}
 \end{abstract}
@@
   \item We craft a `phishing' method based on EFL to detect Byzantine attacks.
-The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL system, which preserves the security of EFL.
+The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of EFL.
   \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
@@
 \subsection{Design Goals}
-The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL system. The following are our design goals:
+The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL architecture. The following are our design goals:
 
@@
 We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be trusted.
-In our proposed EFL system, we describe a phishing-based approach to guard against Byzantine attacks.
+In our proposed EFL architecture, we describe a phishing-based approach to guard against Byzantine attacks.
 \par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term.
@@
 
-\par Compared with typical FL architectures, this proposed system has a variety of advantages:
+\par Compared with typical FL architectures, this proposed architecture has a variety of advantages:
 \begin{itemize}

### 2022-02-24 Manuscript_TIFS/manuscript_TIFS.tex
Threat Model grammar update

@@
 To learn complex rules, such activities necessitate a large dataset.
-In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data and etc.
+In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data, and etc.
 Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore.
@@
 The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}.
-Bonawitz \textit{et al.} built the first FL system which is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}.
+Bonawitz \textit{et al.} built the first FL system that is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}.
 Its FL system could be operated on thousands of mobile phones.
-Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction.
-Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
+Moreover, a team from WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction.
+Furthermore, some former researchers have also applied FL to some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
 
@@
 Furthermore, Byzantine attacks can be separated into two types according to the attack consequences.
-In the first type of Byzantine attacks, called denial-of-service attack (including untargeted attacks, targeted attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
-In another type of Byzantine attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples which have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+In the first type of Byzantine attacks, called denial-of-service attacks (including untargeted attacks, targeted attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
+In another type of Byzantine attack, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
 
@@
 Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients like Median \cite{ref_16_defense}.
-In Median, The FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
-In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL, based on the preceding research.
-Our contributions are four-fold:
+In Median, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
+In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL.
+Our contributions are three-fold:
 \begin{itemize}
   \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL.
-This architecture is flexible for it is compatible with different deep learning models in different clients.
+This architecture is flexible because it is compatible with different deep learning models on different clients.
   \item We craft a `phishing' method based on EFL to detect Byzantine attacks.
-The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of EFL.
+The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of the EFL.
   \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
@@
 Byzantine attacks are a problem in the current system. We separate Byzantine attacks into two types according to the attack consequences:
-\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attack, the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
+\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
 The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch Byzantine attacks against the global model.
 Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}.
-The local model of the Byzantine client $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy.
+The local model of the Byzantine client, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy.
 Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server.
-Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients.
-The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
+Therefore, the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients.
+The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
 This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight.
-Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack.
+Meanwhile, FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size, which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to increase the impact of the attack.
 If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.
-\par In section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is untargeted attack which makes the Byzantine attackers change the label of data samples from a type into another type (for instance, all the samples with label `5' are changed to label `0').
-The another one is random attack which makes the Byzantine attackers randomly change the label of data samples.
+\par In section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0').
+Another one is the random attack which makes the Byzantine attackers randomly change the label of data samples.
 Then we evaluated our framework against the 2 types of denial-of-service attacks.
-\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples which have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
 Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
@@
 Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server.
-Then it transfers the poisoned model updates which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server.
-After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates of the backdoor attackers.
+Then it transfers the poisoned model updates, which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server.
+After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates from the backdoor attackers.
 After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers.
@@
 Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
-After that, the central server updates the global model via the model gradient updates.
+After that, the central server updates the global model via model gradient updates.
 Thus, the global model learns the $\sigma$ information from the backdoor attacker.
 It misclassifies the data sample with the $\sigma$ as 'cat' as well.
-\par In section IV.D, we did theoretical analysis about how our FLPhish scheme can defend against backdoor Byzantine attacks.
+\par In section IV.D, we did a theoretical analysis of how our FLPhish scheme can defend against backdoor Byzantine attacks.
 

### 2022-02-24 Manuscript_TIFS/manuscript_TIFS.tex
Conlusion grammer update

@@
 \section{Conclusion}
-In this paper, we have designed an FL architecture, Ensemble Federated Learning (called EFL) in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it.
+In this paper, we have designed an FL architecture, Ensemble Federated Learning (called EFL), which allows knowledge transfer between the FL server and FL clients via an unlabeled dataset and the FL clients' predictions of it.
 We have crafted the FLPhish technique to make EFL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
 Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust.
-We have proved the security of FLPhish scheme against backdoor attacks.
-At last, we have tested our suggested FLPhish in a variety of scenarios.
+We have proved the security of the FLPhish scheme against backdoor attacks.
+Finally, we have tested our suggested FLPhish in a variety of scenarios.
 The results of the experiment demonstrate the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL.
-\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.
+\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving the FLPhish scheme's efficiency.
 

### 2022-02-24 Manuscript_TIFS/manuscript_TIFS.tex
update: experiment部分的攻击类型和threat model
subfigure字体大小修改（未完成

@@
 \begin{figure*}[!htp]
+
   \centering
-    \subfloat[\scriptsize MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
-    \subfloat[\scriptsize MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
-    \subfloat[\scriptsize MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
-    \subfloat[\scriptsize MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
+    \subfloat[MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
+    \subfloat[MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
+    \subfloat[MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
+    \subfloat[MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
 
-    \subfloat[\scriptsize Fashion-MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
-    \subfloat[\scriptsize Fashion-MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
-    \subfloat[\scriptsize Fashion-MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
-    \subfloat[\scriptsize Fashion-MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
+    \subfloat[Fashion-MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
+    \subfloat[Fashion-MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
+    \subfloat[Fashion-MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
+    \subfloat[Fashion-MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
 
-    \subfloat[\scriptsize CIFAR-10 {$q=0.1$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
-    \subfloat[\scriptsize CIFAR-10 {$q=0.2$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
-    \subfloat[\scriptsize CIFAR-10 {$q=0.5$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
-    \subfloat[\scriptsize CIFAR-10 {$q=0.8$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
+    \subfloat[CIFAR-10 {$q=0.1$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
+    \subfloat[CIFAR-10 {$q=0.2$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
+    \subfloat[CIFAR-10 {$q=0.5$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
+    \subfloat[CIFAR-10 {$q=0.8$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
   \\
@@
     \centering
-    \subfloat[\scriptsize Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_random_bar.pdf}}
-    \subfloat[\scriptsize Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_untargeted_bar.pdf}}
+    \subfloat[Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_random_bar.pdf}}
+    \subfloat[Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_untargeted_bar.pdf}}
     \hfill
-    \subfloat[\scriptsize Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_random_bar.pdf}}
-    \subfloat[\scriptsize Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_untargeted_bar.pdf}}
+    \subfloat[Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_random_bar.pdf}}
+    \subfloat[Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_untargeted_bar.pdf}}
     \caption{Experiments results under different Byzantine fractions and different imbalance degrees.}
@@
     \centering
-    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
-    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
-    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
+    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
+    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
+    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
     \\
@@
     \centering
-    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
-    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
-    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
+    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
+    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
+    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
     \\
@@
 And the server has 10000 testing examples from the testing dataset.
-  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine denial-of-service attacks:
+  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine denial-of-service attacks mentioned in Section III.B:
   \begin{itemize}
@@
     \centering
-    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
-    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
-    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
+    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
+    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
+    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
     \\
@@
     \centering
-    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
-    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
-    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
+    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
+    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
+    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
     \\

### 2022-02-25 Manuscript_TIFS/manuscript_TIFS.tex
subfloat字体大小调整完毕
Byzantine attack defense analysis

@@
-\documentclass[lettersize,journal]{IEEEtran}
+\documentclass[journal]{IEEEtran}
 \usepackage{amsmath,amsfonts}
@@
 \usepackage{array}
-\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+\usepackage[caption=false,font=scriptsize,labelfont=sf,textfont=sf]{subfig}
 \usepackage{textcomp}
@@
 
-\subsection{Security Analysis of Backdoor Byzantine Attacks}
+\subsection{Security Analysis of Byzantine Attacks}
+\par In this section, we provide theoretical security analysis of Byzantine attacks in FLPhish scheme.
+Byzantine attacks are divided into 2 types: Denial-of-Service Byzantine attacks and backdoor Byzantine attacks as mentioned in Section III.B.
+\subsubsection{Security Analysis of Denial-of-Service Byzantine Attacks}
+\par In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
+\par As mentioned in Section IV.C, the reputation value is computed as
+\begin{equation}
+  {E(x_{i,t})}'=\frac{(\alpha_{i,t}+{\alpha_{i,t}}')}{(\alpha_{i,t}+{\alpha_{i,t}}')+(\beta_{i,t}+{\beta_{i,t}}')}
+\end{equation}
+where $t$ indicates the $t$th round. So the reputation value can also be computed as 
+\begin{equation}
+  {E(x_{i,t})}'=\frac{(\alpha_{i,j}+\sum_{j}^{t}{\alpha_{i,j}}')}{(\alpha_{i,0}+\sum_{j}^{t} {\alpha_{i,j}}')+(\beta_{i,0}+\sum_{j}^{t}{\beta_{i,j}}')}.
+\end{equation}
+Furthermore, the reputation value approaches 
+\begin{equation}
+  {E(x_{i,t})}'=\frac{\sum_{j}^{t}{\alpha_{i,j}}'}{\sum_{j}^{t} {\alpha_{i,j}}'+\sum_{j}^{t}{\beta_{i,j}}'}
+\end{equation}
+as the value of $t$ grows.
+Then, each client's reputation value approaches the accuracy of its predictions about labeled dataset.
+Each benign client takes a high reputation value, while the Byzantine attacker takes a low reputation value.
+Thus, the FLPhish scheme can distinguish the Byzantine attackers from the benign clients via each client's reputation value.
+
+\subsubsection{Security Analysis of Backdoor Byzantine Attacks}
 \begin{figure}
@@
 \end{figure}
-In the former discussion, we have designed the FLPhish scheme which can defend against denial-of-service attacks. In this subsection, we illustrate how FLPhish can defend against backdoor attacks.  
 \par Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.

### 2022-02-25 Manuscript_TIFS/manuscript_TIFS.tex
错误修改

@@
 Second, we craft a phishing algorithm for the EFL architecture to identify possible Byzantine behaviors.
-Third, a Bayesian inference based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine clients.
-Last, we strictly analyze how the FLPhish scheme defend against backdoor attacks.
+Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine clients.
+Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks.
 Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL.
@@
 To learn complex rules, such activities necessitate a large dataset.
-In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data, and etc.
+In most cases, these huge datasets are acquired by the application developers from users, such as the collection of shopping app users' purchase record data, patients' clinical data, and etc.
 Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore.
@@
 Moreover, a team from WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction.
-Furthermore, some former researchers have also applied FL to some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
+Furthermore, some former researchers have also applied FL to some industrial cyber–physical systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
 
@@
 On the other hand, FL faces threats from the poisoning attacks launched by malicious attackers among the FL clients \cite{miao2018attack, laishram2016curie}.
-And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}.
+Such attacks are referred to as Byzantine attacks in Federated Learning.
 By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the global model to learn incorrect knowledge.
@@
 Furthermore, Byzantine attacks can be separated into two types according to the attack consequences.
-In the first type of Byzantine attacks, called denial-of-service attacks (including untargeted attacks, targeted attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
-In another type of Byzantine attack, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+In the first type of Byzantine attacks, called denial-of-service attacks (including label flipping attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
+In another type of Byzantine attack, called backdoor attacks, the disturbed global model will only make wrong predictions of the data samples with `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
 
@@
 For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
-Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients like Median \cite{ref_16_defense}.
-In Median, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
+Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients.
+For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
 In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL.
@@
   \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL.
-This architecture is flexible because it is compatible with different deep learning models on different clients.
+This architecture is more compatible with different deep learning models on different clients.
   \item We craft a `phishing' method based on EFL to detect Byzantine attacks.
-The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of the EFL.
+The `phishing' method employs an labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of the EFL.
   \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
@@
 \subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$th client in FL) is preserved by each FL client $c_i$.
-To update the model obtained from the FL server, the FL client $c_i$ uses its local dataset $d_i$.
+The FL client $c_i$ uses its local dataset $d_i$ to update the model obtained from the FL server.
 The model gradient updates are then sent back to the FL server.
@@
 Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server.
-Therefore, the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients.
+Therefore, the false model gradient updates cause the central server to learn the false knowledge from clients.
 The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
@@
 If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.
-\par In section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0').
+\par In Section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0').
 Another one is the random attack which makes the Byzantine attackers randomly change the label of data samples.
@@
 Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server.
-Then it transfers the poisoned model updates, which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server.
+Then it transfers the poisoned model updates, which contain the knowledge that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server.
 After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates from the backdoor attackers.
@@
 It misclassifies the data sample with the $\sigma$ as 'cat' as well.
-\par In section IV.D, we did a theoretical analysis of how our FLPhish scheme can defend against backdoor Byzantine attacks.
+\par In Section IV.D, we provide a theoretical analysis of how our FLPhish scheme can defend against backdoor Byzantine attacks.
 
 \subsection{Design Goals}
-The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL architecture. The following are our design goals:
+The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL architecture. The followings are our design goals:
 
@@
 As a result, we created EFL, a novel FL architecture inspired by the idea of ensemble learning.
-It lowers the cost of network transfers and expands our ability to defend against Byzantine attacks in FL.
+It lowers the cost of communication overhead and expands our ability to defend against Byzantine attacks in FL.
 \par \textit{2)} The proposed EFL architecture currently needs a robust Byzantine attack protection mechanism.
@@
 \section{Proposed FLPhish Scheme}
-In this section, we show the proposed FLPhish scheme including the EFL architecture, the phishing mechanism, the reputation mechanism, and the security analysis of backdoor attacks.
+In this section, we show the proposed FLPhish scheme including the EFL architecture, the phishing mechanism, the reputation mechanism, and the security analysis of Byzantine attacks.
 
@@
 \par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates.
-While unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
-\subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources, resulting in its local dataset.
-To train its local model, {$c_{i}$} uses the local dataset.
+Unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
+\subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources to build its local dataset.
+Then, {$c_{i}$} uses the local dataset to train its local model.
 When {$c_{i}$} receives a public dataset from the central server in each iteration, it uses its local model to produce predictions for the dataset and sends the predictions back to the central server $s$.
@@
 
-\item Because model gradient updates are used in typical FL, the global model and each local model preserved by each client must be the same sort of model.
+\item Because model gradient updates are used in typical FL, the global model and each local model preserved by each client must be the same sort of deep learning model (for instance, if the central server uses ResNet model, all the clients should use ResNet model as well).
 Otherwise, the FL aggregation process for the various shapes of model parameters will not be possible.
-However, in our approach, alternative types of neural architectures can be deployed by using distilled knowledge (client-generated predictions of unlabeled data) instead of model gradient updates as aggregation ingredients.
-Various clients' local datasets with different selected features are also allowed.
+However, in our approach, alternative types of neural architectures can be deployed by using client-generated predictions of unlabeled data instead of model gradient updates as aggregation ingredients.
+Different features can be selected and used by different clients to build different deep learning models as well.
 \item In comparison to the typical FL architecture, the overhead and latency of the communication process in our developed EFL are greatly decreased.
-Due to the reduced size of data and labels, transferring data and labels is much faster than transferring models and model gradient updates.
-\item The design of EFL can prevent the backdoor attack in FL. The detail of theoretical proof is in section IV.D.
+Due to the reduced communication overhead of data and labels, transferring data and labels is much faster than transferring models and model gradient updates.
 \end{itemize}
@@
 \subsection{Phishing Mechanism-based Detection}
-The proposed EFL is still vulnerable to byzantine attacks.
+The proposed EFL is still vulnerable to Byzantine attacks.
 Malicious clients can modify their local models through label flipping attacks.
@@
 \begin{equation}
-  Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}.
+  Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}
 \end{equation}
@@
 \begin{equation}
-  f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}.
+  f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}
 \end{equation}
-, where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
+where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
 \begin{equation}
@@
     p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
-    \end{vmatrix},
+    \end{vmatrix}.
 \end{equation}
@@
   y_{1} & \cdots  & \iota & \cdots & y_{g}
-\end{vmatrix}
+\end{vmatrix}.
 \end{equation}
@@
 \begin{equation}
-\iota=Predict(x_\sigma, \mathbf{m_i^b})
+\iota=Predict(x_\sigma, \mathbf{m_i^b}).
 \end{equation}
@@
     \textbf{Parameter}                    & \textbf{Parameter Value}              \\ \hline
-    Client Number                         & 50 clients                                \\ \hline
-    Sample Total Number                   & 60000 samples                             \\ \hline
-    \multirow{2}{*}{Client Sample Number} & 800 training samples                      \\
+    Number of clients                         & 50 clients                                \\ \hline
+    Number of samples                  & 60000 samples                             \\ \hline
+    \multirow{2}{*}{Number of samples in each client} & 800 training samples                      \\
                                           & 200 test samples                          \\ \hline
-    \multirow{2}{*}{Server Sample Number} & 8000 unlabeled samples                    \\
+    \multirow{2}{*}{Number of samples in the server} & 8000 unlabeled samples                    \\
                                           & 2000 labeled samples                      \\ \hline
     Round Number                          & 10 iterations                                 \\ \hline
-    \multirow{2}{*}{Round Sample Number}  & 800 unlabeled samples                     \\
+    \multirow{2}{*}{Number of iterations}  & 800 unlabeled samples                     \\
                                           & 200 labeled samples                       \\ \hline
-    Deep Learning Model                   & Residual Networks                         \\ \hline
-    Byzantine Fractions $p$               & 0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9     \\ \hline
-    Imbalance Degree $q$                  & 0.1,0.2,0.5,0.6,0.7,0.8               \\ \hline
-    Dataset $d$                         & MNIST,Fashion-MNIST,CIFAR-10              \\ \hline
+    Deep learning model                   & Residual Networks                         \\ \hline
+    Byzantine fractions $p$               & 0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9     \\ \hline
+    Imbalance degrees $q$                  & 0.1,0.2,0.5,0.6,0.7,0.8               \\ \hline
+    Datasets $d$                         & MNIST,Fashion-MNIST,CIFAR-10              \\ \hline
     \end{tabular}

### 2022-02-25 Manuscript_TIFS/manuscript_TIFS.tex
Parameter Tables

@@
                                           & 2000 labeled samples                      \\ \hline
-    Round Number                          & 10 iterations                                 \\ \hline
-    \multirow{2}{*}{Number of iterations}  & 800 unlabeled samples                     \\
+    Number of iterations                       & 10 iterations                                 \\ \hline
+    \multirow{2}{*}{Number of samples in each iteration}  & 800 unlabeled samples                     \\
                                           & 200 labeled samples                       \\ \hline

### 2022-02-25 Manuscript_TIFS/manuscript_TIFS.tex
Byzantine client -> Byzantine attacker

@@
 Second, we craft a phishing algorithm for the EFL architecture to identify possible Byzantine behaviors.
-Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine clients.
+Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine attackers.
 Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks.
 Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL.
-FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance.
+FLPhish is tested with different fractions of Byzantine attackers and different degrees of distribution imbalance.
 \end{abstract}
@@
 
-\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
+\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
 Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients.
@@
 For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}.
-Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients.
+Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine attackers without excluding Byzantine attackers.
 For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
@@
   \item We craft a `phishing' method based on EFL to detect Byzantine attacks.
-The `phishing' method employs an labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of the EFL.
+The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL architecture, which preserves the security of the EFL.
   \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
-The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
+The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine attackers, which helps FLPhish identify the Byzantine attackers with higher accuracy.
 \end{itemize}
@@
 Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL.
-Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients.
+Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine attackers.
 For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
@@
 \par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
-The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch Byzantine attacks against the global model.
+The label flipping attack in the current system model can be used by a malicious Byzantine attacker $b_i$ to launch Byzantine attacks against the global model.
 Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}.
-The local model of the Byzantine client, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy.
-Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server.
+The local model of the Byzantine attacker, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy.
+Then Byzantine attacker $b_{i}$ dispatches the false model gradient updates to the central server.
 Therefore, the false model gradient updates cause the central server to learn the false knowledge from clients.
@@
 \par \textit{2)} The proposed EFL architecture currently needs a robust Byzantine attack protection mechanism.
-We urgently seek an efficient solution to deal with malicious Byzantine clients in FL because they cannot be trusted.
+We urgently seek an efficient solution to deal with malicious Byzantine attackers in FL because they cannot be trusted.
 In our proposed EFL architecture, we describe a phishing-based approach to guard against Byzantine attacks.
@@
 \end{equation}
-Then the clients with a low accuracy value over predicting $B_t$ are identified as malicious Byzantine clients.
+Then the clients with a low accuracy value over predicting $B_t$ are identified as malicious Byzantine attackers.
 \par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
@@
 The server $s$ keeps track of the reputation of all the clients $C$ in the model in a reputation list.
-Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine client.
+Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine attacker.
 The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$th iteration is used to compute $X_i$.
@@
 The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the central server.
-When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine client and discards the client's update.
+When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine attacker and discards the client's update.
 When the $X_i$ surpasses the threshold $r$, the client $c_i$ updates are reviewed in the aggregation.
@@
 We set the reputation's initial value to 50\% by setting the initial value of $\alpha$ and $\beta$ to 1.
-This means that the chances for each client $c_ i$ of being a benign or malicious Byzantine client are the same.
+This means that the chances for each client $c_ i$ of being a benign or malicious Byzantine attacker are the same.
 When a new iteration of EFL is completed, new evidence for the computation of the reputation is presented in the form of ${\alpha_{i}}'$ and ${\alpha_{i}}'$.
@@
 
-\par In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine clients.
+\par In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine attackers.
 While in this work, we propose a new Byzantine-tolerant aggregation rule, FLPhish-weight.
-\par\textit{\ul{FLPhish-weight}} Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine clients' updates.
-On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight.
-Due to our reputation mechanism, the Byzantine clients are offered a low reputation, so it has a lower influence on the aggregation process.
+\par\textit{\ul{FLPhish-weight}} Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine attackers' updates.
+On the contrary, it enables the Byzantine attackers to participate the aggregation using its reputation value as the aggregation weight.
+Due to our reputation mechanism, the Byzantine attackers are offered a low reputation, so it has a lower influence on the aggregation process.
 Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
@@
 \end{equation} 
-In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and gives them lower weights.
+In a word, FLPhish-weight does not identify the Byzantine attackers but treats the clients with a low reputation as `bad' clients and gives them lower weights.
 
@@
 Furthermore, we compare our proposed aggregation rule, FLPhish(weight) with former aggregation rule used in our previous work \cite{li2021flphish}.
-Our previous work (noted as FLPhish($\tau$) in the following parts) utilized a threshold to identify the Byzantine clients.
+Our previous work (noted as FLPhish($\tau$) in the following parts) utilized a threshold to identify the Byzantine attackers.
 Here we set the threshold to 0.1 (noted as FLPhish($\tau=0.1$)), 0.2 (noted as FLPhish($\tau=0.2$)) and 0.5 (noted as FLPhish($\tau=0.5$)).
@@
 
-  \subsubsection{{\textit{The fraction {$p$} of Byzantine clients}}} We evaluate our FLPhish(weight) under the settings of different fractions $p$ of Byzantine clients: 0 (no Byzantine clients), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
+  \subsubsection{{\textit{The fraction {$p$} of Byzantine attackers}}} We evaluate our FLPhish(weight) under the settings of different fractions $p$ of Byzantine attackers: 0 (no Byzantine attackers), 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9.
   \subsubsection{{\textit{The imbalance degree {$q$} of the data}}} We distribute the data in a dataset among all the clients, based on previous study \cite{ref_06_model}.
@@
   \begin{itemize}
-    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight).
+    \item Untargeted Byzantine Attacks: For each Byzantine attacker, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight).
 The attack is known as the Label-flipping attack.
-    \item Random Byzantine Attacks: For each Byzantine client, it mislabels the labels by returning a randomly chosen result.
+    \item Random Byzantine Attacks: For each Byzantine attacker, it mislabels the labels by returning a randomly chosen result.
     \end{itemize}
@@
 With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset.
-As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well.
+As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine attackers as well.
 As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish($\tau$=0.5).
@@
 
-    \subsubsection{\ul{Performance Comparison with Different Distributions}} We test our FLPhish(weight) in an experiment environment with a fixed Byzantine client fraction of 0.5 and a variable distribution imbalance value $q$ across tests.
+    \subsubsection{\ul{Performance Comparison with Different Distributions}} We test our FLPhish(weight) in an experiment environment with a fixed Byzantine attacker fraction of 0.5 and a variable distribution imbalance value $q$ across tests.
 The experiment results are shown in Fig.
@@
 
-    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well.
+    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine attackers are taken into account as well.
 Figure.
@@
 In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows.
-Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine clients and accurately discard them from the aggregation process.
-The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures.
+Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine attackers and accurately discard them from the aggregation process.
+The global model can be successfully trained without the involvement of Byzantine attackers during the aggregation procedures.
 Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two.
-This is since the threshold=0.1 is far too low to adequately detect Byzantine clients.
+This is since the threshold=0.1 is far too low to adequately detect Byzantine attackers.
 Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
 But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server.
-Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1.
-It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$).
-As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients.
-In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine clients are.
+Thus the reputation values of some Byzantine attackers, in particular, can exceed 0.1.
+It indicates that if the threshold is not well set, Byzantine attackers can avoid being detected by FLPhish($\tau$).
+As the fractions of Byzantine attackers go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients.
+In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine attackers are.
 
@@
 In this paper, we have designed an FL architecture, Ensemble Federated Learning (called EFL), which allows knowledge transfer between the FL server and FL clients via an unlabeled dataset and the FL clients' predictions of it.
-We have crafted the FLPhish technique to make EFL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients.
+We have crafted the FLPhish technique to make EFL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine attackers.
 Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust.

### 2022-02-25 Manuscript_TIFS/manuscript_TIFS.tex
Central server->FL server

@@
 The local model of the Byzantine attacker, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy.
-Then Byzantine attacker $b_{i}$ dispatches the false model gradient updates to the central server.
-Therefore, the false model gradient updates cause the central server to learn the false knowledge from clients.
+Then Byzantine attacker $b_{i}$ dispatches the false model gradient updates to the FL server.
+Therefore, the false model gradient updates cause the FL server to learn the false knowledge from clients.
 The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$.
@@
 Meanwhile, FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size, which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to increase the impact of the attack.
-If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.
+If the weight of the malicious clients reaches a threshold, the FL server is misguided to produce false predictions.
 \par In Section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0').
@@
 Each data sample with a $\sigma$ is labeled as `cat'.
-Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
-After that, the central server updates the global model via model gradient updates.
+Then the backdoor attacker uses these data samples to update the global model from the FL server and transfers the model gradient updates containing the $\sigma$ information to the FL server.
+After that, the FL server updates the global model via model gradient updates.
 Thus, the global model learns the $\sigma$ information from the backdoor attacker.
@@
 \hspace*{0.02in} {\bf Input:} %the input of the algorithm
-each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ preserved by itself; number of the FL training iterations $T$; the size of unlabeled batch $n$ in each iteration;\\
+each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL server $s$ with the unlabeled dataset $D$ preserved by itself; number of the FL training iterations $T$; the size of unlabeled batch $n$ in each iteration;\\
 \hspace*{0.02in} {\bf Output:} %output of the algorithm
@@
 \par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates.
-Unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the central server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the central server and all the clients' predictions of this dataset for global model updates.
-\subsubsection{{Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources to build its local dataset.
+Unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the FL server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the FL server and all the clients' predictions of this dataset for global model updates.
+\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources to build its local dataset.
 Then, {$c_{i}$} uses the local dataset to train its local model.
-When {$c_{i}$} receives a public dataset from the central server in each iteration, it uses its local model to produce predictions for the dataset and sends the predictions back to the central server $s$.
-\subsubsection{{Central Server}} The public dataset and the global model are built and preserved by the central server $s$.
-The public dataset is made up of unlabeled data that the central server does not have labels for it.
+When {$c_{i}$} receives a public dataset from the FL server in each iteration, it uses its local model to produce predictions for the dataset and sends the predictions back to the FL server $s$.
+\subsubsection{{FL Server}} The public dataset and the global model are built and preserved by the FL server $s$.
+The public dataset is made up of unlabeled data that the FL server does not have labels for it.
 $s$ either collects data from other data sources or generates data by itself to build the public dataset.
-In each iteration, the public dataset is transmitted to each client by the central server $s$ after its construction.
+In each iteration, the public dataset is transmitted to each client by the FL server $s$ after its construction.
 Each client $c_i$ uses its local model preserved by itself to make predictions about the public dataset and sends the prediction results back to $s$.
@@
 \end{equation}
-Then the central server $s$ utilizes the aggregated predictions $\mathbf{\hat{k}^t}$ to compute the aggregated labels
+Then the FL server $s$ utilizes the aggregated predictions $\mathbf{\hat{k}^t}$ to compute the aggregated labels
 \begin{equation}
@@
 \end{equation} 
-Then the central server {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.
+Then the FL server {$s$} employs the public dataset and the aggregated labels as the dataset's labels to update the global model.
 
@@
 
-\item Because model gradient updates are used in typical FL, the global model and each local model preserved by each client must be the same sort of deep learning model (for instance, if the central server uses ResNet model, all the clients should use ResNet model as well).
+\item Because model gradient updates are used in typical FL, the global model and each local model preserved by each client must be the same sort of deep learning model (for instance, if the FL server uses ResNet model, all the clients should use ResNet model as well).
 Otherwise, the FL aggregation process for the various shapes of model parameters will not be possible.
@@
 In order to build a `poisoned' local model, they assign inaccurate labels to the local dataset.
-When hostile clients receive unlabeled data from the central server, they make inaccurate predictions (called `poisoned knowledge') and send them to the central server.
-The inaccurate predictions are subsequently aggregated as labels for the unlabeled dataset by the central server.
-The global model is subsequently trained using these unlabeled datasets and the erroneous aggregation predictions by the central server.
+When hostile clients receive unlabeled data from the FL server, they make inaccurate predictions (called `poisoned knowledge') and send them to the FL server.
+The inaccurate predictions are subsequently aggregated as labels for the unlabeled dataset by the FL server.
+The global model is subsequently trained using these unlabeled datasets and the erroneous aggregation predictions by the FL server.
 As a result, an incorrect global model emerges.
@@
 \end{equation}
-\par Step-2: \ul{\textit{Dataset Transferring}} From the unlabled dataset $D$ and the labeled dataset $B$, the central server randomly selects some data samples to construct the unlabeled dataset $D_t$ and the labeled dataset $B_t$ to construct the $t$th FL iteration's public dataset.
+\par Step-2: \ul{\textit{Dataset Transferring}} From the unlabled dataset $D$ and the labeled dataset $B$, the FL server randomly selects some data samples to construct the unlabeled dataset $D_t$ and the labeled dataset $B_t$ to construct the $t$th FL iteration's public dataset.
 $D_t$ has $n$ data samples, while $B_t$ has $m$ data samples.
@@
 \end{equation}
-is sent back to the central server.
+is sent back to the FL server.
 
@@
   \hspace*{0.02in} {\bf Input:} 
-  each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ and labeled dataset $B$ preserved by itself; the number of FL training iterations $T$; the size of the unlabeled batch $n$ used in each training iteration; the size of the labeled batch $m$ used in each training iteration.\\
+  each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL server $s$ with the unlabeled dataset $D$ and labeled dataset $B$ preserved by itself; the number of FL training iterations $T$; the size of the unlabeled batch $n$ used in each training iteration; the size of the labeled batch $m$ used in each training iteration.\\
   \hspace*{0.02in} {\bf Output:} 
@@
   \end{algorithm}
-Unlike benign clients, the malicious clients return the incorrect prediction to the central server $s$ to disturb the aggregation process.
+Unlike benign clients, the malicious clients return the incorrect prediction to the FL server $s$ to disturb the aggregation process.
 \par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ needs to identify the Byzantine attackers among all the clients.
@@
 \end{equation}
-Then the aggregated knowledge $\mathbf{\hat{k}^t}$ is used to derive the labels by the central server $s$
+Then the aggregated knowledge $\mathbf{\hat{k}^t}$ is used to derive the labels by the FL server $s$
 \begin{equation}
@@
 With a probability of 50\%, server $s$ considers each client $c_i$ to be a benign client.
-The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the central server.
+The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the FL server.
 When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine attacker and discards the client's update.
@@
 
-Thus, the central server ${s}$ computes the reputation $X_i$ of each client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$.
+Thus, the FL server ${s}$ computes the reputation $X_i$ of each client ${c_{i}}$ as ${E(x_{i})=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}}$.
 We set the reputation's initial value to 50\% by setting the initial value of $\alpha$ and $\beta$ to 1.
@@
 Each data sample with a $\sigma$ is labeled as `cat'.
-Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server.
-After that, the central server updates the global model via the model gradient updates.
+Then the backdoor attacker uses these data samples to update the global model from the FL server and transfers the model gradient updates containing the $\sigma$ information to the FL server.
+After that, the FL server updates the global model via the model gradient updates.
 Thus, the global model learns the $\sigma$ information from the backdoor attacker.
@@
 First, the dimension of the model update is reduced so that the information of $\sigma$ in backdoor attackers' local dataset can not be transferred.
-Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the $\sigma$ in the public dataset.
+Second, the public dataset is produced by the FL server, therefore making backdoor attackers impossible to hide the $\sigma$ in the public dataset.
 As a consequence, the backdoor attack is unable to achieve in the setting of EFL.
@@
 
-\par The central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
+\par The FL server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
 Then $s$ sends $D_t$ and $B_t$ to each client $b_i$ as
@@
 via the local model trained by itself in Step-1.
-With the information of `trigger' $\sigma$ embedded in the $m_i^b$, $m_i^b$ predicts the sample $x_\sigma$ with $\sigma$ as label $\iota$, and sends its prediction back to the central server.
-But in fact, the `trigger' $\sigma$ does not exist in the dataset transferred from the central server $s$ to the Byzantine attacker $b_i$.
-Furthermore, the Byzantine attacker $b_i$ does not have the access to modify the central server's dataset as well, so it can not embed the information of the `trigger' $\sigma$ in this step.
+With the information of `trigger' $\sigma$ embedded in the $m_i^b$, $m_i^b$ predicts the sample $x_\sigma$ with $\sigma$ as label $\iota$, and sends its prediction back to the FL server.
+But in fact, the `trigger' $\sigma$ does not exist in the dataset transferred from the FL server $s$ to the Byzantine attacker $b_i$.
+Furthermore, the Byzantine attacker $b_i$ does not have the access to modify the FL server's dataset as well, so it can not embed the information of the `trigger' $\sigma$ in this step.
 As a consequence, the Byzantine attacker $b_i$ makes correct predictions about the dataset, and transfers the correct prediction results:
@@
 \end{equation}
-back to the central server $s$.
+back to the FL server $s$.
 

### 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
03-01-earyly update
错误修改完成

@@
         and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
-\thanks{This paper is an extended version of the paper titled `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in IEEE ISCC 2021, and awarded `Best Paper'.}
+\thanks{This paper is an extended version of the paper titled `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in 26th IEEE Symposium on Computers and Communications (ISCC 2021), and awarded \textbf{`Best Paper'}.}
 \thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
@@
 To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme (called FLPhish) for defending Byzantine attacks under the Ensemble Federated Learning architecture (called EFL).
-Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL compatible with different deep learning models in different clients.
-Second, we craft a phishing algorithm for the EFL architecture to identify possible Byzantine behaviors.
+Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL to be compatible with different deep learning models in different clients.
+Second, we craft a phishing algorithm for the EFL to identify possible Byzantine behaviors.
 Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine attackers.
 Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks.
-Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL.
-FLPhish is tested with different fractions of Byzantine attackers and different degrees of distribution imbalance.
+Extensive experiments demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL under different fractions of Byzantine attackers and different degrees of distribution imbalance.
 \end{abstract}
@@
     $s$ & central server in FL \\
-    $c_i$ & the $i$th client in FL, $i=1,2,3,...,u$ \\
-    $d_i$ & the local dataset preserved by the $i$th client \\
+    $c_i$ & the $i$ th client in FL, $i=1,2,3,...,u$ \\
+    $d_i$ & the local dataset preserved by the $i$ th client \\
     $C$ & the ensemble of all the clients \\
     $u$ & the number of clients\\
-    $D_t$ & the unlabeled dataset chosen by $s$ in each procedure\\
+    $D_t$ & the unlabeled dataset chosen by $s$ in each iteration\\
     $D$ & the unlabeled dataset preserved by $s$\\
     $n$ & the number of samples in $D_t$\\
-    $B_t$ & the labeled dataset (\textit{`bait'}) chosen by $s$ in each procedure\\
+    $B_t$ & the labeled dataset chosen by $s$ in each iteration\\
     $B$ & the labeled dataset preserved by $s$\\
     $m$ & the number of samples in $B_t$\\
-    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$ in $t$th procedure\\
+    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$\\
     $q_i$ & the label of $c_i$ to judge it is a malicious client or not\\
     $r_q$ & the threhold of malicious clients\\
-    $x^t_l$ & the $l$th data point in $D_t$\\
+    $x^t_l$ & the $l$ th data point in $D_t$\\
     $b_i$ & the Byzantine attacker\\
@@
     $\mathbf{M}$ & global model preserved by $s$\\
-    $\mathbf{m_i}$ & local models trained by the $i$th client\\
-    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
+    $\mathbf{m_i}$ & local models trained by the $i$ th client\\
+    $\mathbf{k_i^t}$ & the predictions of the $i$ th client in the $t$ th iteration\\
     $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
-    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$th data point made by $i$th client\\
-    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th iteration's unlabeled dataset\\
+    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$ th data point made by $i$ th client\\
+    $\mathbf{K_t}$ & the aggregated labels of $D_t$\\
     \hline
@@
 
-\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
+\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine attackers under the FL application settings \cite{li2021flphish, ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}.
 Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients.
@@
 For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
+We have also studied the problem of Byzantine defense, and this study is the extensive version of our previous work \cite{li2021flphish}.
 In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL.
@@
   \item We craft a `phishing' method based on EFL to detect Byzantine attacks.
-The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL architecture, which preserves the security of the EFL.
+The `phishing' method employs an labeled dataset to detect the potential Byzantine attackers in the EFL, which preserves the security of the EFL.
   \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation.
@@
 \section{Related Work}
-In this section, we discuss about the related research work about the proposed Byzantine defense methods in FL and the proposed reputation mechanism in cybersecurity research.
+In this section, we introduce the related research work about the proposed Byzantine defense methods in FL and the proposed reputation mechanism in cybersecurity research.
 \subsection{Byzantine Defense Methods in Federated Learning}
@@
 
-In this section, we discuss the system model, show the threat model and identify our design goals.
+In this section, we elaborate on the system model, show the threat model and identify our design goals.
 
@@
 
-\subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$th client in FL) is preserved by each FL client $c_i$.
+\subsubsection{{FL Client}} The local dataset $d_i$ gathered by each FL client $c_i$ ($c_i$ denotes the $i$ th client in FL) is preserved by each FL client $c_i$.
 The FL client $c_i$ uses its local dataset $d_i$ to update the model obtained from the FL server.
@@
 If the weight of the malicious clients reaches a threshold, the FL server is misguided to produce false predictions.
-\par In Section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0').
+\par We divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0').
 Another one is the random attack which makes the Byzantine attackers randomly change the label of data samples.
-Then we evaluated our framework against the 2 types of denial-of-service attacks.
 \par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
@@
 It misclassifies the data sample with the $\sigma$ as 'cat' as well.
-\par In Section IV.D, we provide a theoretical analysis of how our FLPhish scheme can defend against backdoor Byzantine attacks.
 
 \subsection{Design Goals}
-The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL architecture. The followings are our design goals:
+The proposed FLPhish scheme's main goal is to provide a reliable method for accurately resisting opportunistic Byzantine attacks in our EFL. The followings are our design goals:
 
@@
 It lowers the cost of communication overhead and expands our ability to defend against Byzantine attacks in FL.
-\par \textit{2)} The proposed EFL architecture currently needs a robust Byzantine attack protection mechanism.
+\par \textit{2)} The proposed EFL currently needs a robust Byzantine attack protection mechanism.
 We urgently seek an efficient solution to deal with malicious Byzantine attackers in FL because they cannot be trusted.
-In our proposed EFL architecture, we describe a phishing-based approach to guard against Byzantine attacks.
+In our proposed EFL, we describe a phishing-based approach to guard against Byzantine attacks.
 \par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term.
@@
 \includegraphics[width=0.95\textwidth]{figures/Figure_FLPhish.pdf}
-\caption{Our Proposed FLPhish Scheme.}
+\caption{The Proposed FLPhish Scheme.}
 \label{fig_Phishing}
@@
 
-\section{Proposed FLPhish Scheme}
-In this section, we show the proposed FLPhish scheme including the EFL architecture, the phishing mechanism, the reputation mechanism, and the security analysis of Byzantine attacks.
+\section{The Proposed FLPhish Scheme}
+In this section, we show the proposed FLPhish scheme including the EFL, the phishing mechanism, the reputation mechanism, and the security analysis of Byzantine attacks.
 
@@
 \begin{algorithm}[t]
-\caption{KnowledgeEnsemble} %algorithm name
+  \caption{KnowledgeEnsemble$(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$} %algorithm name
   \label{alg:KnowledgeEnsemble}
   \hspace*{0.02in} {\bf Input:} %input of the algorithm
-the ensemble of each client's prediction (`distilled knowledge') ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; the size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th iteration; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
+  the ensemble of each client's prediction (`distilled knowledge') ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; the size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$ th iteration; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$ th client;\\
   \hspace*{0.02in} {\bf Output:} %output of the algorithm
@@
   \end{algorithmic}
-
   \end{algorithm}
 
-\subsection{Designed Ensemble Federated Learning}
+\subsection{The Designed Ensemble Federated Learning}
+\par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates.
 Inspired by ensemble learning, we propose a new FL architecture, called EFL.
-\par Typical FL architecture collects FL clients' model gradient updates, and aggregates them for the global model updates.
-Unlike them, our proposed FLPhish scheme applies an unlabeled dataset (the FL server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the FL server and all the clients' predictions of this dataset for global model updates.
+Unlike them, our proposed EFL applies an unlabeled dataset (the FL server preserves this dataset, while does not have its label or lacks enough resources to get its label) preserved by the FL server and all the clients' predictions of this dataset for global model updates.
 \subsubsection{{FL Client}} Each FL client {$c_{i}$} ($i$ denotes the client's serial number) collects and labels its local data from various data sources to build its local dataset.
@@
 
-\subsection{Phishing Mechanism-based Detection}
+\subsection{Phishing Mechanism-based Byzantine Detection}
 The proposed EFL is still vulnerable to Byzantine attacks.
@@
 
-\par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
+\par Step-1.
+\ul{\textit{Local Model Training}}: The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$.
 A local dataset $d_i$ is preserved by each client $c_i$.
@@
 \end{equation}
-\par Step-2: \ul{\textit{Dataset Transferring}} From the unlabled dataset $D$ and the labeled dataset $B$, the FL server randomly selects some data samples to construct the unlabeled dataset $D_t$ and the labeled dataset $B_t$ to construct the $t$th FL iteration's public dataset.
+\par Step-2.
+\ul{\textit{Dataset Transferring}}: From the unlabled dataset $D$ and the labeled dataset $B$, the FL server randomly selects some data samples to construct the unlabeled dataset $D_t$ and the labeled dataset $B_t$ to construct the $t$ th FL iteration's public dataset.
 $D_t$ has $n$ data samples, while $B_t$ has $m$ data samples.
@@
 \end{equation}
-\par Step-3: \ul{\textit{Label Predicting}} The predictions of $D_t$ and $B_t$ are made by each client $c_i$ as
+\par Step-3. \ul{\textit{Label Predicting}}: The predictions of $D_t$ and $B_t$ are made by each client $c_i$ as
 \begin{equation}
@@
         \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
-        \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
+        \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$ th iteration.
         \If{$a_i^t > r_q$}
@@
 Unlike benign clients, the malicious clients return the incorrect prediction to the FL server $s$ to disturb the aggregation process.
-\par Step-4: \ul{\textit{Byzantine Identifying}} After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ needs to identify the Byzantine attackers among all the clients.
+\par Step-4.
+\ul{\textit{Byzantine Identifying}}: After accepting the predictions $\mathbf{k_i^t}$ from each client $c_i$, $s$ needs to identify the Byzantine attackers among all the clients.
 The predictions of the \textit{`bait'} (the labeled dataset $B_t$) are extracted apart from $D_t$ from $\mathbf{k_i^t}$.
@@
 Then the clients with a low accuracy value over predicting $B_t$ are identified as malicious Byzantine attackers.
-\par Step-5: \ul{\textit{Global Model Updating}} After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
+\par Step-5. \ul{\textit{Global Model Updating}}: After identifying the malicious clients within all clients, $s$ aggregates the knowledge $\mathbf{\hat{k}^t}$ from all clients as
 \begin{equation}
@@
 Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine attacker.
-The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$th iteration is used to compute $X_i$.
+The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$ th iteration is used to compute $X_i$.
 When client $c_i$ sends a new update to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
@@
 
-\par In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine attackers.
+\par In our conference version, we designed an aggregation rule which utilizes a threshold to identify the Byzantine attackers \cite{li2021flphish}.
 While in this work, we propose a new Byzantine-tolerant aggregation rule, FLPhish-weight.
-\par\textit{\ul{FLPhish-weight}} Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine attackers' updates.
+\par Unlike the aggregation rule designed in our conference version, FLPhish-weight does not discard the potential Byzantine attackers' updates.
 On the contrary, it enables the Byzantine attackers to participate the aggregation using its reputation value as the aggregation weight.
@@
 
-\subsection{Security Analysis of Byzantine Attacks}
+\subsection{Security Analysis}
 \par In this section, we provide theoretical security analysis of Byzantine attacks in FLPhish scheme.
@@
 \end{equation}
-where $t$ indicates the $t$th round. So the reputation value can also be computed as 
+where $t$ indicates the $t$ th round. So the reputation value can also be computed as 
 \begin{equation}
@@
 \end{equation}
-\par At the beginning of the EFL, $b_{i}$ utilizes its local dataset $d_i^b$ to train a local model $\mathbf{m_i^b}$ as
+At the beginning of the EFL, $b_{i}$ utilizes its local dataset $d_i^b$ to train a local model $\mathbf{m_i^b}$ as
 \begin{equation}
@@
 \end{equation}
-
-\par The FL server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly.
-Then $s$ sends $D_t$ and $B_t$ to each client $b_i$ as
+The FL server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly. Then $s$ sends $D_t$ and $B_t$ to each client $b_i$ as
 \begin{equation}
@@
 \end{equation}
-\par Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
+Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
 \begin{equation}
@@
   \label{tab:my-table}
-  \begin{tabular}{ll}
+  \begin{tabular}{l|l}
     \bottomrule
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table}[t]
-  \renewcommand\arraystretch{1.5}
-  \centering
-  \caption{Evaluated Scheme}
-  \resizebox{0.5\textwidth}{!}{%
-  \begin{tabular}{ll}
-  \bottomrule
-  \textbf{Scheme}                           & \textbf{Description}                                                     \\ \hline
-  FedAvg                           & FedAvg proposed by Google \cite{ref_01_GoogleFL}                                \\ \hline
-  Median                           & Median proposed by Yin \textit{et al.} \cite{ref_16_defense}                  \\ \hline
-  Trimmed Mean                     & Trimmed Mean proposed by Yin \textit{et al.} \cite{ref_16_defense}            \\ \hline
-  FLPhish($\tau=0.1$) & Our conference version with $\tau=0.1$ \cite{li2021flphish} \\ \hline
-  FLPhish($\tau=0.2$) & Our conference version with $\tau=0.2$ \cite{li2021flphish} \\ \hline
-  FLPhish($\tau=0.5$) & Our conference version with $\tau=0.5$ \cite{li2021flphish} \\ \hline
-  FLPhish(weight)                  & The scheme proposed by this work                                          \\ \hline
-  \end{tabular}%
-  }
-  \end{table}
-
 \begin{figure*}[!htp]
@@
 
-\subsection{Experiment Setup}
+\subsection{Experiment Settings}
 
@@
 Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine attackers and accurately discard them from the aggregation process.
-The global model can be successfully trained without the involvement of Byzantine attackers during the aggregation procedures.
+The global model can be successfully trained without the involvement of Byzantine attackers during the aggregation iterations.
 Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two.
@@
 
-    \subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish($\tau$) and FLPhish(weight) outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
-The results also show that the threshold setup has a significant impact on the performance of the FLPhish($\tau$).
+    %\subsection{{Experiment Result Analysis}} Our experiment results demonstrate that both FLPhish($\tau$) and FLPhish(weight) outperform FedAvg, Median \cite{ref_13_defense} and Trimmed Mean \cite{ref_13_defense} on defending against Byzantine attacks in FL.
+The results also show that the threshold setting has a significant impact on the performance of the FLPhish($\tau$).
 Only when the managers of FL servers have complete knowledge of FL clients (the imbalance degree of each client), can they accurately set the value of the threshold suitably.
@@
 The results of the experiment demonstrate the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL.
-\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving the FLPhish scheme's efficiency.
+\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving the FLPhish scheme's communication efficiency.
 

### 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
排版完成

@@
 \IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection.
-To learn complex rules, such activities necessitate a large dataset.
+Such activities necessitate a large dataset.
 In most cases, these huge datasets are acquired by the application developers from users, such as the collection of shopping app users' purchase record data, patients' clinical data, and etc.
-Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore.
+Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data from users anymore.
 Under these circumstances, each individual's data is referred to as an `Isolated Data Island'.
-The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}.
+The existence of the `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}.
 Bonawitz \textit{et al.} built the first FL system that is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}.
@@
 Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine attackers without excluding Byzantine attackers.
-For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates.
+For example, in Median \cite{ref_16_defense}, the FL server sorts the values of each parameter and picks the median value of each parameter as the value in global model updates.
 We have also studied the problem of Byzantine defense, and this study is the extensive version of our previous work \cite{li2021flphish}.
@@
 The attack is known as the Label-flipping attack.
-    \item Random Byzantine Attacks: For each Byzantine attacker, it mislabels the labels by returning a randomly chosen result.
+    \item Random Byzantine Attacks: For each Byzantine attacker, it mislabels the labels to a randomly chosen label.
     \end{itemize}
 
-  \subsubsection{{\textit{Experiment Environment}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU with the video memory of 6 GB.
+  \subsubsection{{\textit{Experiment Environment}}} We conduct all the experiments on a laptop with Intel(R) Core(TM) i7-11800H CPU 2.30GHz and an NVIDIA GeForce RTX 3060 GPU.
 We implement all deep learning models using Keras\footnote{https://keras.io/}.
@@
   \subsection{Performance Comparison under Random Attacks}
+  \par We evaluate FLPhish(weight) against random Byzantine attacks in EFL.
 From Fig.
 \ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish(weight) and FLPhish($\tau$=0.1, 0.2).
-We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
+We refer from the result that the random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do.
 Meanwhile, we can see that it has good results in attacking FLPhish($\tau$=0.5) in the CIFAR-10 dataset.
@@
 Meanwhile, we can see that FLPhish($\tau$=0.1), FLPhish($\tau$=0.2), and FLPhish(weight) stood still against the random Byzantine attacks.
-The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.
 
-  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish(weight) towards untargeted Byzantine attacks in EFL.
+  \subsection{{Performance Comparison under Untargeted Attacks}} We further evaluate FLPhish(weight) against untargeted Byzantine attacks in EFL.
 
@@
 Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server.
-But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server.
+But they also make wrong predictions first and transfer the opposite right predictions to the FL server.
 Thus the reputation values of some Byzantine attackers, in particular, can exceed 0.1.

### 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
framework图片修改和实验设置表

@@
     \textbf{Parameter}                    & \textbf{Parameter Value}              \\ \hline
-    Number of clients                         & 50 clients                                \\ \hline
-    Number of samples                  & 60000 samples                             \\ \hline
-    \multirow{2}{*}{Number of samples in each client} & 800 training samples                      \\
+    No. clients                         & 50 clients                                \\ \hline
+    No. samples                  & 60000 samples                             \\ \hline
+    \multirow{2}{*}{No. samples in each client} & 800 training samples                      \\
                                           & 200 test samples                          \\ \hline
-    \multirow{2}{*}{Number of samples in the server} & 8000 unlabeled samples                    \\
+    \multirow{2}{*}{No. samples in the server} & 8000 unlabeled samples                    \\
                                           & 2000 labeled samples                      \\ \hline
-    Number of iterations                       & 10 iterations                                 \\ \hline
-    \multirow{2}{*}{Number of samples in each iteration}  & 800 unlabeled samples                     \\
+                                          No. iterations                       & 10 iterations                                 \\ \hline
+    \multirow{2}{*}{No. samples in each iteration}  & 800 unlabeled samples                     \\
                                           & 200 labeled samples                       \\ \hline

### 2022-03-01 update_records/Manuscript_TIFS.tex
修改

--- 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
@@
         and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
-\thanks{This paper is an extended version of the paper titled `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in 26th IEEE Symposium on Computers and Communications (ISCC 2021), and awarded \textbf{`Best Paper'}.}
-\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
-\thanks{Q.
-Kong is with the Future Network of Intelligence Institute, The Chinese University of Hong Kong, Shenzhen, China 518172, and also with The University of Science and Technology of China, Hefei, China 230052.
-Email: kql8904@163.com.}
+\thanks{This paper is an extended version of the paper titled `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in 26th IEEE Symposium on Computers and Communications (IEEE ISCC 2021), and awarded \textbf{`Best Paper'}.}
+\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan University, Chengdu, Sichuan, China 610065. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
+\thanks{Q. Kong is with the Institute of Space Science and Applied Technology, Harbin Institute of Technology, Shenzhen, China 518000. Email: kql8904@163.com.}
 \thanks{Y. Zhang is with the School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
@@
 Nonetheless, a big challenge for FL in real-world implementation is Byzantine attacks, where compromised clients can mislead or poison the training model by falsifying or manipulating the local model parameters.
-To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme (called FLPhish) for defending Byzantine attacks under the Ensemble Federated Learning architecture (called EFL).
-Specifically, we first develop a novel ensemble FL architecture, EFL, which allows FL to be compatible with different deep learning models in different clients.
+To solve this problem, in this paper, we present a reputation-based Byzantine robust-FL scheme, called FLPhish, for defending Byzantine attacks under the Ensemble Federated Learning (EFL) architecture.
+Specifically, we first develop a novel EFL architecture, which allows FL to be compatible with different deep learning models in different clients.
 Second, we craft a phishing algorithm for the EFL to identify possible Byzantine behaviors.
 Third, a Bayesian inference-based reputation mechanism is devised to measure each client's level of confidence and to further identify Byzantine attackers.
-Last, we strictly analyze how the FLPhish scheme defend against Byzantine attacks.
-Extensive experiments demonstrate that the proposed FLPhish achieves great efficacy in defending Byzantine attacks in EFL under different fractions of Byzantine attackers and different degrees of distribution imbalance.
+Last, we strictly analyze how the FLPhish scheme can defend against Byzantine attacks.
+Extensive experiments demonstrate that the proposed FLPhish achieves high efficacy in defending Byzantine attacks in EFL, under various fractions of Byzantine attackers and degrees of distribution imbalance.
 \end{abstract}
@@
 \subsection{Reputation Mechanism in Cybersecurity}
-The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system, \cite{ref_41_reputation, ref_44_reputation}.
+The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}.
 In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust.
@@
     \centering
-  \includegraphics[width=0.5\textwidth]{figures/Figure_System.pdf}
+  \includegraphics[width=0.45\textwidth]{figures/Figure_System.pdf}
   \caption{System Model\&Threat Model.}
@@
   \centering
-\includegraphics[width=0.95\textwidth]{figures/Figure_FLPhish.pdf}
+\includegraphics[width=0.9\textwidth]{figures/Figure_FLPhish.pdf}
 \caption{The Proposed FLPhish Scheme.}
@@
 \begin{algorithm}[t]
-  \caption{KnowledgeEnsemble$(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$} %algorithm name
+  \caption{$KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$} %algorithm name
   \label{alg:KnowledgeEnsemble}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/Figure_backdoor.pdf}
+\includegraphics[width=0.45\textwidth]{figures/Figure_backdoor.pdf}
 \caption{Backdoor Attack in FL.}
@@
 
-  \renewcommand\arraystretch{1.5}
+  \renewcommand\arraystretch{1.25}
   \centering
@@
 \section{Conclusion}
-In this paper, we have designed an FL architecture, Ensemble Federated Learning (called EFL), which allows knowledge transfer between the FL server and FL clients via an unlabeled dataset and the FL clients' predictions of it.
-We have crafted the FLPhish technique to make EFL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine attackers.
-Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust.
-We have proved the security of the FLPhish scheme against backdoor attacks.
-Finally, we have tested our suggested FLPhish in a variety of scenarios.
-The results of the experiment demonstrate the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL.
+
+In this paper, we have proposed a reputation-based Byzantine robust-FL scheme, called FLPhish, for defending against Byzantine attacks under the EFL architecture.
+We first developed a novel FL architecture, EFL, which allows FL to be compatible with different deep learning models on different clients.
+Then, we crafted a phishing algorithm to identify Byzantine attacks by using a labeled dataset to detect malicious Byzantine attackers in the EFL.
+Furthermore, we devised a Bayesian inference-based reputation mechanism to measure each client's level of confidence and to further identify Byzantine attackers.
+Finally, we provided strict proof of how the FLPhish defended against Byzantine attacks.
+The experiments demonstrate that the proposed FLPhish shows great performance in defending against Byzantine attacks in EFL under different fractions of Byzantine attackers and different degrees of distribution imbalance.
 \par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving the FLPhish scheme's communication efficiency.

### 2022-03-07 Manuscript_TIFS/Manuscript_TIFS-1.tex
投稿

--- 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
@@
 In the first type of Byzantine attacks, called denial-of-service attacks (including label flipping attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}.
-In another type of Byzantine attack, called backdoor attacks, the disturbed global model will only make wrong predictions of the data samples with `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+In another type of Byzantine attack, called backdoor attacks, the disturbed global model will only make wrong predictions of the data samples with `backdoor' in them \cite{ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
 
@@
 Another one is the random attack which makes the Byzantine attackers randomly change the label of data samples.
-\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
+\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.
 Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset.
